### 2021-01-31 firms/mgmt/CuratingLocKnowledge_Bocconi_03-2021.tex
Added Bocconi lecture

\documentclass[10pt]{beamer}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{amsmath}
\usepackage{mathpazo}
\usepackage{hyperref}
\usepackage{multimedia}
\usepackage{multicol}
\usepackage{epsfig}
\usepackage{curves}
\usepackage{epsfig}
\usepackage{epic}
\usepackage{curves}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{fix-cm}
\usepackage{graphicx}
\usepackage{hyperref}

\setcounter{MaxMatrixCols}{10}
%TCIDATA{OutputFilter=LATEX.DLL}
%TCIDATA{Version=5.00.0.2606}
%TCIDATA{Codepage=932}
%TCIDATA{<META NAME="SaveForMode" CONTENT="1">}
%TCIDATA{BibliographyScheme=Manual}
%TCIDATA{Created=Friday, November 03, 2006 10:56:24}
%TCIDATA{LastRevised=Thursday, February 19, 2015 11:02:18}
%TCIDATA{<META NAME="GraphicsSave" CONTENT="32">}
%TCIDATA{<META NAME="DocumentShell" CONTENT="Other Documents\SW\Slides - Beamer">}
%TCIDATA{Language=American English}
%TCIDATA{CSTFile=beamer.cst}

\newenvironment{stepenumerate}{\begin{enumerate}[<+->]}{\end{enumerate}}
\newenvironment{stepitemize}{\begin{itemize}[<+->]}{\end{itemize} }
\newenvironment{stepenumeratewithalert}{\begin{enumerate}[<+-| alert@+>]}{\end{enumerate}}
\newenvironment{stepitemizewithalert}{\begin{itemize}[<+-| alert@+>]}{\end{itemize} }
\usetheme{Boadilla}

\usefonttheme{serif}
\setbeamercovered{invisible}

%------------------------------------------------
%	PRESENTATION BASICS
%------------------------------------------------

\title[Curating Local Knowledge]{Curating Local Knowledge}
\subtitle{Experimental Evidence from Small Retailers in Indonesia}

\author[Dalton, R{\"u}schenp{\"o}hler, Uras, and Zia]
{
Patricio S. Dalton\inst{1}\
Julius R{\"u}schenp{\"o}hler\inst{2}
Burak Uras\inst{1}\\and
Bilal Zia\inst{3}
}

\institute[]
{
\inst{1} Tilburg University\\
\bigskip
\inst{2} CEGA, UC Berkeley\\
\bigskip
\inst{3} The World Bank\\
}

\date{March 04, 2021}

\title[Curating Local Knowledge]{Curating Local Knowledge}
\subtitle{Experimental Evidence from Small Retailers in Indonesia}

\author[Dalton, R{\"u}schenp{\"o}hler, Uras, and Zia]
{
Patricio S. Dalton\inst{1}\
Julius R{\"u}schenp{\"o}hler\inst{2}
Burak Uras\inst{1}\\and
Bilal Zia\inst{3}
}

\institute[]
{
\inst{1} Tilburg University\\
\bigskip
\inst{2} CEGA, UC Berkeley\\
\bigskip
\inst{3} The World Bank\\
}

\date{March 04, 2021}

%------------------------------------------------
%	PRESENTATION SLIDES
%------------------------------------------------

\begin{document}

\begin{frame}
\titlepage
\end{frame}

%\begin{frame}
%\frametitle{Overview}
%\tableofcontents[hideallsubsections]
%\end{frame}

%------------------------------------------------
\section{Background}

\begin{frame}
\frametitle{Background}
	\begin{itemize}
	\item Micro \& Small firms (MSEs) main \textbf{source of employment} in the developing world
	\vspace{0.2in}
	\item In \textbf{Indonesia}, MSEs represent 99\% of all firms and 94.5\% of employment 
	\vspace{0.2in}
	\item Understanding the factors fostering efficiency and growth of MSEs is an important research and policy goal
	\end{itemize}
\end{frame}

%------------------------------------------------
\begin{frame}
\frametitle{A Growing Focus on Management}
\begin{itemize}
\item \textbf{Classroom Training}: Field, et al. (2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); Drexler, Fischer \& Schoar (2014); McKenzie \& Woodruff (2014, 2017); Bulte et al. (2017); Anderson, Chandy \& Zia (2018); Lafortune et al. (2018)
\vspace{0.2in}
\item \textbf{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
\vspace{0.2in}

\item \textbf{Mobilizing Peer Knowledge}:
    \begin{itemize}
    \item Brooks et al. (2018) $\rightarrow$ Local mentors (market information)
    \item Cai \& Szeidl (2018) $\rightarrow$ Business meetings
    \item Abebe et al. (2019) $\rightarrow$ Management experience matching
    \end{itemize}
    \vspace{0.2in}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{What We Do}
\begin{itemize}
\item Some facts about business practices in firms:
	\begin{itemize}	
	\item Vast heterogeneity in business practices and performance across similar businesses (de Mel, McKenzie \& Woodruff, 2009)
	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US (Bloom et al, 2019)
	\end{itemize}
\vspace{0.2in}
\pause
\item Research thus far has mostly overlooked this underlying heterogeneity in design and implementation of programs
\vspace{0.2in}
\pause
\item Our idea is to make it \textbf{central} to the research design: 
	\begin{itemize}
	\item Use variation across businesses to identify business practices associated with successful performance
	\item Instead of teaching set courses, provide consulting, or matching; we curate what works from local peers
	\item Test different communication channels and their cost-effectiveness
\end{itemize}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Selecting Local Best Practices}
\begin{itemize}
\item Detailed \textcolor[rgb]{0.00,0.07,1.00}{qualitative interviews} with local business peers:
    \begin{itemize}
    \item Understand and codify their practices (record-keeping, financial planning, stocking-up, marketing, and joint decision-making)
    \item Identify implementation norms and beliefs regarding each practice (e.g. whether they are complicated, necessary, etc.)
    \item Document locally relevant tips and rule of thumbs
    \end{itemize}
\vspace{0.2in}
\item Baseline \textcolor[rgb]{0.00,0.07,1.00}{quantitative survey}
    \begin{itemize}
    \item Measure practices and outcomes
    \item Quantitative association of business practices with profits and sales
    \end{itemize}
\end{itemize}
\end{frame}

%
\begin{frame}
\frametitle{How Do We Share this Knowledge?}
		\begin{itemize}
		\item \textbf{Handbook}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Pure information}: Which practices, how to adopt, and why?\\
            %\item \textbf{Positive Frame}: Retailers who implement [x] report y\% \textbf{higher} sales and z\% \textbf{higher} profits.
            %\item \textbf{Negative Frame}: Retailers who do \textbf{not} implement [x] report y\% \textbf{lower} sales and z\% \textbf{lower} profits.
			\end{itemize}
\bigskip
Supplemented with two types of experiential learning:
\bigskip
		\item \textbf{Movie}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Psychological and emotional involvement}$\rightarrow$ social learning is possible through \textbf{observing the successful experience of similar others}.
			\item Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013).\\
			\end{itemize}

\bigskip
		\item \textbf{In-shop Light Assistance}
			\begin{itemize}
			\item \textcolor[rgb]{0.00,0.07,1.00}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textbf{experience, with a small nudge} (Kolb, 1984).
			\end{itemize}
			\vspace{0.05in}
%\bigskip
%			$\rightarrow$ Horse race between role models and business counseling.
		\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Research Questions}
	\begin{itemize}
	%\item \textbf{Local characterization}
	%\vspace{0.05in}
	%	\begin{itemize}
	%	\item Which practices are associated with high profits?
	%	\item How do successful businesses implement them?
	%	\end{itemize}
	%\vspace{0.05in}
	\item \textbf{Adoption}
		\begin{itemize}
		\item Do retailers adopt these practices once peer best practices are aggregated and made common knowledge?
		\item If so, ...
			\begin{itemize}
			\item Does the type of experiential involvement matter?
			\end{itemize}
		\end{itemize}
    \vspace{0.3in}
	\item \textbf{Impact}
		\begin{itemize}
		\item Does firm profitability increase?
		\item If so, what are the channels?
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Sample}
\begin{itemize}
\item Listing of 2042 small retail businesses from 29 administrative communities (Kelurahan) in urban Jakarta
\item Selection criteria for firm listing:
	\begin{itemize}
%	\item General willingness to grow
	\item At least 4$m^{2}$ in size
	\item At least two different product categories on offer
	\item At least 30 meters distance to next business in sample $\rightarrow$ to minimize spillovers
	\end{itemize}
\item Random sample of 1301 from the list
\item Randomization to treatment arms stratified by
	\begin{itemize}
	\item Gender
	\item Firm space (4-6$m^2$, 6-10$m^2$, 10 and above $m^2$)
	\item Composite score of business practices above or below median
	\item Kelurahan
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Experimental Design}
	\begin{itemize}
%    \item \textbf{Same set of business practices} across treatments \\
	\item Three types of information provision:
	\vspace{0.05in}
		\begin{itemize}
		\item \textcolor[rgb]{0.00,0.07,1.00}{Handbook} with best practices and tips
		\vspace{0.05in}
		\item \textcolor[rgb]{0.00,0.07,1.00}{Movie} with successful peers
		\vspace{0.05in}
		\item Business practice implementation \textcolor[rgb]{0.00,0.07,1.00}{assistance}
		\end{itemize}
	\vspace{0.05in}
\end{itemize}
	\begin{itemize}
\item{Five experimental groups}
        %\begin{itemize}
        %\item{Handbooks (N=1040)}
        %: Positive Framing (N=520) and Negative Framing (N=520)}\\
	\vspace{0.05in}
            \begin{enumerate}
              \item \textcolor[rgb]{0.00,0.07,1.00}{Handbook} only (N=260)
              \item \textcolor[rgb]{0.00,0.07,1.00}{Handbook} and invitation to \textcolor[rgb]{0.00,0.07,1.00}{movie} screening (N=260)
              \item \textcolor[rgb]{0.00,0.07,1.00}{Handbook} and offer of two \textcolor[rgb]{0.00,0.07,1.00}{assistance} visits (N=260)
              \item \textcolor[rgb]{0.00,0.07,1.00}{Handbook} and both \textcolor[rgb]{0.00,0.07,1.00}{movie} and \textcolor[rgb]{0.00,0.07,1.00}{assistance} (N=260)
              \item Control (N=261)
            \end{enumerate}
        \end{itemize}
    %\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Timeline}
\begin{enumerate}
    \item September 2015: \textcolor[rgb]{0.00,0.07,1.00}{Qualitative} Interviews
    \item[]
    \item January 2016: \textcolor[rgb]{0.00,0.07,1.00}{Listing} for Baseline
    \item[]
    \item Feb-Apr 2016: \textcolor[rgb]{0.00,0.07,1.00}{Baseline} Survey
    \item[]
    \item Oct-Nov 2016: \textcolor[rgb]{0.00,0.07,1.00}{Interventions}
    \item[]
    \item Apr-May 2017: \textcolor[rgb]{0.00,0.07,1.00}{Midline}
    \item[]
    \item Apr-May 2018: \textcolor[rgb]{0.00,0.07,1.00}{Endline}
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Typical Retail Shop in the Sample}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=4in]{pics/retailer1.jpg}
	%\caption{Best-practices handbook}
	\label{height}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Typical Retail Shop in the Sample II}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=4in]{pics/retailer2.jpg}
	%\caption{Best-practices handbook}
	\label{height}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Handbook}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=4in]{pics/handbook.jpg}

	\label{height}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Handbook Content}
\begin{figure}[htbp]
	\centering
		\includegraphics[width=2.6in]{pics/Handbook_return.jpg}

	\label{height}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Handbook Content II}

\begin{figure}[htbp]
	\centering
		\includegraphics[width=2.6in]{pics/Handbook_stepbystep.jpg}

	\label{height}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Movie with Successful Peers}
\begin{figure}[htbp]
	\centering
		\includegraphics[width=4.4in]{pics/movie.jpg}

	\label{height}
\end{figure}
\end{frame}

\begin{frame}
\frametitle{Implementation Assistance for Business Practices}
\begin{figure}[htbp]
	\centering
		\includegraphics[width=2.0in]{pics/Assistance_expl.jpg}

	\label{height}
\end{figure}
\end{frame}

\section{Data and Analysis}

\begin{frame}
\frametitle{Summary Statistics}
{\tiny{
	\begin{table}
		%\begin{adjustbox}{width=9.6cm}
		\centering	
		%\tabcolsep=0.2cm

			\begin{tabular}{l*{10}{c}}
			\hline\hline
			\hline

&\multicolumn{1}{c}{\textbf{Control}}
&&\multicolumn{1}{c}{\textbf{HB only}}	
&&\multicolumn{1}{c}{\textbf{HB \& MOV}	}
&&\multicolumn{1}{c}{\textbf{HB \& HELP}}	
&&\multicolumn{1}{c}{\textbf{HB \& MOV}}	\\

&\multicolumn{1}{c}{}
&&\multicolumn{1}{c}{}	
&&\multicolumn{1}{c}{}
&&\multicolumn{1}{c}{}	
&&\multicolumn{1}{c}{\textbf{\& HELP}}	\\

&\textit{N = 261}	
&&\textit{N = 260}	
&&\textit{N = 260}	
&&\textit{N = 260}	
&&\textit{N = 260}	\\
\hline \\

\textbf{Firm Owner Characteristics} \\
Gender (Male=1)											& 0.28	&& 0.3	&&0.29	&& 0.3	&& 0.28\\
Age														&45.22	&&45.27	&&45.28	&&45.16	&&45.38 \\
Education (Years)										&9.1	&&9.52	&&9.36	&&9.42	&&9.55 \\
%Digitspan												& 1.7	&& 1.67 && 	1.8 &&	1.67	&& 1.69 \\
														%&(1.12) 	&& 		&& 		&& 		&& 		&& \\
Risk Preference (0 - 10 ``Perfectly Risk-Seeking'')		&3.74	&&3.76	&&3.88	&&3.6	&&3.68 \\											
Time Preference	(0 - 10 ``Perfect Patience'')			&5.19	&&5.07	&&5.21	&&5.25	&&5.2 \\[0.5ex]
\\														
\textbf{Firm Characteristics} \\
Firm Age (Years)										&12.76		&&13.77		&&14.03		&&13.98		&&13.47 \\
Family Member Is Business Partner							&0.56		&&0.6		&&0.63		&&0.59		&&0.62 \\
Total Number of Workers									&2.03		&&2.05		&&1.9		&&1.99		&&2.04 \\
%Number of Full Time Paid Employees						&0.09		&&0.1		&&0.08		&&0.08		&&0.11		&&0.08 \\
														%&(0.3)		&&			&&			&&			&&			&& \\
Business Has Tax ID										&0.2		&&0.21		&&0.2		&&0.15		&&0.18 \\
Total Sales Last Month (USD PPP)						&4454.37 &&	4730.64	&& 4840.55	&& 4761.4	&& 5139 \\

Total Profits Last Month (USD PPP)						& 889.58	&& 961.1 &&	926.78	&& 825.25	&& 934.66 \\
Applied for Bus Loan in Last 12 Months
			    & 0.2	&& 0.17	&& 0.15	&& 0.22	&& 0.17 \\

Obtained Bus Loan in Last 12 Months
						& 0.18 &&	0.15	&& 0.14	&& 0.18	&& 0.14 \\[0.5ex]
\\
\\
\textbf{Business Practices} \\
Management Practices Aggregate Score											& 0.37	&& 0.36	&& 0.37	&& 0.35	&& 0.37 \\
\hspace{3mm}Marketing Subscore												& 0.23	&& 0.23 &&	0.25	&& 0.23	&& 0.24 \\
\hspace{3mm}Stocking-up	Subscore											& 0.45	&& 0.47	&& 0.47	&& 0.47	&& 0.46 \\
\hspace{3mm}Record-keeping Subscore											& 0.33	&& 0.28	&& 0.3	&& 0.29 &&	0.3 \\
\hspace{3mm}Financial-planning Subscore									& 0.51	&& 0.47	&& 0.47	&& 0.43	&& 0.47 \\
%\hspace{3mm} Discussion Subscore                        & 0.57	&& 0.59	  && 0.61	&& 0.6	&& 0.64  \\
&		&&		&&		&& \\
		\hline
		\hline
			\end{tabular}
		%\end{adjustbox}

		%\begin{adjustbox}{center}
			%\begin{tabular}{l*{12}{l}}
			%\multicolumn{13}{p{0.95\textwidth}}{\footnotesize \textit{Notes}: $^1$ Last month's sales and profits appear with both tails winsorized at 1%.}
			%\end{tabular}
		%\end{adjustbox}

	\end{table}}}
\begin{itemize}
\item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Movie: Take Up and Assessment}
{\scriptsize{\begin{table}[htbp]
%\fontsize{10}{11}\selectfont
  \centering
 %   \tabcolsep=0.10cm
    %\begin{adjustbox}{width=11cm}
    \begin{tabular}{lcc}
    \hline
   	& (1)   					&(2)   						 \\
    \hline
  	& \textbf{HB \& MOV} 		& \textbf{HB \& MOV}		  \\
  	& 							& \textbf{\& HELP}			\\
   	& \textbf{(A)}   			& \textbf{(B)}   			 \\
 	&							&							\\
% 	&							&							&& \textit{F-test}\\
   	%	& Assigned 				& Assigned 					&&  \\
   	& \textit{N=260} 			& \textit{N=260} 			 \\
   \hline
   														&		&		 \\
    \textbf{Attendance} 								&       &         \\
  	% 													&		&		&& \\
    Business Owner or Partner Attended Film Screening 	& 0.52  & 0.49   \\
    %Baseline respondent attended film screening 		& 0.47  & 0.45  && 0.792 \\
   	%Respondent was reminded by phone 					& 0.05  & 0.07  && 0.355 \\
    %Respondent was reminded by visit to business 		& 0.35  & 0.33  && 0.782 \\
    %Distance to screening location (in decimal degrees)& 0.01  & 0.01  && 0.869 \\
	&       &       \\
    \textbf{Evaluation (1-4 Scale):}	&       &        \\
   	%									&       &       &&  \\
    Has Learned Something New	& 3.34  & 3.21  \\
    Feels Inspired 				& 3.31  & 3.30   \\
    Feels Hopeful 				& 3.60  & 3.42   \\
    Feels Bored 				& 0.83  & 0.97    \\
    \end{tabular}
   % \end{adjustbox}

\end{table}}}

\end{frame}

%%% Attendance and feedback to assistance + comparison between experimental groups
\begin{frame}

\frametitle{Assistance: Take Up and Assessment}
{\scriptsize{\begin{table}[htbp]
%\fontsize{10}{11}\selectfont
  \centering
    %\tabcolsep=0.10cm
   % \begin{adjustbox}{width=11cm}
    \begin{tabular}{lcc}
    \hline
    & (1)   			& (2) 			\\
    \hline
   	& \textbf{HB \& HELP} 		& \textbf{HB \& MOV,}		 \\
  	& 							& \textbf{\& HELP}			 \\
   	& \textbf{(A)}   			& \textbf{(B)}   			\\
	&							&							 \\
% 	&							&							&& \textit{F-test}\\
   	%	&& Assigned 				& Assigned 					&&  \\
   	& \textit{N=260} 			& \textit{N=260} 		\\
    \hline
          																				&       &      \\
    \multicolumn{1}{l}{\textbf{Attendance}} 											&       &        \\
    %\multicolumn{1}{l}{\textit{1st session}} 											&       &       & &  \\
    \multicolumn{1}{l}{    Business Owner or Partner Attended 1st Session} 				& 0.77  & 0.78  \\
    %\multicolumn{1}{l}{    Baseline respondent attended 1st session} 					& 0.76  & 0.77  && 0.756 \\
    %\multicolumn{1}{l}{    Recipient plans to use at least one new practice} 			& 0.37  & 0.47  && 0.021** \\
    %\multicolumn{1}{l}{    Recipient plans neither handbook study nor implementation} 	& 0.12  & 0.11  && 0.784 \\
         														 						%&     	&       &&  \\
    %\multicolumn{1}{l}{\textit{2nd session}} 											&       &       &&  \\
    \multicolumn{1}{l}{    Business Owner or Partner Attended 2nd Session} 				& 0.68  & 0.68   \\
    %\multicolumn{1}{l}{    Baseline respondent attended 2nd session} 					& 0.67  & 0.67  && 1 \\
    %\multicolumn{1}{l}{    Recipient plans to use at least one new practice} 			& 0.39  & 0.47  && 0.063* \\
    %\multicolumn{1}{l}{    Recipient plans neither handbook study nor implementation} 	& 0.13  & 0.08  && 0.044** \\
          																				&       &        \\
    \multicolumn{1}{l}{\textbf{Evaluation (1-4 Scale)}} 								&       &         \\
    \multicolumn{1}{l}{Has Learned Something New} 										& 2.88  & 2.89   \\
    \multicolumn{1}{l}{Feels Inspired} 													& 2.76  & 2.83   \\
    \multicolumn{1}{l}{Feels Hopeful} 													& 2.88  & 2.97  \\
    \multicolumn{1}{l}{Feels Bored} 													& 0.59  & 0.43   \\
    \end{tabular}
   % \end{adjustbox}

\end{table}}}
\end{frame}

\begin{frame}
\frametitle{Impact on Business Practices}
\framesubtitle{Aggregate Scores}
{\tiny{\begin{table}[t]
%\centering
%\begin{adjustbox}{width=10cm}
%	\tabcolsep=0.05cm
	\begin{tabular}{l*{10}{c}}
		\hline \hline
		\\
			&\textbf{Record}			&&\textbf{Planning}			&&\textbf{Stocking-up}	&&\textbf{Marketing} && \textbf{Joint} \\
&\textbf{Keeping}                       &&                        &&	                   &&	 && Decision-making \\
					&(1)					&&(2)						&&(3) 						&&(4) && (5)\\
			\cline{2-2}					\cline{4-4}					\cline{6-6}			\cline{8-8} \cline{10-10}  \\

Assigned Handbook 			&                    0.025   &&	          0.027   	 &&           -0.007   	 &&          -0.011   	  &&         0.011
      \\
         							&               (0.209)   	   &&      (0.273)   	&&         (0.694)   	     &&    (0.694)   	&&         (0.694)
    \\

Assigned Handbook \& Movie 	&                     0.057*** 	 &&          0.043  	   &&       0.038  	    &&       0.040    &&        0.040        \\
          							&              (0.009)   &&	         (0.107)   	  &&       (0.117)   	  &&       (0.166)   	 &&        (0.217)         \\

Assigned Handbook \& Assistance 	&              0.065*** 	  &&         0.034   	&&           0.011   	 &&           0.039 	       &&      0.037    \\
         							&           (0.004)   	  &&       (0.166)   &&	         (0.664)   && 	         (0.166)   	  &&       (0.239)    \\

Assigned All Three          	&                0.054***	  &&         0.068***  	 &&          0.053**  	    &&       0.061**	   &&        0.059*          \\
									&             (0.009)    &&	         (0.009)   	&&         (0.020)   	  &&       (0.032)   &&	         (0.094)           \\

\hline         							
\\
R-squared									&               0.204   	 &&          0.192   	&&           0.187   	&&           0.150	 &&           0.120             \\
Sample Size 								&               2205   	  &&          2204   	   &&         2205   	 &&           2205   	    &&        2205      \\
Dependent Variable Mean of Control 		&                  0.196  	  &&         0.402   	 &&          0.471    &&	           0.250    	 &&          0.269          \\
Dependent Variable SD of Control 			&              0.252    	 &&          0.310   	  &&         0.270      	  &&         0.320    && 	           0.420        	\\
F-tests (p-value):							&			&&			&&			&&			\\
\hspace{5mm}Book = Book \& Mov				        &               0.069   	   &&           0.487   	  &&          0.014     	  &&          0.028    	 &&          0.300           \\
\hspace{5mm}Book = Book \& Assistance				        &               0.025  	  &&          0.754     	 &&           0.304   	 &&          0.030    	  &&          0.348                 \\
\hspace{5mm}Book = All Three				        &                  0.096    	  &&         0.073    	    &&      0.001   	  &&         0.002    &&	         0.082        \\
\hline
	\end{tabular}
%\end{adjustbox}
\end{table}}}
\begin{itemize}
\item Multiple hypothesis testing corrected p-values in parentheses
\item "All Three" improvement of 28 \% in record-keeping, 17 \% in planning, 11 \% in stocking, 24 \% in marketing and 22 \% in joint decision making.
\end{itemize}
\end{frame}

\begin{frame}

\frametitle{\centering{Business Profits}}
{\scriptsize{\begin{table}[t]
\centering
%\begin{adjustbox}{width=9cm}
%	\tabcolsep=0.05cm
	\begin{tabular}{l*{5}{c}}
\hline
\hline
			   &&Profits	        &&Profits \\
				&&last month  		&&last month \\
			&&(win 5\%)			&&(IHS) \\
				&&(1)				&&(2)	\\
&& \\
					\hline
&&\\

Assigned Handbook 					&&-91.307   	&& -0.067   		\\
       								 	&&         (78.400)  	&&          (0.088)  	\\

Assigned Handbook \& Movie				&&110.378   	  	&& 0.055   		\\
       									&&         (86.841)  	&&          (0.092)  	\\

Assigned Handbook \& Assistance 	&&         310.455***	&&           0.261***		\\
       								 	&&         (89.488) 	&&          (0.096)  	\\

Assigned All Three          		&&         191.088**  	&&           0.199** 		\\
       								 	&&         (84.662)  	&&          (0.094)  	\\

   	\\
\hline         							
\\
R-squared											  	&& 0.179  	&& 0.211  	\\
Sample Size 											&&2172	&& 2172 	\\
Dependent Variable Mean in Control Group			 	&&          894.544   	&&           6.817 	\\
Dependent Variable SD in Control Group				 	&&         1127.783   	 &&          1.348  	\\
F-tests (p-value):											&&			&&			\\
\hspace{5mm}Book = Book \& Mov				        	&&    0.020   	&&            0.167 	\\
\hspace{5mm}Book = Book \& Assistance				  			&&0.000   	&&0.000  	\\
\hspace{5mm}Book = All Three			   			  	&&0.001   	&&0.003  	\\
\hline
	\end{tabular}
%\end{adjustbox}

\end{table}}}
\begin{itemize}
\item Profits increase by 35\% (about 0.28 sd.) - ITT.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Business Sales}
{\scriptsize{\begin{table}[t]
\centering
%\begin{adjustbox}{width=9cm}
%	\tabcolsep=0.05cm
	\begin{tabular}{l*{5}{c}}
\hline
\hline
                &&ITT	        &&TOT \\
			   &&Sales	        &&Sales \\
				&&last month  		&&last month \\
			&&(win 5\%)			&&(win 5\% \\
				&&(1)				&&(2)	\\
&& \\
					\hline
&&\\

Assigned Handbook 					&&-396.976   	&&               -417.198		\\
       								 	&&        (314.252)   	&&          -417.198	\\

Assigned Handbook \& Movie				&&335.489   	  	&& 601.221    		\\
       									&&       (337.881)  	&&            (606.634)	\\

Assigned Handbook \& Assistance 	&&                   836.755**	&&                     1031.692** 	\\
       								 	&&        (372.924) 	&&            (457.015) 	\\

Assigned All Three         		&&         807.462**  	&&                         1558.326**		\\
       								 	&&        (358.384)  	&&          (696.317)   	\\

   	\\
\hline         							
\\
R-squared											  	&& 0.492  	&&  0.483	\\
Sample Size 											&& 2197	&& 2197 	\\
Dependent Variable Mean in Control Group			 	&&         4998.923   &&	          4998.923 	\\
Dependent Variable SD in Control Group				 	&&         5623.257   	&&           5623.257	\\
F-tests (p-value):											&&			&&			\\
\hspace{5mm}Book = Book \& Mov				        	&&            0.020 	&&           0.047 	\\
\hspace{5mm}Book = Book \& Assistance				  			&&0.000   	&& 0.000 	\\
\hspace{5mm}Book = All Three			   			  	&&0.000   	&&0.001  	\\
\hline
	\end{tabular}
%\end{adjustbox}

\end{table}}}
\begin{itemize}
\item Sales increase by 16\% (about 0.15 sd.) - ITT %- and 31\% (0.28 sd.) - TOT.
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Other Outcomes}
\begin{itemize}
\item \textbf{No significant} impacts on:
    \begin{itemize}
    \vspace{0.2in}
    \item Business expenses
    \vspace{0.2in} 		
    \item Size of the shop
      \vspace{0.2in}
    \item Number of employees
      \vspace{0.2in}
    \item Number of customers
       \vspace{0.2in}
     \item Business credit
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Efficiency Gains?}
\begin{enumerate}
\item Unpacking impacts on practices shows improvements in efficiency practices:
\vspace{0.1in}
\begin{itemize}
\item Adjust stocks based on product profitability
\item Negotiate lower prices with suppliers
\item Consult with former customers
\item Offer discounts
\item Make joint decisions
\item Review financial performance to identify channels of improvement
\item Make anticipated budget for upcoming costs
\end{itemize}
\vspace{0.2in}
\pause
\item These are non-record-keeping practices. Also, variance in profits among the treated businesses does not converge
\vspace{0.2in}
\pause
\item Causal-mediation analysis shows that the most important drivers of impact on sales and profits are stocking up and marketing practices.
\end{enumerate}
\vspace{0.2in}
$\rightarrow$ \textcolor[rgb]{0.00,0.07,1.00}{Efficiency gains}
\end{frame}

\begin{frame}
\frametitle{Knowledge or Aspirations?}
\begin{itemize}
\item Our interventions could have increased business performance and practice adoption through an increase in business aspirations rather than (or on top of) business knowledge.
\vspace{0.2in}
\item We directly measure business aspirations at baseline, midline, and endline for all shop owners in the sample.
\vspace{0.2in}
\item We elicit short (one year) and long-term (ideal) aspirations on various business dimensions:
\vspace{0.1in}
    \begin{itemize}
    \item sales
    \item shop size
    \item number of customers
    \item number of employees
    \end{itemize}
\vspace{0.2in}
\item No treatment effects on aspirations
\vspace{0.2in}
\end{itemize}
$\rightarrow$ \textcolor[rgb]{0.00,0.07,1.00}{Knowledge}
\end{frame}

\begin{frame}
\frametitle{Business Stealing?}
Do treated businesses improve performance at the expense of the control group?
\vspace{0.1in}
\begin{itemize}
\item Shops in Control group \textbf{do not decrease} their sales and profits from baseline to endline. They remain the same.
\vspace{0.1in}
\item Shops in Control group that are closer to the treated shops \textbf{do not suffer bigger losses in sales and profits} than those who are further away.
\end{itemize}
\vspace{0.2in}
$\rightarrow$ \textcolor[rgb]{0.00,0.07,1.00}{No evidence for business stealing}
\end{frame}

\begin{frame}
\frametitle{Cost-Effectiveness}
\begin{itemize}
\item \textbf{Low cost} per firm:
\begin{itemize}
\item Cost Handbook alone: USD 100
\item Cost Handbook \& Movie: USD 125
\item Cost Handbook \& Assistance: USD 125
\item Cost Handbook \& Assistance \& Movie: USD 150
\vspace{0.20in}
\end{itemize}
\item \textbf{High Benefits}
    \begin{itemize}
    \item Up to USD 330 per month in profits.
    \item Adoption of top practices by retailers.
    \end{itemize}
\vspace{0.20in}
 \item Research Design \textbf{scalable and replicable} in other settings.
\end{itemize}
\end{frame}

%--------------------------------------
\begin{frame}
\frametitle{Takeaways}
\begin{itemize}
    \item Curating local knowledge has value for business growth 
            \vspace{0.20in}
    \item Knowledge alone does not have an impact but needs additional help or nudges
            \vspace{0.20in}
	\item These "add-ons" are inexpensive and scalable, making this type of intervention very attractive for policy

\end{itemize}
\end{frame}

\end{document}

### 2021-02-01 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added Bocconi lecture
Added outline of lecture + paper pres

--- 2021-01-31 firms/mgmt/CuratingLocKnowledge_Bocconi_03-2021.tex
@@
 \newenvironment{stepitemizewithalert}{\begin{itemize}[<+-| alert@+>]}{\end{itemize} }
-\usetheme{Boadilla}
+
+%\usetheme{Boadilla}
+\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
+\usetheme[right]{Berkeley}
+\setbeamercolor{sidebar}{bg=blue}
 
@@
 
-%------------------------------------------------
-%	PRESENTATION BASICS
-%------------------------------------------------
+\title[Skills, Practices, and Aspirations of Small Firms in LMICs]{Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings}
+\author[R{\"u}schenp{\"o}hler]{Julius R{\"u}schenp{\"o}hler\inst{*}}
+\institute[]{\inst{*} UC Berkeley, CEGA}
+\date{March 04, 2021}
+
+\begin{document}
+
+\setbeamertemplate{sidebar right}{}
+
+\begin{frame}
+\titlepage
+\end{frame}
+
+\setbeamertemplate{sidebar right}[sidebar theme]
+
+%\begin{frame}
+%\frametitle{Overview of the Lecture}
+%\tableofcontents[hideallsubsections]
+%\end{frame}
+
+\AtBeginSection
+{\begin{frame}{Overview}
+\tableofcontents[currentsection,hideothersubsections]
+\end{frame}}
+
+%\begin{document}
+
+\section{\textbf{PART I: Lecture} \\ \quad \emph{Business Practices}}
+
+\subsection{Business Practices Around the World}
+
+\begin{frame}
+\frametitle{?}
+	\begin{itemize}
+	\item Bloom and van Reenen (2010): Business practices, motivation
+	\vspace{0.2in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Heterogeneity in Business Practices}
+	\begin{itemize}
+	\item Bloom and van Reenen (2010): Heterogeneity
+	\vspace{0.2in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Value-Added of Business Practices}
+	\begin{itemize}
+	\item Bloom and van Reenen (2010): Correlation with productivity
+	\vspace{0.2in}
+	\end{itemize}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
+\frametitle{Business Practices of Small Firms}
+	\begin{itemize}
+	\item McKenzie and Woodruff (2017): Heterogeneity and predictiveness
+	\vspace{0.2in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Business Practices of Small Firms}
+	\begin{itemize}
+	\item McKenzie and Woodruff (2017): Example categories and practices
+	\vspace{0.2in}
+	\end{itemize}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
+\frametitle{Best Practices for Small Firms}
+	\begin{itemize}
+	\item McKenzie and Woodruff (2017): Portable best practices
+	\vspace{0.2in}
+	\end{itemize}
+\end{frame}
+
+\subsection{Classical MSME Training}
+
+\begin{frame}
+\frametitle{History and Prevalence}
+	\begin{itemize}
+	\item At least \textcolor{red}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
+	\vspace{0.1in}
+	\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
+	\vspace{0.2in}
+	\item Examples: Start and Improve Your Business (ILO), Business Edge (IFC), \textcolor{red}{ELSE??}
+	\item 
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+%----------------------
+
+\begin{frame}
+\frametitle{Typical Training Program}
+	\begin{itemize}
+	\item Content %\textcolor{}{}
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Typical Training Program}
+	\begin{itemize}
+	\item Delivery %\textcolor{}{}
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
+\frametitle{Impact on Businesses}
+	\begin{itemize}
+	\item First wave (Karlan and Valdivia, 2011, etc.)
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Impact on Businesses}
+	\begin{itemize}
+	\item Econometric and implementation issues (McKenzie and Woodruff, 2014)
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Impact on Businesses}
+	\begin{itemize}
+	\item Recent evaluations (McKenzie, 2020)
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\subsection{Extensions of the Classical Approach}
+
+\begin{frame}
+\frametitle{Targeted Training}
+	\begin{itemize}
+	\item Female entrepreneurs
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Targeted Training}
+	\begin{itemize}
+	\item Young entrepreneurs
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Targeted Training}
+	\begin{itemize}
+	\item Gazelles
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
+\frametitle{On-site Consulting}
+	\begin{itemize}
+	\item ?
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{On-site Consulting}
+	\begin{itemize}
+	\item ?
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
+\frametitle{Complementary Constraints}
+	\begin{itemize}
+	\item McKenzie cash paper
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Complementary Constraints}
+	\begin{itemize}
+	\item McKenzie cash paper
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\subsection{Measurement of Firm Performance}
+
+\begin{frame}
+\frametitle{Imprecision of Outcome Measures}
+	\begin{itemize}
+	\item Confidence Intervals, pic?
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Reliability of Self-reports}
+	\begin{itemize}
+	\item Self-reports of aggregate
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Reliability of Self-reports}
+	\begin{itemize}
+	\item Disaggregating quantities in self-reports
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Reliability of Self-report}
+	\begin{itemize}
+	\item Direct measures
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
+\frametitle{Sales vs. Profits}
+	\begin{itemize}
+	\item 
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Sales vs. Profits}
+	\begin{itemize}
+	\item 
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+% ---------------------
+
+\begin{frame}
+\frametitle{?}
+	\begin{itemize}
+	\item 
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{?}
+	\begin{itemize}
+	\item 
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\subsection{Mechanisms}
+
+\begin{frame}
+\frametitle{Heterogeneity of Impact}
+	\begin{itemize}
+	\item Heterogeneity of treatment effect poorly understood across different approaches
+	\item Potential constraints are manifold, and likely context-dependent
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Education}
+	\begin{itemize}
+	\item 
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Family Commitments}
+	\begin{itemize}
+	\item 
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Identity Concerns}
+	\begin{itemize}
+	\item 
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Aspirations}
+	\begin{itemize}
+	\item 
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Local Relevance of Best Practices}
+	\begin{itemize}
+	\item 
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\subsection{Alternative Approaches}
+
+\begin{frame}
+\frametitle{Local Knowledge}
+	\begin{itemize}
+	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Local Knowledge}
+	\begin{itemize}
+	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Local Knowledge}
+	\begin{itemize}
+	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
+\frametitle{Role Models}
+	\begin{itemize}
+	\item La Ferrara!
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Role Models}
+	\begin{itemize}
+	\item La Ferrara!
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Role Models}
+	\begin{itemize}
+	\item La Ferrara!
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+%\setbeamertemplate{sidebar right}{}
+\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
+
+\subsection{Takeaways}
+
+\begin{frame}
+\frametitle{Takeaways}
+	\begin{itemize}
+    \item
+   	\vspace{0.10in}
+\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Questions}
+	\begin{itemize}
+	\item Any questions?
+	\vspace{0.2in}
+	\item[] .. before we move on to our paper?
+	\end{itemize}
+\end{frame}
+
+%-----------------------------------------------------------
+%------------------------------------------------------------
+%------------------------------------------------------------
+%------------------------------------------------------------
+%------------------------------------------------------------
+
+\addtocontents{toc}{\protect\setcounter{tocdepth}{99}}
 
@@
 \author[Dalton, R{\"u}schenp{\"o}hler, Uras, and Zia]
-{
-Patricio S. Dalton\inst{1}\
+{Patricio S. Dalton\inst{1}\
 Julius R{\"u}schenp{\"o}hler\inst{2}
 Burak Uras\inst{1}\\and
-Bilal Zia\inst{3}
-}
+Bilal Zia\inst{3}}
 
-\institute[]
-{
+\institute[]{
 \inst{1} Tilburg University\\
@@
 \bigskip
-\inst{3} The World Bank\\
-}
+\inst{3} The World Bank}
 
@@
 
-\title[Curating Local Knowledge]{Curating Local Knowledge}
-\subtitle{Experimental Evidence from Small Retailers in Indonesia}
+%\setbeamertemplate{sidebar right}{}
 
-\author[Dalton, R{\"u}schenp{\"o}hler, Uras, and Zia]
-{
-Patricio S. Dalton\inst{1}\
-Julius R{\"u}schenp{\"o}hler\inst{2}
-Burak Uras\inst{1}\\and
-Bilal Zia\inst{3}
-}
-
-\institute[]
-{
-\inst{1} Tilburg University\\
-\bigskip
-\inst{2} CEGA, UC Berkeley\\
-\bigskip
-\inst{3} The World Bank\\
-}
-
-\date{March 04, 2021}
-
-%------------------------------------------------
-%	PRESENTATION SLIDES
-%------------------------------------------------
-
-\begin{document}
+\section{\textbf{PART II: Paper} \\ \quad \emph{Curating Local Knowledge}}
 
@@
 
-%\begin{frame}
-%\frametitle{Overview}
-%\tableofcontents[hideallsubsections]
-%\end{frame}
+\setbeamertemplate{sidebar right}[sidebar theme]
 

### 2021-02-01 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added details to color scheme, sidebar, paper pres, role models

@@
-\documentclass[10pt]{beamer}
+\documentclass[hideothersubsections, usenames,dvipsnames,10pt]{beamer}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%\usetheme{Boadilla}
-\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
+% Color scheme and sidebar
+\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}
+\definecolor{bleudefrance}{rgb}{0.19, 0.55, 0.91}
+\definecolor{bluemunsell}{rgb}{0.0, 0.5, 0.69}
+%#09BADB #DB1A71
 \usetheme[right]{Berkeley}
-\setbeamercolor{sidebar}{bg=blue}
+\setbeamercolor{palette primary}{bg=ceruleanblue,fg=white}
+\setbeamercolor{palette secondary}{bg=bleudefrance,fg=white}
+%\setbeamercolor{sidebar}{bg=bleudefrance}
+
+% Mini frames
+%\useoutertheme[subsection=true]{miniframes}
 
@@
 
-\title[Skills, Practices, and Aspirations of Small Firms in LMICs]{Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings}
-\author[R{\"u}schenp{\"o}hler]{Julius R{\"u}schenp{\"o}hler\inst{*}}
+\title[]{Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings}
+\author[]{Julius R{\"u}schenp{\"o}hler\inst{*}}
 \institute[]{\inst{*} UC Berkeley, CEGA}
@@
 
+% Create generic TOC
+
+%\AtBeginSection
+%{\begin{frame}{Overview}
+%\tableofcontents[currentsection,hideothersubsections]
+%\end{frame}}
+
+\section{\textbf{PART I: Lecture} \\ \quad \emph{Business Practices}}
+
 \setbeamertemplate{sidebar right}{}
@@
 
-%\begin{frame}
-%\frametitle{Overview of the Lecture}
-%\tableofcontents[hideallsubsections]
-%\end{frame}
-
-\AtBeginSection
-{\begin{frame}{Overview}
+\begin{frame}{Lecture Overview}
 \tableofcontents[currentsection,hideothersubsections]
-\end{frame}}
-
-%\begin{document}
-
-\section{\textbf{PART I: Lecture} \\ \quad \emph{Business Practices}}
+\end{frame}
 
@@
 	\begin{itemize}
-	\item Bloom and van Reenen (2010): Business practices, motivation
+	\item Bloom and van Reenen (2010, 2019): Business practices, motivation
 	\vspace{0.2in}
@@
 	\begin{itemize}
-	\item Bloom and van Reenen (2010): Correlation with productivity
+	\item Bloom and van Reenen (2019): Correlation with productivity
 	\vspace{0.2in}
@@
 	\begin{itemize}
-	\item McKenzie and Woodruff (2017): Heterogeneity and predictiveness
+	\item McKenzie and Woodruff (2009, 2017): Heterogeneity and predictiveness
 	\vspace{0.2in}
@@
 	\begin{itemize}
-	\item McKenzie and Woodruff (2017): Example categories and practices
+	\item McKenzie and Woodruff (2009, 2017): Example categories and practices
 	\vspace{0.2in}
@@
 	\begin{itemize}
-	\item At least \textcolor{red}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
+	\item At least \textcolor{bleudefrance}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
 	\vspace{0.1in}
@@
 	\begin{itemize}
-	\item First wave (Karlan and Valdivia, 2011, etc.)
+	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
 	\vspace{0.1in}
@@
 	\begin{itemize}
+	\item Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{On-site Consulting}
+	\begin{itemize}
 	\item ?
@@
 
-\begin{frame}
-\frametitle{On-site Consulting}
-	\begin{itemize}
-	\item ?
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
 %---------------------
@@
 	\begin{itemize}
-	\item McKenzie cash paper
+	\item McKenzie cash JDE paper
 	\vspace{0.1in}
@@
 	\begin{itemize}
+	\item Drexler, Fischer \& Schoar (2014)
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Family Commitments}
+	\begin{itemize}
 	\item 
@@
 \begin{frame}
-\frametitle{Family Commitments}
+\frametitle{Identity Concerns}
 	\begin{itemize}
@@
 \begin{frame}
-\frametitle{Identity Concerns}
+\frametitle{Aspirations}
 	\begin{itemize}
@@
 \begin{frame}
-\frametitle{Aspirations}
+\frametitle{Local Relevance of Best Practices}
 	\begin{itemize}
@@
 
-\begin{frame}
-\frametitle{Local Relevance of Best Practices}
+\subsection{Alternative Approaches}
+
+\begin{frame}
+\frametitle{Rules of Thumb}
+	\begin{itemize}
+	\item Drexler, Fischer \& Schoar (2014)
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
+\begin{frame}
+\frametitle{Rules of Thumb}
 	\begin{itemize}
@@
 
-\subsection{Alternative Approaches}
+%---------------------
 
@@
 	\begin{itemize}
-	\item La Ferrara!
+	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
 	\vspace{0.1in}
@@
 	\begin{itemize}
-	\item La Ferrara!
+	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018
 	\vspace{0.1in}
@@
 	\begin{itemize}
-	\item La Ferrara!
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-%\setbeamertemplate{sidebar right}{}
+	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
+	\vspace{0.1in}
+	\end{itemize}
+\end{frame}
+
 \addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
@@
 
-\title[Curating Local Knowledge]{Curating Local Knowledge}
+\title[]{Curating Local Knowledge}
 \subtitle{Experimental Evidence from Small Retailers in Indonesia}
 
-\author[Dalton, R{\"u}schenp{\"o}hler, Uras, and Zia]
+\author[]
 {Patricio S. Dalton\inst{1}\
@@
 \bigskip
-\inst{2} CEGA, UC Berkeley\\
+\inst{2} UC Berkeley, CEGA\\
 \bigskip
@@
 
-%\setbeamertemplate{sidebar right}{}
-
 \section{\textbf{PART II: Paper} \\ \quad \emph{Curating Local Knowledge}}
 
+\setbeamertemplate{sidebar right}{}
+
 \begin{frame}
@@
 
+\begin{frame}{Paper Overview}
+\tableofcontents[currentsection,hideothersubsections]
+\end{frame}
+
 %------------------------------------------------
-\section{Background}
+\subsection{Motivation}
 
@@
 \item \textbf{Classroom Training}: Field, et al.
-(2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); Drexler, Fischer \& Schoar (2014); McKenzie \& Woodruff (2014, 2017); Bulte et al.
+(2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); McKenzie \& Woodruff (2014, 2017); Bulte et al.
 (2017); Anderson, Chandy \& Zia (2018); Lafortune et al.
@@
 
-\begin{frame}
-\frametitle{What We Do}
+\subsection{Our Approach}
+\begin{frame}
+\frametitle{Harnessing Cross-Firm Heterogeneity}
 \begin{itemize}
@@
 \begin{frame}
-\frametitle{How Do We Share this Knowledge?}
+\frametitle{Disseminating Knowledge}
 		\begin{itemize}
@@
 \bigskip
-		\item \textbf{In-shop Light Assistance}
+		\item \textbf{In-shop Assistance}
 			\begin{itemize}
 			\item \textcolor[rgb]{0.00,0.07,1.00}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textbf{experience, with a small nudge} (Kolb, 1984).
+			\item Facilitated by local lay person
 			\end{itemize}
@@
 \end{frame}
+
+\subsection{Data and Design}
 
@@
 
-\section{Data and Analysis}
+\subsection{Results}
 
@@
 
+\subsection{Discussion}
 \begin{frame}
@@
 \vspace{0.20in}
- \item Research Design \textbf{scalable and replicable} in other settings.
-\end{itemize}
-\end{frame}
-
-%--------------------------------------
+ \item Research Design likely \textbf{scalable and replicable} in other settings.
+\end{itemize}
+\end{frame}
+
+\subsection{Conclusion}
 \begin{frame}
@@
             \vspace{0.20in}
-    \item Knowledge alone does not have an impact but needs additional help or nudges
+    \item Information alone does not have impact, but behavioral interventions are needed
             \vspace{0.20in}
@@
 
+%\bibliographystyle{econometrica}
+%\bibliography{sampleBibFile}
+
 \end{document}

### 2021-02-02 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Aesthetics

@@
 \newenvironment{stepitemizewithalert}{\begin{itemize}[<+-| alert@+>]}{\end{itemize} }
-
-% Color scheme and sidebar
-\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}
-\definecolor{bleudefrance}{rgb}{0.19, 0.55, 0.91}
-\definecolor{bluemunsell}{rgb}{0.0, 0.5, 0.69}
+\newenvironment{itemize_3pt}{\itemize\addtolength{\itemsep}{3pt}}{\enditemize}
+\newenvironment{enumerate_3pt}{\enumerate\addtolength{\itemsep}{3pt}}{\endenumerate}
+
+% Font
+\usefonttheme{serif}
+\setbeamercovered{invisible}
+
+% Color scheme
+\definecolor{cerulean}{rgb}{0.16, 0.32, 0.75}
+\definecolor{bdf}{rgb}{0.19, 0.55, 0.91}
+\definecolor{offwhite}{RGB}{255,253,238}
+\definecolor{red}{RGB}{213,94,0}
 %#09BADB #DB1A71
+
 \usetheme[right]{Berkeley}
-\setbeamercolor{palette primary}{bg=ceruleanblue,fg=white}
-\setbeamercolor{palette secondary}{bg=bleudefrance,fg=white}
-%\setbeamercolor{sidebar}{bg=bleudefrance}
+\setbeamercolor{background canvas}{bg=offwhite}
+\setbeamercolor{palette primary}{bg=cerulean,fg=white}
+\setbeamercolor{palette secondary}{bg=bdf,fg=white}
+\setbeamercolor{frametitle}{fg=offwhite}
+%\setbeamercolor{sidebar}{bg=cerulean}
+
+%\newenvironment{transitionframe}{\setbeamercolor{background canvas}{bg=bdf}\begin{frame}}{\end{frame}}
+%\setbeamercolor{title}{fg=black}
+%\setbeamercolor{itemize item}{fg=blue}
+%\setbeamercolor{itemize subitem}{fg=blue}
+%\setbeamercolor{enumerate item}{fg=blue}
+%\setbeamercolor{enumerate subitem}{fg=blue}
+%\setbeamercolor{button}{bg=offwhite,fg=blue}
+
+\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
+\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
+%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}
+
+% Page number and navigation
+\setbeamerfont{page number in head/foot}{size=\small}
+%\setbeamertemplate{footline}[frame number]
+\setbeamertemplate{navigation symbols}{}
+
+\addtobeamertemplate{footline}
+{%
+   \usebeamercolor[fg]{author in sidebar}
+   \vskip-1cm\hskip8pt
+   \insertframenumber\,/\,\inserttotalframenumber\kern1em\vskip4pt%
+}
 
@@
 
-\usefonttheme{serif}
-\setbeamercovered{invisible}
-
 \title[]{Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings}
-\author[]{Julius R{\"u}schenp{\"o}hler\inst{*}}
-\institute[]{\inst{*} UC Berkeley, CEGA}
+\author[]{Julius R{\"u}schenp{\"o}hler\inst{}}
+\institute[]{\inst{} UC Berkeley, CEGA}
 \date{March 04, 2021}
@@
 \frametitle{?}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item Bloom and van Reenen (2010, 2019): Business practices, motivation
-	\vspace{0.2in}
-	\end{itemize}
+	\vspace{0.1in}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Heterogeneity in Business Practices}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item Bloom and van Reenen (2010): Heterogeneity
-	\vspace{0.2in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Value-Added of Business Practices}
-	\begin{itemize}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{}
+	\begin{itemize_3pt}
 	\item Bloom and van Reenen (2019): Correlation with productivity
-	\vspace{0.2in}
-	\end{itemize}
+	\vspace{0.1in}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Business Practices of Small Firms}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item McKenzie and Woodruff (2009, 2017): Heterogeneity and predictiveness
-	\vspace{0.2in}
-	\end{itemize}
+	\vspace{0.1in}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Business Practices of Small Firms}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item McKenzie and Woodruff (2009, 2017): Example categories and practices
-	\vspace{0.2in}
-	\end{itemize}
+	\vspace{0.1in}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Best Practices for Small Firms}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item McKenzie and Woodruff (2017): Portable best practices
-	\vspace{0.2in}
-	\end{itemize}
+	\vspace{0.1in}
+	\end{itemize_3pt}
 \end{frame}
@@
 
+%\begin{frame}
+%\begin{center}
+%{ \Huge \textcolor{black}{Classical MSME Training}}
+%\end{center}
+%\end{frame}
+
 \begin{frame}
 \frametitle{History and Prevalence}
-	\begin{itemize}
-	\item At least \textcolor{bleudefrance}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
-	\vspace{0.1in}
+	\begin{itemize_3pt}
+		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
 		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
-	\vspace{0.2in}
-	\item Examples: Start and Improve Your Business (ILO), Business Edge (IFC), \textcolor{red}{ELSE??}
+		\vspace{0.1in}
+		\item Examples:
+		\begin{itemize_3pt}
+			\item Start and Improve Your Business (ILO)
+			\item Business Edge (IFC)
+			\item EMPRETEC Entrepreneurship Training Workshop (UNCTAD)
+		\end{itemize_3pt} 
+	\end{itemize_3pt}
+\end{frame}
+
+%----------------------
+
+\begin{frame}
+\frametitle{Typical Training Program}
+	\begin{itemize_3pt}
+	\item Content %\textcolor{}{}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Typical Training Program}
+	\begin{itemize_3pt}
+	\item Delivery %\textcolor{}{}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
+\frametitle{Impact on Businesses}
+	\begin{itemize_3pt}
+	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Impact on Businesses}
+	\begin{itemize_3pt}
+	\item Econometric and implementation issues (McKenzie and Woodruff, 2014)
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Impact on Businesses}
+	\begin{itemize_3pt}
+	\item Recent evaluations (McKenzie, 2020)
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\subsection{Extensions of the Classical Approach}
+
+\begin{frame}
+\frametitle{Targeted Training}
+	\begin{itemize_3pt}
+	\item Female entrepreneurs
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Targeted Training}
+	\begin{itemize_3pt}
+	\item Young entrepreneurs
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Targeted Training}
+	\begin{itemize_3pt}
+	\item Gazelles
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
+\frametitle{On-site Consulting}
+	\begin{itemize_3pt}
+	\item Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{On-site Consulting}
+	\begin{itemize_3pt}
+	\item ?
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
+\frametitle{Complementary Constraints}
+	\begin{itemize_3pt}
+	\item McKenzie cash JDE paper
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Complementary Constraints}
+	\begin{itemize_3pt}
+	\item McKenzie cash JDE paper
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\subsection{Measurement of Firm Performance}
+
+\begin{frame}
+\frametitle{Imprecision of Outcome Measures}
+	\begin{itemize_3pt}
+	\item Confidence Intervals, pic?
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Reliability of Self-reports}
+	\begin{itemize_3pt}
+	\item Self-reports of aggregate
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Reliability of Self-reports}
+	\begin{itemize_3pt}
+	\item Disaggregating quantities in self-reports
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Reliability of Self-report}
+	\begin{itemize_3pt}
+	\item Direct measures
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
+\frametitle{Sales vs. Profits}
+	\begin{itemize_3pt}
 	\item 
 	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-%----------------------
-
-\begin{frame}
-\frametitle{Typical Training Program}
-	\begin{itemize}
-	\item Content %\textcolor{}{}
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Typical Training Program}
-	\begin{itemize}
-	\item Delivery %\textcolor{}{}
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-%---------------------
-
-\begin{frame}
-\frametitle{Impact on Businesses}
-	\begin{itemize}
-	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Impact on Businesses}
-	\begin{itemize}
-	\item Econometric and implementation issues (McKenzie and Woodruff, 2014)
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Impact on Businesses}
-	\begin{itemize}
-	\item Recent evaluations (McKenzie, 2020)
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\subsection{Extensions of the Classical Approach}
-
-\begin{frame}
-\frametitle{Targeted Training}
-	\begin{itemize}
-	\item Female entrepreneurs
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Targeted Training}
-	\begin{itemize}
-	\item Young entrepreneurs
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Targeted Training}
-	\begin{itemize}
-	\item Gazelles
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-%---------------------
-
-\begin{frame}
-\frametitle{On-site Consulting}
-	\begin{itemize}
-	\item Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{On-site Consulting}
-	\begin{itemize}
-	\item ?
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-%---------------------
-
-\begin{frame}
-\frametitle{Complementary Constraints}
-	\begin{itemize}
-	\item McKenzie cash JDE paper
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Complementary Constraints}
-	\begin{itemize}
-	\item McKenzie cash JDE paper
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\subsection{Measurement of Firm Performance}
-
-\begin{frame}
-\frametitle{Imprecision of Outcome Measures}
-	\begin{itemize}
-	\item Confidence Intervals, pic?
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Reliability of Self-reports}
-	\begin{itemize}
-	\item Self-reports of aggregate
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Reliability of Self-reports}
-	\begin{itemize}
-	\item Disaggregating quantities in self-reports
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Reliability of Self-report}
-	\begin{itemize}
-	\item Direct measures
-	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-%---------------------
+	\end{itemize_3pt}
+\end{frame}
 
@@
 \frametitle{Sales vs. Profits}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item 
 	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Sales vs. Profits}
-	\begin{itemize}
+	\end{itemize_3pt}
+\end{frame}
+
+% ---------------------
+
+\begin{frame}
+\frametitle{?}
+	\begin{itemize_3pt}
 	\item 
 	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-% ---------------------
+	\end{itemize_3pt}
+\end{frame}
 
@@
 \frametitle{?}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item 
 	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{?}
-	\begin{itemize}
-	\item 
-	\vspace{0.1in}
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Heterogeneity of Impact}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item Heterogeneity of treatment effect poorly understood across different approaches
@@
 	\vspace{0.1in}
-	\end{itemize}
-\end{frame}
-
-\begin{frame}
-\frametitle{Education}
-	\begin{itemize}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Education and literacy}
+	\begin{itemize_3pt}
 	\item Drexler, Fischer \& Schoar (2014)
 	\vspace{0.1in}
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Family Commitments}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item 
 	\vspace{0.1in}
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Identity Concerns}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item 
 	\vspace{0.1in}
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Aspirations}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item 
 	\vspace{0.1in}
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Local Relevance of Best Practices}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item 
 	\vspace{0.1in}
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Rules of Thumb}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item Drexler, Fischer \& Schoar (2014)
 	\vspace{0.1in}
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Rules of Thumb}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item 
 	\vspace{0.1in}
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Local Knowledge}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
 	\vspace{0.1in}
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Role Models}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
 	\vspace{0.1in}
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Role Models}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018
 	\vspace{0.1in}
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Takeaways}
-	\begin{itemize}
+	\begin{itemize_3pt}
     \item
    	\vspace{0.10in}
-\end{itemize}
+\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Questions}
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item Any questions?
-	\vspace{0.2in}
+	\vspace{0.1in}
 	\item[] .. before we move on to our paper?
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Background}
-	\begin{itemize}
-	\item Micro \& Small firms (MSEs) main \textbf{source of employment} in the developing world
-	\vspace{0.2in}
-	\item In \textbf{Indonesia}, MSEs represent 99\% of all firms and 94.5\% of employment 
-	\vspace{0.2in}
+	\begin{itemize_3pt}
+	\item Micro \& Small firms (MSEs) main \textcolor{bdf}{source of employment} in the developing world
+	\vspace{0.1in}
+	\item In \textcolor{bdf}{Indonesia}, MSEs represent 99\% of all firms and 94.5\% of employment 
+	\vspace{0.1in}
 	\item Understanding the factors fostering efficiency and growth of MSEs is an important research and policy goal
-	\end{itemize}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{A Growing Focus on Management}
-\begin{itemize}
-\item \textbf{Classroom Training}: Field, et al.
+\begin{itemize_3pt}
+\item \textcolor{bdf}{Classroom Training}: Field, et al.
 (2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); McKenzie \& Woodruff (2014, 2017); Bulte et al.
@@
 (2018)
-\vspace{0.2in}
-\item \textbf{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
-\vspace{0.2in}
-
-\item \textbf{Mobilizing Peer Knowledge}:
-    \begin{itemize}
+\vspace{0.1in}
+\item \textcolor{bdf}{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
+\vspace{0.1in}
+
+\item \textcolor{bdf}{Mobilizing Peer Knowledge}:
+    \begin{itemize_3pt}
     \item Brooks et al. (2018) $\rightarrow$ Local mentors (market information)
@@
     \item Abebe et al. (2019) $\rightarrow$ Management experience matching
-    \end{itemize}
-    \vspace{0.2in}
-\end{itemize}
+    \end{itemize_3pt}
+    \vspace{0.1in}
+\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Harnessing Cross-Firm Heterogeneity}
-\begin{itemize}
+\begin{itemize_3pt}
 \item Some facts about business practices in firms:
-	\begin{itemize}	
+	\begin{itemize_3pt}	
 	\item Vast heterogeneity in business practices and performance across similar businesses (de Mel, McKenzie \& Woodruff, 2009)
 	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US (Bloom et al, 2019)
-	\end{itemize}
-\vspace{0.2in}
+	\end{itemize_3pt}
+\vspace{0.1in}
 \pause
 \item Research thus far has mostly overlooked this underlying heterogeneity in design and implementation of programs
-\vspace{0.2in}
+\vspace{0.1in}
 \pause
-\item Our idea is to make it \textbf{central} to the research design: 
-	\begin{itemize}
+\item Our idea is to make it \textcolor{bdf}{central} to the research design: 
+	\begin{itemize_3pt}
 	\item Use variation across businesses to identify business practices associated with successful performance
@@
 	\item Test different communication channels and their cost-effectiveness
-\end{itemize}
-\end{itemize}
+\end{itemize_3pt}
+\end{itemize_3pt}
 
@@
 \frametitle{Selecting Local Best Practices}
-\begin{itemize}
-\item Detailed \textcolor[rgb]{0.00,0.07,1.00}{qualitative interviews} with local business peers:
-    \begin{itemize}
+\begin{itemize_3pt}
+\item Detailed \textcolor{bdf}{qualitative interviews} with local business peers:
+    \begin{itemize_3pt}
     \item Understand and codify their practices (record-keeping, financial planning, stocking-up, marketing, and joint decision-making)
@@
     \item Document locally relevant tips and rule of thumbs
-    \end{itemize}
-\vspace{0.2in}
-\item Baseline \textcolor[rgb]{0.00,0.07,1.00}{quantitative survey}
-    \begin{itemize}
+    \end{itemize_3pt}
+\vspace{0.1in}
+\item Baseline \textcolor{bdf}{quantitative survey}
+    \begin{itemize_3pt}
     \item Measure practices and outcomes
     \item Quantitative association of business practices with profits and sales
-    \end{itemize}
-\end{itemize}
+    \end{itemize_3pt}
+\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Disseminating Knowledge}
-		\begin{itemize}
-		\item \textbf{Handbook}
-			\begin{itemize}
-			\item \textcolor[rgb]{0.00,0.07,1.00}{Pure information}: Which practices, how to adopt, and why?\\
-            %\item \textbf{Positive Frame}: Retailers who implement [x] report y\% \textbf{higher} sales and z\% \textbf{higher} profits.
-            %\item \textbf{Negative Frame}: Retailers who do \textbf{not} implement [x] report y\% \textbf{lower} sales and z\% \textbf{lower} profits.
-			\end{itemize}
+		\begin{itemize_3pt}
+		\item \textcolor{bdf}{Handbook}
+			\begin{itemize_3pt}
+			\item \textcolor{bdf}{Pure information}: Which practices, how to adopt, and why?\\
+            %\item \textcolor{bdf}{Positive Frame}: Retailers who implement [x] report y\% \textcolor{bdf}{higher} sales and z\% \textcolor{bdf}{higher} profits.
+            %\item \textcolor{bdf}{Negative Frame}: Retailers who do \textcolor{bdf}{not} implement [x] report y\% \textcolor{bdf}{lower} sales and z\% \textcolor{bdf}{lower} profits.
+			\end{itemize_3pt}
 \bigskip
@@
 \bigskip
-		\item \textbf{Movie}
-			\begin{itemize}
-			\item \textcolor[rgb]{0.00,0.07,1.00}{Psychological and emotional involvement}$\rightarrow$ social learning is possible through \textbf{observing the successful experience of similar others}.
+		\item \textcolor{bdf}{Movie}
+			\begin{itemize_3pt}
+			\item \textcolor{bdf}{Psychological and emotional involvement}$\rightarrow$ social learning is possible through \textcolor{bdf}{observing the successful experience of similar others}.
 			\item Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013).\\
-			\end{itemize}
+			\end{itemize_3pt}
 
 \bigskip
-		\item \textbf{In-shop Assistance}
-			\begin{itemize}
-			\item \textcolor[rgb]{0.00,0.07,1.00}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textbf{experience, with a small nudge} (Kolb, 1984).
+		\item \textcolor{bdf}{On-site Assistance}
+			\begin{itemize_3pt}
+			\item \textcolor{bdf}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textcolor{bdf}{experience, with a small nudge} (Kolb, 1984).
 			\item Facilitated by local lay person
-			\end{itemize}
+			\end{itemize_3pt}
 			\vspace{0.05in}
@@
 %			$\rightarrow$ Horse race between role models and business counseling.
-		\end{itemize}
+		\end{itemize_3pt}
 
@@
 \frametitle{Research Questions}
-	\begin{itemize}
-	%\item \textbf{Local characterization}
+	\begin{itemize_3pt}
+	%\item \textcolor{bdf}{Local characterization}
 	%\vspace{0.05in}
-	%	\begin{itemize}
+	%	\begin{itemize_3pt}
 	%	\item Which practices are associated with high profits?
 	%	\item How do successful businesses implement them?
-	%	\end{itemize}
+	%	\end{itemize_3pt}
 	%\vspace{0.05in}
-	\item \textbf{Adoption}
-		\begin{itemize}
+	\item \textcolor{bdf}{Adoption}
+		\begin{itemize_3pt}
 		\item Do retailers adopt these practices once peer best practices are aggregated and made common knowledge?
 		\item If so, ...
-			\begin{itemize}
+			\begin{itemize_3pt}
 			\item Does the type of experiential involvement matter?
-			\end{itemize}
-		\end{itemize}
+			\end{itemize_3pt}
+		\end{itemize_3pt}
     \vspace{0.3in}
-	\item \textbf{Impact}
-		\begin{itemize}
+	\item \textcolor{bdf}{Impact}
+		\begin{itemize_3pt}
 		\item Does firm profitability increase?
 		\item If so, what are the channels?
-		\end{itemize}
-	\end{itemize}
+		\end{itemize_3pt}
+	\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Sample}
-\begin{itemize}
+\begin{itemize_3pt}
 \item Listing of 2042 small retail businesses from 29 administrative communities (Kelurahan) in urban Jakarta
 \item Selection criteria for firm listing:
-	\begin{itemize}
+	\begin{itemize_3pt}
 %	\item General willingness to grow
@@
 	\item At least 30 meters distance to next business in sample $\rightarrow$ to minimize spillovers
-	\end{itemize}
+	\end{itemize_3pt}
 \item Random sample of 1301 from the list
 \item Randomization to treatment arms stratified by
-	\begin{itemize}
+	\begin{itemize_3pt}
 	\item Gender
@@
 	\item Kelurahan
-	\end{itemize}
-\end{itemize}
+	\end{itemize_3pt}
+\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Experimental Design}
-	\begin{itemize}
-%    \item \textbf{Same set of business practices} across treatments \\
+	\begin{itemize_3pt}
+%    \item \textcolor{bdf}{Same set of business practices} across treatments \\
 	\item Three types of information provision:
 	\vspace{0.05in}
-		\begin{itemize}
-		\item \textcolor[rgb]{0.00,0.07,1.00}{Handbook} with best practices and tips
+		\begin{itemize_3pt}
+		\item \textcolor{bdf}{Handbook} with best practices and tips
+		\item \textcolor{bdf}{Movie} with successful peers
+		\item Best-practice on-site implementation \textcolor{bdf}{assistance}
+		\end{itemize_3pt}
 	\vspace{0.05in}
-		\item \textcolor[rgb]{0.00,0.07,1.00}{Movie} with successful peers
-		\vspace{0.05in}
-		\item Business practice implementation \textcolor[rgb]{0.00,0.07,1.00}{assistance}
-		\end{itemize}
-	\vspace{0.05in}
-\end{itemize}
-	\begin{itemize}
+\end{itemize_3pt}
+	\begin{itemize_3pt}
 \item{Five experimental groups}
-        %\begin{itemize}
+        %\begin{itemize_3pt}
         %\item{Handbooks (N=1040)}
@@
 	\vspace{0.05in}
-            \begin{enumerate}
-              \item \textcolor[rgb]{0.00,0.07,1.00}{Handbook} only (N=260)
-              \item \textcolor[rgb]{0.00,0.07,1.00}{Handbook} and invitation to \textcolor[rgb]{0.00,0.07,1.00}{movie} screening (N=260)
-              \item \textcolor[rgb]{0.00,0.07,1.00}{Handbook} and offer of two \textcolor[rgb]{0.00,0.07,1.00}{assistance} visits (N=260)
-              \item \textcolor[rgb]{0.00,0.07,1.00}{Handbook} and both \textcolor[rgb]{0.00,0.07,1.00}{movie} and \textcolor[rgb]{0.00,0.07,1.00}{assistance} (N=260)
+            \begin{enumerate_3pt}
+              \item \textcolor{bdf}{Handbook} only (N=260)
+              \item \textcolor{bdf}{Handbook} and invitation to \textcolor{bdf}{movie} screening (N=260)
+              \item \textcolor{bdf}{Handbook} and offer of two \textcolor{bdf}{assistance} visits (N=260)
+              \item \textcolor{bdf}{Handbook} and both \textcolor{bdf}{movie} and \textcolor{bdf}{assistance} (N=260)
               \item Control (N=261)
-            \end{enumerate}
-        \end{itemize}
-    %\end{itemize}
+            \end{enumerate_3pt}
+        \end{itemize_3pt}
+    %\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Timeline}
-\begin{enumerate}
-    \item September 2015: \textcolor[rgb]{0.00,0.07,1.00}{Qualitative} Interviews
-    \item[]
-    \item January 2016: \textcolor[rgb]{0.00,0.07,1.00}{Listing} for Baseline
-    \item[]
-    \item Feb-Apr 2016: \textcolor[rgb]{0.00,0.07,1.00}{Baseline} Survey
-    \item[]
-    \item Oct-Nov 2016: \textcolor[rgb]{0.00,0.07,1.00}{Interventions}
-    \item[]
-    \item Apr-May 2017: \textcolor[rgb]{0.00,0.07,1.00}{Midline}
-    \item[]
-    \item Apr-May 2018: \textcolor[rgb]{0.00,0.07,1.00}{Endline}
-\end{enumerate}
-\end{frame}
-
-\begin{frame}
-\frametitle{Typical Retail Shop in the Sample}
+\begin{enumerate_3pt}
+    \item September 2015: \textcolor{bdf}{Qualitative} Interviews
+    \item January 2016: \textcolor{bdf}{Firm listing} ($\rightarrow$ survey instrument)
+    \item Feb-Apr 2016: \textcolor{bdf}{Baseline} survey
+    \item Oct-Nov 2016: \textcolor{bdf}{Interventions}
+    \item Apr-May 2017: \textcolor{bdf}{Midline} survey
+    \item Apr-May 2018: \textcolor{bdf}{Endline} survey
+\end{enumerate_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Typical Business in the Sample}
 
@@
 \begin{frame}
-\frametitle{Typical Retail Shop in the Sample II}
+\frametitle{Typical Business in the Sample}
 
@@
 \begin{frame}
-\frametitle{Handbook}
+\frametitle{Best-practices Handbook}
 
@@
 \begin{frame}
-\frametitle{Handbook Content II}
+\frametitle{Handbook Content}
 
@@
 
-&\multicolumn{1}{c}{\textbf{Control}}
-&&\multicolumn{1}{c}{\textbf{HB only}}	
-&&\multicolumn{1}{c}{\textbf{HB \& MOV}	}
-&&\multicolumn{1}{c}{\textbf{HB \& HELP}}	
-&&\multicolumn{1}{c}{\textbf{HB \& MOV}}	\\
+&\multicolumn{1}{c}{\textcolor{bdf}{Control}}
+&&\multicolumn{1}{c}{\textcolor{bdf}{HB only}}	
+&&\multicolumn{1}{c}{\textcolor{bdf}{HB \& MOV}	}
+&&\multicolumn{1}{c}{\textcolor{bdf}{HB \& HELP}}	
+&&\multicolumn{1}{c}{\textcolor{bdf}{HB \& MOV}}	\\
 
@@
 &&\multicolumn{1}{c}{}	
-&&\multicolumn{1}{c}{\textbf{\& HELP}}	\\
+&&\multicolumn{1}{c}{\textcolor{bdf}{\& HELP}}	\\
 
@@
 
-\textbf{Firm Owner Characteristics} \\
+\textcolor{bdf}{Firm Owner Characteristics} \\
 Gender (Male=1)											& 0.28	&& 0.3	&&0.29	&& 0.3	&& 0.28\\
@@
 \\														
-\textbf{Firm Characteristics} \\
+\textcolor{bdf}{Firm Characteristics} \\
 Firm Age (Years)										&12.76		&&13.77		&&14.03		&&13.98		&&13.47 \\
@@
 \\
-\textbf{Business Practices} \\
+\textcolor{bdf}{Business Practices} \\
 Management Practices Aggregate Score											& 0.37	&& 0.36	&& 0.37	&& 0.35	&& 0.37 \\
@@
 	\end{table}}}
-\begin{itemize}
+\begin{itemize_3pt}
 \item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
-\end{itemize}
+\end{itemize_3pt}
 \end{frame}
@@
     \hline
-  	& \textbf{HB \& MOV} 		& \textbf{HB \& MOV}		  \\
-  	& 							& \textbf{\& HELP}			\\
-   	& \textbf{(A)}   			& \textbf{(B)}   			 \\
+  	& \textcolor{bdf}{HB \& MOV} 		& \textcolor{bdf}{HB \& MOV}		  \\
+  	& 							& \textcolor{bdf}{\& HELP}			\\
+   	& \textcolor{bdf}{(A)}   			& \textcolor{bdf}{(B)}   			 \\
  	&							&							\\
@@
    														&		&		 \\
-    \textbf{Attendance} 								&       &         \\
+    \textcolor{bdf}{Attendance} 								&       &         \\
   	% 													&		&		&& \\
@@
 	&       &       \\
-    \textbf{Evaluation (1-4 Scale):}	&       &        \\
+    \textcolor{bdf}{Evaluation (1-4 Scale):}	&       &        \\
    	%									&       &       &&  \\
@@
     \hline
-   	& \textbf{HB \& HELP} 		& \textbf{HB \& MOV,}		 \\
-  	& 							& \textbf{\& HELP}			 \\
-   	& \textbf{(A)}   			& \textbf{(B)}   			\\
+   	& \textcolor{bdf}{HB \& HELP} 		& \textcolor{bdf}{HB \& MOV,}		 \\
+  	& 							& \textcolor{bdf}{\& HELP}			 \\
+   	& \textcolor{bdf}{(A)}   			& \textcolor{bdf}{(B)}   			\\
 	&							&							 \\
@@
           																				&       &      \\
-    \multicolumn{1}{l}{\textbf{Attendance}} 											&       &        \\
+    \multicolumn{1}{l}{\textcolor{bdf}{Attendance}} 											&       &        \\
     %\multicolumn{1}{l}{\textit{1st session}} 											&       &       & &  \\
@@
           																				&       &        \\
-    \multicolumn{1}{l}{\textbf{Evaluation (1-4 Scale)}} 								&       &         \\
+    \multicolumn{1}{l}{\textcolor{bdf}{Evaluation (1-4 Scale)}} 								&       &         \\
     \multicolumn{1}{l}{Has Learned Something New} 										& 2.88  & 2.89   \\
@@
 		\\
-			&\textbf{Record}			&&\textbf{Planning}			&&\textbf{Stocking-up}	&&\textbf{Marketing} && \textbf{Joint} \\
-&\textbf{Keeping}                       &&                        &&	                   &&	 && Decision-making \\
+			&\textcolor{bdf}{Record}			&&\textcolor{bdf}{Planning}			&&\textcolor{bdf}{Stocking-up}	&&\textcolor{bdf}{Marketing} && \textcolor{bdf}{Joint} \\
+&\textcolor{bdf}{Keeping}                       &&                        &&	                   &&	 && Decision-making \\
 					&(1)					&&(2)						&&(3) 						&&(4) && (5)\\
@@
 \end{table}}}
-\begin{itemize}
+\begin{itemize_3pt}
 \item Multiple hypothesis testing corrected p-values in parentheses
 \item "All Three" improvement of 28 \% in record-keeping, 17 \% in planning, 11 \% in stocking, 24 \% in marketing and 22 \% in joint decision making.
-\end{itemize}
+\end{itemize_3pt}
 \end{frame}
@@
 \end{table}}}
-\begin{itemize}
+\begin{itemize_3pt}
 \item Profits increase by 35\% (about 0.28 sd.) - ITT.
-\end{itemize}
+\end{itemize_3pt}
 \end{frame}
@@
 \end{table}}}
-\begin{itemize}
+\begin{itemize_3pt}
 \item Sales increase by 16\% (about 0.15 sd.) - ITT %- and 31\% (0.28 sd.) - TOT.
-\end{itemize}
+\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Other Outcomes}
-\begin{itemize}
-\item \textbf{No significant} impacts on:
-    \begin{itemize}
-    \vspace{0.2in}
+\begin{itemize_3pt}
+\item \textcolor{bdf}{No significant} impacts on:
+    \begin{itemize_3pt}
+    \vspace{0.1in}
     \item Business expenses
-    \vspace{0.2in} 		
+    \vspace{0.1in} 		
     \item Size of the shop
-      \vspace{0.2in}
+      \vspace{0.1in}
     \item Number of employees
-      \vspace{0.2in}
+      \vspace{0.1in}
     \item Number of customers
-       \vspace{0.2in}
+       \vspace{0.1in}
      \item Business credit
-    \end{itemize}
-\end{itemize}
+    \end{itemize_3pt}
+\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Efficiency Gains?}
-\begin{enumerate}
+\begin{enumerate_3pt}
 \item Unpacking impacts on practices shows improvements in efficiency practices:
 \vspace{0.1in}
-\begin{itemize}
+\begin{itemize_3pt}
 \item Adjust stocks based on product profitability
@@
 \item Make anticipated budget for upcoming costs
-\end{itemize}
-\vspace{0.2in}
+\end{itemize_3pt}
+\vspace{0.1in}
 \pause
 \item These are non-record-keeping practices. Also, variance in profits among the treated businesses does not converge
-\vspace{0.2in}
+\vspace{0.1in}
 \pause
 \item Causal-mediation analysis shows that the most important drivers of impact on sales and profits are stocking up and marketing practices.
-\end{enumerate}
-\vspace{0.2in}
-$\rightarrow$ \textcolor[rgb]{0.00,0.07,1.00}{Efficiency gains}
+\end{enumerate_3pt}
+\vspace{0.1in}
+$\rightarrow$ \textcolor{bdf}{Efficiency gains}
 \end{frame}
@@
 \frametitle{Knowledge or Aspirations?}
-\begin{itemize}
+\begin{itemize_3pt}
 \item Our interventions could have increased business performance and practice adoption through an increase in business aspirations rather than (or on top of) business knowledge.
-\vspace{0.2in}
+\vspace{0.1in}
 \item We directly measure business aspirations at baseline, midline, and endline for all shop owners in the sample.
-\vspace{0.2in}
+\vspace{0.1in}
 \item We elicit short (one year) and long-term (ideal) aspirations on various business dimensions:
 \vspace{0.1in}
-    \begin{itemize}
+    \begin{itemize_3pt}
     \item sales
@@
     \item number of employees
-    \end{itemize}
-\vspace{0.2in}
+    \end{itemize_3pt}
+\vspace{0.1in}
 \item No treatment effects on aspirations
-\vspace{0.2in}
-\end{itemize}
-$\rightarrow$ \textcolor[rgb]{0.00,0.07,1.00}{Knowledge}
+\vspace{0.1in}
+\end{itemize_3pt}
+$\rightarrow$ \textcolor{bdf}{Knowledge}
 \end{frame}
@@
 \frametitle{Business Stealing?}
-Do treated businesses improve performance at the expense of the control group?
-\vspace{0.1in}
-\begin{itemize}
-\item Shops in Control group \textbf{do not decrease} their sales and profits from baseline to endline. They remain the same.
-\vspace{0.1in}
-\item Shops in Control group that are closer to the treated shops \textbf{do not suffer bigger losses in sales and profits} than those who are further away.
-\end{itemize}
-\vspace{0.2in}
-$\rightarrow$ \textcolor[rgb]{0.00,0.07,1.00}{No evidence for business stealing}
+Do treated businesses improve performance at the expense of the control?
+\vspace{0.1in}
+\begin{itemize_3pt}
+\item Sales and profits of \textcolor{bdf}{control businesses do not decrease} from baseline to endline (roughly equal)
+\item Sales and profits of control businesses \textcolor{bdf}{closer to treated shops do not decrease by more} than those further away
+\item[] $\rightarrow$ \textcolor{bdf}{No evidence for business stealing}
+\end{itemize_3pt}
 \end{frame}
@@
 \frametitle{Cost-Effectiveness}
-\begin{itemize}
-\item \textbf{Low cost} per firm:
-\begin{itemize}
+
+\textcolor{bdf}{Small costs (per firm)}:
+\begin{itemize_3pt}
 \item Cost Handbook alone: USD 100
@@
 \item Cost Handbook \& Assistance: USD 125
-\item Cost Handbook \& Assistance \& Movie: USD 150
-\vspace{0.20in}
-\end{itemize}
-\item \textbf{High Benefits}
-    \begin{itemize}
-    \item Up to USD 330 per month in profits.
-    \item Adoption of top practices by retailers.
-    \end{itemize}
-\vspace{0.20in}
- \item Research Design likely \textbf{scalable and replicable} in other settings.
-\end{itemize}
+\item Cost Handbook \& Movie \& Assistance: USD 150
+\end{itemize_3pt}
+\vspace{0.5em}
+
+\textcolor{bdf}{Substantial Benefits}
+\begin{itemize_3pt}
+\item Up to USD 330 per month in profits
+\item Adoption of top practices by retailers
+\end{itemize_3pt}
+
+\vspace{0.5em}
+Research design likely \textcolor{bdf}{scalable and portable}
+
 \end{frame}
@@
 \frametitle{Takeaways}
-\begin{itemize}
-    \item Curating local knowledge has value for business growth 
-            \vspace{0.20in}
-    \item Information alone does not have impact, but behavioral interventions are needed
-            \vspace{0.20in}
-	\item These "add-ons" are inexpensive and scalable, making this type of intervention very attractive for policy
-
-\end{itemize}
+\begin{itemize_3pt}
+    \item \textcolor{bdf}{Curating local knowledge has value for business growth} 
+    \item Information alone does not have impact, only combined with \textcolor{bdf}{behavioral interventions}
+    \item Mechanism likely \textcolor{bdf}{knowledge-based}, not aspirations-based
+	\item Behavioral interventions are \textcolor{bdf}{inexpensive and scalable}
+	\vspace{-0.5em}
+	\item[] $\rightarrow$  Attractive for policy!
+
+\end{itemize_3pt}
 \end{frame}

### 2021-02-03 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Worked on scheme color, fonts, and bibliography

@@
 \usepackage{hyperref}
+\usepackage{natbib}
 
@@
 \definecolor{bdf}{rgb}{0.19, 0.55, 0.91}
-\definecolor{offwhite}{RGB}{255,253,238}
+\definecolor{offwhite}{RGB}{255,253,243}
 \definecolor{red}{RGB}{213,94,0}
@@
 %\setbeamercolor{sidebar}{bg=cerulean}
-
 %\newenvironment{transitionframe}{\setbeamercolor{background canvas}{bg=bdf}\begin{frame}}{\end{frame}}
@@
 
+% Font
 \setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
@@
 %\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}
+\setbeamerfont{title in sidebar}{}
+\setbeamerfont{author in sidebar}{}
+\setbeamercolor{section in sidebar}{bg=bdf,fg=offwhite}
+\setbeamercolor{subsection in sidebar}{bg=bdf,fg=offwhite}
+
+%\setbeamercolor{title}{bg=red!25!blue,fg=white}
+%\setbeamercolor{fo} {bg=red!25!blue,fg=white}
+%\setbeamercolor{sidebar}{bg=red!25!blue,fg=white}
+%\setbeamercolor{author in sidebar}{fg=black!20!white}
+%\setbeamercolor{title in sidebar}{fg=white}
+%\setbeamercolor{normal text}{bg=white}
+%\setbeamercolor{frametitle}{fg=white}
+%\setbeamercolor{section in sidebar}{bg=black,fg=white}
+%\setbeamercolor{subsection in sidebar}{bg=black,fg=white}
+%\setbeamercolor{block title}{bg=red!25!blue,fg=white}
+%\setbeamercolor{block body}{bg=blue!20!white,fg=black}
+%\setbeamerfont{subsection in sidebar}{size=\tiny}
+%\setbeamerfont{title in sidebar}{size=\scriptsize}
+%\setbeamerfont{author in sidebar}{size=\tiny}
+%\setbeamercovered{transparent}
 
@@
 
+% Bibliography
+%\renewcommand\bibliographytypesize{\small}
+\renewcommand*{\bibfont}{\scriptsize}
+
 \title[]{Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings}
@@
 	\begin{itemize_3pt}
-	\item Bloom and van Reenen (2010, 2019): Business practices, motivation
+	\item Bloom and van Reenen (2010, 2019): Business practices, motivation \citep{Bloom2010, Bloom2019}
 	\vspace{0.1in}
@@
 	\begin{itemize_3pt}
-	\item Bloom and van Reenen (2010): Heterogeneity
+	\item Bloom and van Reenen (2010): Heterogeneity \citep{Bloom2010}
 	\vspace{0.1in}
@@
 	\begin{itemize_3pt}
-	\item Bloom and van Reenen (2019): Correlation with productivity
+	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
 	\vspace{0.1in}
@@
 \begin{frame}
+\frametitle{Business Practices in Small Firms}
+	\begin{itemize_3pt}
+	\item McKenzie and Woodruff (2009, 2017): Heterogeneity and predictiveness \citep{McKenzie2009, McKenzie2017}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
 \frametitle{Business Practices of Small Firms}
 	\begin{itemize_3pt}
-	\item McKenzie and Woodruff (2009, 2017): Heterogeneity and predictiveness
-	\vspace{0.1in}
-	\end{itemize_3pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Business Practices of Small Firms}
-	\begin{itemize_3pt}
-	\item McKenzie and Woodruff (2009, 2017): Example categories and practices
+	\item McKenzie and Woodruff (2009, 2017): Example categories and practices \citep{McKenzie2009, McKenzie2017}
 	\vspace{0.1in}
@@
 	\begin{itemize_3pt}
-	\item McKenzie and Woodruff (2017): Portable best practices
+	\item McKenzie and Woodruff (2017): Portable best practices \citep{McKenzie2017}
 	\vspace{0.1in}
@@
 	\begin{itemize_3pt}
-		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; McKenzie, 2020)
+		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; \citet{McKenzie2020})
 		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
@@
 \frametitle{Typical Training Program}
-	\begin{itemize_3pt}
-	\item Content %\textcolor{}{}
+	Content
+	\begin{itemize_3pt}
+	%\textcolor{}{}
+	\item Training is delivered by 600 local certified trainers and by a pool of approximately 60 international master trainers. All trainers are also entrepreneurs.
+	\item Empretec Training Workshops offer different levels of instruction that include:
+	\item 6-day courses (48 hours); 32-hour (usually spread over 4 days) for micro-entrepreneurs with low levels of literacy; Interactive coaching based on real business challenges of participants.
 	\vspace{0.1in}
@@
 \frametitle{Typical Training Program}
-	\begin{itemize_3pt}
-	\item Delivery %\textcolor{}{}
+	Delivery
+	\begin{itemize_3pt}
+	\item %\textcolor{}{}
 	\vspace{0.1in}
@@
 \begin{frame}
-\frametitle{Impact on Businesses}
+\frametitle{Evidence on Impact}
 	\begin{itemize_3pt}
 	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
-	\vspace{0.1in}
-	\end{itemize_3pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Impact on Businesses}
-	\begin{itemize_3pt}
-	\item Econometric and implementation issues (McKenzie and Woodruff, 2014)
-	\vspace{0.1in}
-	\end{itemize_3pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Impact on Businesses}
-	\begin{itemize_3pt}
-	\item Recent evaluations (McKenzie, 2020)
+					 \citep{Karlan2011} \citep{Field2010} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Evidence on Impact}
+	\begin{itemize_3pt}
+	\item Econometric and implementation issues \citep{McKenzie2014}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Evidence on Impact}
+	\begin{itemize_3pt}
+	\item Recent evaluations (McKenzie, 2020) \citep{McKenzie2020}
 	\vspace{0.1in}
@@
 \frametitle{Targeted Training}
-	\begin{itemize_3pt}
-	\item Female entrepreneurs
+	Female entrepreneurs
+	\begin{itemize_3pt}
+		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016,McKenziePuerto2020}
+		\item ?
 	\vspace{0.1in}
@@
 \frametitle{Targeted Training}
-	\begin{itemize_3pt}
-	\item Young entrepreneurs
+	Young entrepreneurs
+	\begin{itemize_3pt}
+		\item Entrepreneurship programs in school and university
+		\item Example: University final year course in Tunisia \citep{Alaref2020}
+		\item ?
 	\vspace{0.1in}
@@
 \begin{frame}
+\frametitle{Specific Domains}
+	\begin{itemize_3pt}
+	\item \citep{Anderson2018}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Specific Domain}
+	\begin{itemize_3pt}
+	\item \citep{Anderson2018}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+%---------------------
+
+\begin{frame}
 \frametitle{On-site Consulting}
 	\begin{itemize_3pt}
-	\item Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
+	\item Bloom, et al. (2013); Karlan et al. (2015); Bruhn, Karlan, and Schoar (2019)
+	\item Large firms: \citep{Bloom2013}; SMEs: \citep{Bruhn2018}
+	\item \citep{Karlan2015} \citep{Bruhn2019}
 	\vspace{0.1in}
@@
 \begin{frame}
+\frametitle{Multimedia delivery}
+	TV shows
+	\begin{itemize_3pt}
+	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
+	\item ?
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Multimedia delivery}
+	TV shows
+	\begin{itemize_3pt}
+	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
+	\item ?
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Multimedia delivery}
+	Text messages
+	\begin{itemize_3pt}
+	\item \citep{Cole2019} \citep{Acimovic2020}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+% -----------------------
+
+\begin{frame}
 \frametitle{Complementary Constraints}
@@
 	\begin{itemize_3pt}
-	\item Self-reports of aggregate
+	\item Self-reports of aggregate \citep{deMel2009}
 	\vspace{0.1in}
@@
 	\begin{itemize_3pt}
-	\item Disaggregating quantities in self-reports
+	\item Disaggregating quantities in self-reports \citep{deMel2009}
 	\vspace{0.1in}
@@
 	\begin{itemize_3pt}
-	\item Direct measures
+	\item Direct measures \citep{deMel2009}
 	\vspace{0.1in}
@@
 	\begin{itemize_3pt}
+	\item  \citep{deMel2009}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Sales vs. Profits}
+	\begin{itemize_3pt}
+	\item \citep{deMel2009}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+% ---------------------
+
+\begin{frame}
+\frametitle{?}
+	\begin{itemize_3pt}
 	\item 
@@
 \begin{frame}
-\frametitle{Sales vs. Profits}
+\frametitle{?}
 	\begin{itemize_3pt}
@@
 
-% ---------------------
-
-\begin{frame}
-\frametitle{?}
+\subsection{Mechanisms}
+
+\begin{frame}
+\frametitle{Heterogeneity of Impact}
+	\begin{itemize_3pt}
+	\item Heterogeneity of treatment effects poorly understood across different approaches
+	\item Potential constraints are manifold, and likely context-dependent
+	\item Some already mentioned in passing:
+	\begin{itemize_3pt}
+		\item Credit constraints \citep[see, e.g.,][]{} McKenzie cash paper
+		\item Gender norms and constraints
+		\item Age-related network and knowledge/skill constraints
+	\end{itemize_3pt} 
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Education and literacy}
+	\begin{itemize_3pt}
+	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Family Commitments}
 	\begin{itemize_3pt}
@@
 \begin{frame}
-\frametitle{?}
+\frametitle{Identity Concerns}
 	\begin{itemize_3pt}
@@
 
-\subsection{Mechanisms}
-
-\begin{frame}
-\frametitle{Heterogeneity of Impact}
-	\begin{itemize_3pt}
-	\item Heterogeneity of treatment effect poorly understood across different approaches
-	\item Potential constraints are manifold, and likely context-dependent
-	\vspace{0.1in}
-	\end{itemize_3pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Education and literacy}
-	\begin{itemize_3pt}
-	\item Drexler, Fischer \& Schoar (2014)
-	\vspace{0.1in}
-	\end{itemize_3pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Family Commitments}
+\begin{frame}
+\frametitle{Aspirations}
 	\begin{itemize_3pt}
@@
 \begin{frame}
-\frametitle{Identity Concerns}
+\frametitle{Local Relevance of Best Practices}
 	\begin{itemize_3pt}
@@
 
-\begin{frame}
-\frametitle{Aspirations}
-	\begin{itemize_3pt}
-	\item 
-	\vspace{0.1in}
-	\end{itemize_3pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Local Relevance of Best Practices}
-	\begin{itemize_3pt}
-	\item 
-	\vspace{0.1in}
-	\end{itemize_3pt}
-\end{frame}
-
 \subsection{Alternative Approaches}
@@
 	\begin{itemize_3pt}
-	\item Drexler, Fischer \& Schoar (2014)
+	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
 	\vspace{0.1in}
@@
 	\begin{itemize_3pt}
-	\item 
+	\item \citep{Arraiz2019} \citep{Cole2019}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+%
+
+\begin{frame}
+\frametitle{Entrepreneurial mindset}
+	\begin{itemize_3pt}
+	\item \citep{Campos2017}
+	\vspace{0.1in}
+	\end{itemize_3pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Entrepreneurial mindset}
+	\begin{itemize_3pt}
+	\item \citep{Alibhai2019} \citep{Ubfal2019}
 	\vspace{0.1in}
@@
 
-%\bibliographystyle{econometrica}
-%\bibliography{sampleBibFile}
+%\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
+
+\subsection{References}
+\begin{frame}[allowframebreaks]
+\frametitle{References}
+
+\bibliographystyle{econometrica}
+\bibliography{SME_library}
+\end{frame}
 

### 2021-02-03 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added details to schemes, added slides on MSME background

@@
-\documentclass[hideothersubsections, usenames,dvipsnames,10pt]{beamer}
+\documentclass[hideothersubsections, usenames,dvipsnames,11pt]{beamer}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-% Font
-\usefonttheme{serif}
-\setbeamercovered{invisible}
-
 % Color scheme
@@
 % Font
+\usefonttheme{serif}
+\setbeamercovered{invisible}
 \setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
@@
 \setbeamercolor{subsection in sidebar}{bg=bdf,fg=offwhite}
+\linespread{1.25}
 
@@
 %\setbeamercovered{transparent}
+\setbeamerfont{itemize/enumerate body}{size={\fontsize{9.5}{9.5}}}
+\setbeamerfont{itemize/enumerate subbody}{size={\fontsize{8}{8}}}
+%\setbeamerfont{itemize/enumerate subbody}{family=\sffamily}
 
@@
 
-\section{\textbf{PART I: Lecture} \\ \quad \emph{Business Practices}}
+\section{\textbf{PART I: Lecture} \\ \quad \emph{Business Practices and Training}}
 
@@
 		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
-		\vspace{0.1in}
 		\item Examples:
@@
 \frametitle{Questions}
-	\begin{itemize_3pt}
-	\item Any questions?
-	\vspace{0.1in}
+	\textcolor{bdf}{Any questions?}
+	\begin{itemize_3pt}
 	\item[] .. before we move on to our paper?
@@
 \institute[]{
-\inst{1} Tilburg University\\
-\bigskip
+\inst{1} Tilburg University \\
 \inst{2} UC Berkeley, CEGA\\
-\bigskip
 \inst{3} The World Bank}
@@
 	\begin{itemize_3pt}
-	\item Micro \& Small firms (MSEs) main \textcolor{bdf}{source of employment} in the developing world
-	\vspace{0.1in}
-	\item In \textcolor{bdf}{Indonesia}, MSEs represent 99\% of all firms and 94.5\% of employment 
-	\vspace{0.1in}
+	\item Micro and small firms (MSEs) are typically the main \textcolor{bdf}{source of employment} in the developing world
+	\item In \textcolor{bdf}{Indonesia}, MSEs represent .. 
+	\begin{itemize_3pt}
+		\item .. 99\% of all firms
+		\item .. 94.5\% of employment
+	\end{itemize_3pt} 
 	\item Understanding the factors fostering efficiency and growth of MSEs is an important research and policy goal
@@
 \frametitle{Harnessing Cross-Firm Heterogeneity}
-\begin{itemize_3pt}
-\item Some facts about business practices in firms:
-	\begin{itemize_3pt}	
-	\item Vast heterogeneity in business practices and performance across similar businesses (de Mel, McKenzie \& Woodruff, 2009)
-	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US (Bloom et al, 2019)
-	\end{itemize_3pt}
-\vspace{0.1in}
+Some stylized facts about business practices in small firms
+\begin{itemize_3pt}
+	\item Vast heterogeneity in business practices and performance across similar businesses \citep{deMel2009}
+	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US \citep{Bloom2019}
+	\item[] $\rightarrow$ Research has largely overlooked this heterogeneity in program design and implementation
+\end{itemize_3pt}
+
+\vspace{0.5em}
 \pause
-\item Research thus far has mostly overlooked this underlying heterogeneity in design and implementation of programs
-\vspace{0.1in}
-\pause
-\item Our idea is to make it \textcolor{bdf}{central} to the research design: 
-	\begin{itemize_3pt}
-	\item Use variation across businesses to identify business practices associated with successful performance
-	\item Instead of teaching set courses, provide consulting, or matching; we curate what works from local peers
-	\item Test different communication channels and their cost-effectiveness
-\end{itemize_3pt}
+
+Our idea is to \textcolor{bdf}{make productice use of this heterogeneity} in research design: 
+\begin{itemize_3pt}
+	\item Use cross-firm variation to identify \textcolor{bdf}{practices associated with business performance}
+	\item \textcolor{bdf}{Curate local best practices}
+	\item Test different \textcolor{bdf}{modes of delivery}, and their cost-effectiveness
 \end{itemize_3pt}
@@
 \frametitle{Efficiency Gains?}
-\begin{enumerate_3pt}
-\item Unpacking impacts on practices shows improvements in efficiency practices:
+Unpacking impacts on business practices $\rightarrow$ \textcolor{bdf}{efficiency practices}:
 \vspace{0.1in}
@@
 	\item Make joint decisions
-\item Review financial performance to identify channels of improvement
+	\item Review performance to identify ways to improve
 	\item Make anticipated budget for upcoming costs
-\end{itemize_3pt}
-\vspace{0.1in}
+	\vspace{0.1in}
+
 	\pause
-\item These are non-record-keeping practices. Also, variance in profits among the treated businesses does not converge
-\vspace{0.1in}
+
+	\item[] $\rightarrow$ \textcolor{bdf}{Non-record-keeping practices}
+	\vspace{0.1in}
+
 	\pause
-\item Causal-mediation analysis shows that the most important drivers of impact on sales and profits are stocking up and marketing practices.
-\end{enumerate_3pt}
-\vspace{0.1in}
-$\rightarrow$ \textcolor{bdf}{Efficiency gains}
+
+	\item[] $\rightarrow$ Causal-mediation analysis: \textcolor{bdf}{Stocking up and marketing practices} drive performance effects
+
+	\pause
+
+	\item[] $\rightarrow$ Variance in profits among treated firms does not converge
+
+	\item[] $\rightarrow$ \textcolor{bdf}{Efficiency gains}
+\end{itemize_3pt}
 \end{frame}
@@
 
-\subsection{References}
+%\section*{\textbf{APPENDIX}}
+
+%\subsection{References}
 \begin{frame}[allowframebreaks]

### 2021-02-04 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added content (Anderson 2018, etc.)

@@
 \newenvironment{stepitemizewithalert}{\begin{itemize}[<+-| alert@+>]}{\end{itemize} }
-\newenvironment{itemize_3pt}{\itemize\addtolength{\itemsep}{3pt}}{\enditemize}
-\newenvironment{enumerate_3pt}{\enumerate\addtolength{\itemsep}{3pt}}{\endenumerate}
+\newenvironment{itemize_2pt}{\itemize\addtolength{\itemsep}{2pt}}{\enditemize}
+\newenvironment{enumerate_2pt}{\enumerate\addtolength{\itemsep}{2pt}}{\endenumerate}
 
@@
 %\setbeamercolor{button}{bg=offwhite,fg=blue}
+
+% Create subsection transitions without subsection numbering
+\def\subsectionname{\translate{Subsection}}
+\def\insertsubsectionnumber{\arabic{subsection}}
+\setbeamertemplate{subsection page}
+{
+  %\begin{centering}
+    %{\usebeamerfont{subsection name}\usebeamercolor[fg]{subsection name}\subsectionname~\insertsubsectionnumber}
+    %\vskip1em\par
+    \begin{beamercolorbox}[sep=14pt,center]{part title}
+      \setbeamerfont{subsection title}{size=\fontsize{14}{20}\selectfont}
+      \usebeamerfont{subsection title}\insertsubsection\par
+    \end{beamercolorbox}
+  %\end{centering}
+}
+\def\subsectionpage{\usebeamertemplate*{subsection page}}
+\AtBeginSubsection
+{\frame{\subsectionpage}}
 
@@
 \frametitle{?}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Bloom and van Reenen (2010, 2019): Business practices, motivation \citep{Bloom2010, Bloom2019}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Heterogeneity in Business Practices}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Bloom and van Reenen (2010): Heterogeneity \citep{Bloom2010}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Business Practices in Small Firms}
-	\begin{itemize_3pt}
-	\item McKenzie and Woodruff (2009, 2017): Heterogeneity and predictiveness \citep{McKenzie2009, McKenzie2017}
-	\vspace{0.1in}
-	\end{itemize_3pt}
+
+	Vast heterogeneity in business practices \textcolor{bdf}{also among small firms} \citep{McKenzie2009, McKenzie2017}..
+	\begin{itemize_2pt}
+		\item .. between countries
+		\item .. between industries
+		\item .. between firms
+	\end{itemize_2pt}
+
+	\vspace{0.5em}
+
+	In cross-section, business practices \textcolor{bdf}{associated with higher sales and profits} \citep{McKenzie2017}
+
 \end{frame}
@@
 \frametitle{Business Practices of Small Firms}
-	\begin{itemize_3pt}
-	\item McKenzie and Woodruff (2009, 2017): Example categories and practices \citep{McKenzie2009, McKenzie2017}
-	\vspace{0.1in}
-	\end{itemize_3pt}
+
+	\citet{McKenzie2017} identify \textcolor{bdf}{set of XX best practices} most closely associated with business performance
+	\begin{itemize_2pt}
+		\item 5 major domains of practices
+		\begin{enumerate_2pt}
+			\item Book-keeping
+			\item ?
+			\item ?
+			\item Inventory management and stock control
+			\item Marketing
+		\end{enumerate_2pt}
+	\item[] $\rightarrow$ Association with performance robust across industries and countries
+	\item[] $\rightarrow$
+	\end{itemize_2pt}
 \end{frame}
@@
 \begin{frame}
-\frametitle{Best Practices for Small Firms}
-	\begin{itemize_3pt}
-	\item McKenzie and Woodruff (2017): Portable best practices \citep{McKenzie2017}
-	\vspace{0.1in}
-	\end{itemize_3pt}
+\frametitle{Business Practices of Small Firms}
+	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
+	\begin{itemize_2pt}
+		\item Example practices:
+		\begin{itemize_2pt}
+			\item 
+			\item 
+			\item 
+			\item 
+			\item 
+		\end{itemize_2pt}
+	\item Does adoption of "best practices" \emph{cause} increase in performance?
+	\item How can practice adoption best be facilitated?
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{History and Prevalence}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; \citet{McKenzie2020})
@@
 		\item Examples:
-		\begin{itemize_3pt}
+		\begin{itemize_2pt}
 			\item Start and Improve Your Business (ILO)
@@
 			\item EMPRETEC Entrepreneurship Training Workshop (UNCTAD)
-		\end{itemize_3pt} 
-	\end{itemize_3pt}
+		\end{itemize_2pt} 
+	\end{itemize_2pt}
 \end{frame}
@@
 	Content
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	%\textcolor{}{}
@@
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 	Delivery 
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item %\textcolor{}{}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Evidence on Impact}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
@@
 \frametitle{Evidence on Impact}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Econometric and implementation issues \citep{McKenzie2014}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Evidence on Impact}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Recent evaluations (McKenzie, 2020) \citep{McKenzie2020}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \begin{frame}
-\frametitle{Targeted Training}
+\frametitle{Targeting Training}
 	Female entrepreneurs
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
+		\item \textcolor{bdf}{Most common type of targeted training} (potentially complementary to classical microfinance model)
 		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016,McKenziePuerto2020}
@@
 	\vspace{0.1in}
-	\end{itemize_3pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Targeted Training}
+	\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Targeting Training}
 	Young entrepreneurs
-	\begin{itemize_3pt}
-		\item Entrepreneurship programs in school and university
+	\begin{itemize_2pt}
+		\item Typically embedded as entrepreneurship programs in school and university
 		\item Example: University final year course in Tunisia \citep{Alaref2020}
-		\item ?
-	\vspace{0.1in}
-	\end{itemize_3pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Targeted Training}
-	\begin{itemize_3pt}
-	\item Gazelles
-	\vspace{0.1in}
-	\end{itemize_3pt}
+		\begin{itemize_2pt}
+			\item
+			\item
+		\end{itemize_2pt}
+	\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Targeting Training}
+	High-growth businesses ("gazelles")
+	\begin{itemize_2pt}
+	\item
+	\item
+	\vspace{0.1in}
+	\end{itemize_2pt}
 \end{frame}
@@
 \begin{frame}
-\frametitle{Specific Domains}
-	\begin{itemize_3pt}
+\frametitle{Training Specific Domains}
+
+	\citet{Anderson2018} assign 852 South African businesses to two distinct trainings:
+	\begin{enumerate_2pt}
+		\item Finance/accounting skills
+		\item Marketing/sales skills
+	\end{enumerate_2pt}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Training Specific Domains}
+
+	\citet{Anderson2018} assign 852 South African businesses to two distinct trainings:
+	\begin{enumerate_2pt}
+		\item Finance/accounting skills
+		\begin{itemize_2pt}
+			\item Increased profits
+			\item "Efficiency focus" on lower costs
+			\item[] $\rightarrow$ Benefits established businesses (less market exposure)
+		\end{itemize_2pt}
+		\item Marketing/sales skills
+		\begin{itemize_2pt}
+			\item Increased profits
+			\item "Growth focus" on higher sales, stock investments, and hiring
+			\item[] $\rightarrow$ Benefits new businesses (less market exposure)
+		\end{itemize_2pt}
+	\end{enumerate_2pt}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Training Specific Domain}
+	\begin{itemize_2pt}
 	\item \citep{Anderson2018}
 	\vspace{0.1in}
-	\end{itemize_3pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Specific Domain}
-	\begin{itemize_3pt}
-	\item \citep{Anderson2018}
-	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{On-site Consulting}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Bloom, et al. (2013); Karlan et al. (2015); Bruhn, Karlan, and Schoar (2019)
@@
 \frametitle{On-site Consulting}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item ?
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 	TV shows
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
@@
 	Text messages
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item \citep{Cole2019} \citep{Acimovic2020}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Complementary Constraints}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item McKenzie cash JDE paper
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Imprecision of Outcome Measures}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Confidence Intervals, pic?
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Reliability of Self-reports}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Self-reports of aggregate \citep{deMel2009}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Reliability of Self-reports}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Disaggregating quantities in self-reports \citep{deMel2009}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Reliability of Self-report}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Direct measures \citep{deMel2009}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Sales vs. Profits}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item  \citep{deMel2009}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Sales vs. Profits}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item \citep{deMel2009}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{?}
-	\begin{itemize_3pt}
-	\item 
-	\vspace{0.1in}
-	\end{itemize_3pt}
+	\begin{itemize_2pt}
+	\item 
+	\vspace{0.1in}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Heterogeneity of Impact}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Heterogeneity of treatment effects poorly understood across different approaches
@@
 	\item Some already mentioned in passing:
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 		\item Credit constraints \citep[see, e.g.,][]{} McKenzie cash paper
@@
 		\item Age-related network and knowledge/skill constraints
-	\end{itemize_3pt} 
-	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt} 
+	\vspace{0.1in}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Education and literacy}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Family Commitments}
-	\begin{itemize_3pt}
-	\item 
-	\vspace{0.1in}
-	\end{itemize_3pt}
+	\begin{itemize_2pt}
+	\item 
+	\vspace{0.1in}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Identity Concerns}
-	\begin{itemize_3pt}
-	\item 
-	\vspace{0.1in}
-	\end{itemize_3pt}
+	\begin{itemize_2pt}
+	\item 
+	\vspace{0.1in}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Aspirations}
-	\begin{itemize_3pt}
-	\item 
-	\vspace{0.1in}
-	\end{itemize_3pt}
+	\begin{itemize_2pt}
+	\item 
+	\vspace{0.1in}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Local Relevance of Best Practices}
-	\begin{itemize_3pt}
-	\item 
-	\vspace{0.1in}
-	\end{itemize_3pt}
+	\begin{itemize_2pt}
+	\item 
+	\vspace{0.1in}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Rules of Thumb}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Rules of Thumb}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item \citep{Arraiz2019} \citep{Cole2019}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Entrepreneurial mindset}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item \citep{Campos2017}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Entrepreneurial mindset}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item \citep{Alibhai2019} \citep{Ubfal2019}
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Local Knowledge}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Role Models}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Role Models}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018
 	\vspace{0.1in}
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Takeaways}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
     \item
    	\vspace{0.10in}
-\end{itemize_3pt}
+\end{itemize_2pt}
 \end{frame}
@@
 	\textcolor{bdf}{Any questions?}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item[] .. before we move on to our paper?
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Background}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Micro and small firms (MSEs) are typically the main \textcolor{bdf}{source of employment} in the developing world
 	\item In \textcolor{bdf}{Indonesia}, MSEs represent .. 
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 		\item .. 99\% of all firms
 		\item .. 94.5\% of employment
-	\end{itemize_3pt} 
+	\end{itemize_2pt} 
 	\item Understanding the factors fostering efficiency and growth of MSEs is an important research and policy goal
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{A Growing Focus on Management}
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 \item \textcolor{bdf}{Classroom Training}: Field, et al.
@@
 \item \textcolor{bdf}{Mobilizing Peer Knowledge}:
-    \begin{itemize_3pt}
+    \begin{itemize_2pt}
     \item Brooks et al. (2018) $\rightarrow$ Local mentors (market information)
@@
     \item Abebe et al. (2019) $\rightarrow$ Management experience matching
-    \end{itemize_3pt}
-    \vspace{0.1in}
-\end{itemize_3pt}
+    \end{itemize_2pt}
+    \vspace{0.1in}
+\end{itemize_2pt}
 \end{frame}
@@
 Some stylized facts about business practices in small firms
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 	\item Vast heterogeneity in business practices and performance across similar businesses \citep{deMel2009}
@@
 	\item[] $\rightarrow$ Research has largely overlooked this heterogeneity in program design and implementation
-\end{itemize_3pt}
+\end{itemize_2pt}
 
@@
 
-Our idea is to \textcolor{bdf}{make productice use of this heterogeneity} in research design: 
-\begin{itemize_3pt}
+We \textcolor{bdf}{make productive use of this heterogeneity} in our research design: 
+\begin{itemize_2pt}
 	\item Use cross-firm variation to identify \textcolor{bdf}{practices associated with business performance}
-	\item \textcolor{bdf}{Curate local best practices}
+	\item \textcolor{bdf}{Curation} of local best practices
 	\item Test different \textcolor{bdf}{modes of delivery}, and their cost-effectiveness
-\end{itemize_3pt}
+\end{itemize_2pt}
 
@@
 \frametitle{Selecting Local Best Practices}
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 \item Detailed \textcolor{bdf}{qualitative interviews} with local business peers:
-    \begin{itemize_3pt}
+    \begin{itemize_2pt}
     \item Understand and codify their practices (record-keeping, financial planning, stocking-up, marketing, and joint decision-making)
@@
     \item Document locally relevant tips and rule of thumbs
-    \end{itemize_3pt}
+    \end{itemize_2pt}
 \vspace{0.1in}
 \item Baseline \textcolor{bdf}{quantitative survey}
-    \begin{itemize_3pt}
+    \begin{itemize_2pt}
     \item Measure practices and outcomes
     \item Quantitative association of business practices with profits and sales
-    \end{itemize_3pt}
-\end{itemize_3pt}
+    \end{itemize_2pt}
+\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Disseminating Knowledge}
-		\begin{itemize_3pt}
+		\begin{itemize_2pt}
 		\item \textcolor{bdf}{Handbook}
-			\begin{itemize_3pt}
+			\begin{itemize_2pt}
 			\item \textcolor{bdf}{Pure information}: Which practices, how to adopt, and why?\\
@@
             %\item \textcolor{bdf}{Negative Frame}: Retailers who do \textcolor{bdf}{not} implement [x] report y\% \textcolor{bdf}{lower} sales and z\% \textcolor{bdf}{lower} profits.
-			\end{itemize_3pt}
+			\end{itemize_2pt}
 \bigskip
@@
 		\item \textcolor{bdf}{Movie}
-			\begin{itemize_3pt}
+			\begin{itemize_2pt}
 			\item \textcolor{bdf}{Psychological and emotional involvement}$\rightarrow$ social learning is possible through \textcolor{bdf}{observing the successful experience of similar others}.
 			\item Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013).\\
-			\end{itemize_3pt}
+			\end{itemize_2pt}
 
@@
 		\item \textcolor{bdf}{On-site Assistance}
-			\begin{itemize_3pt}
+			\begin{itemize_2pt}
 			\item \textcolor{bdf}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textcolor{bdf}{experience, with a small nudge} (Kolb, 1984).
 			\item Facilitated by local lay person
-			\end{itemize_3pt}
+			\end{itemize_2pt}
 			\vspace{0.05in}
@@
 %			$\rightarrow$ Horse race between role models and business counseling.
-		\end{itemize_3pt}
+		\end{itemize_2pt}
 
@@
 \frametitle{Research Questions}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	%\item \textcolor{bdf}{Local characterization}
 	%\vspace{0.05in}
-	%	\begin{itemize_3pt}
+	%	\begin{itemize_2pt}
 	%	\item Which practices are associated with high profits?
 	%	\item How do successful businesses implement them?
-	%	\end{itemize_3pt}
+	%	\end{itemize_2pt}
 	%\vspace{0.05in}
 	\item \textcolor{bdf}{Adoption}
-		\begin{itemize_3pt}
+		\begin{itemize_2pt}
 		\item Do retailers adopt these practices once peer best practices are aggregated and made common knowledge?
 		\item If so, ...
-			\begin{itemize_3pt}
+			\begin{itemize_2pt}
 			\item Does the type of experiential involvement matter?
-			\end{itemize_3pt}
-		\end{itemize_3pt}
+			\end{itemize_2pt}
+		\end{itemize_2pt}
     \vspace{0.3in}
 	\item \textcolor{bdf}{Impact}
-		\begin{itemize_3pt}
+		\begin{itemize_2pt}
 		\item Does firm profitability increase?
 		\item If so, what are the channels?
-		\end{itemize_3pt}
-	\end{itemize_3pt}
+		\end{itemize_2pt}
+	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Sample}
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 \item Listing of 2042 small retail businesses from 29 administrative communities (Kelurahan) in urban Jakarta
 \item Selection criteria for firm listing:
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 %	\item General willingness to grow
@@
 	\item At least 30 meters distance to next business in sample $\rightarrow$ to minimize spillovers
-	\end{itemize_3pt}
+	\end{itemize_2pt}
 \item Random sample of 1301 from the list
 \item Randomization to treatment arms stratified by
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 	\item Gender
@@
 	\item Kelurahan
-	\end{itemize_3pt}
-\end{itemize_3pt}
+	\end{itemize_2pt}
+\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Experimental Design}
-	\begin{itemize_3pt}
+	\begin{itemize_2pt}
 %    \item \textcolor{bdf}{Same set of business practices} across treatments \\
@@
 	\vspace{0.05in}
-		\begin{itemize_3pt}
+		\begin{itemize_2pt}
 		\item \textcolor{bdf}{Handbook} with best practices and tips
@@
 		\item Best-practice on-site implementation \textcolor{bdf}{assistance}
-		\end{itemize_3pt}
+		\end{itemize_2pt}
 	\vspace{0.05in}
-\end{itemize_3pt}
-	\begin{itemize_3pt}
+\end{itemize_2pt}
+	\begin{itemize_2pt}
 \item{Five experimental groups}
-        %\begin{itemize_3pt}
+        %\begin{itemize_2pt}
         %\item{Handbooks (N=1040)}
@@
 	\vspace{0.05in}
-            \begin{enumerate_3pt}
+            \begin{enumerate_2pt}
               \item \textcolor{bdf}{Handbook} only (N=260)
@@
               \item Control (N=261)
-            \end{enumerate_3pt}
-        \end{itemize_3pt}
-    %\end{itemize_3pt}
+            \end{enumerate_2pt}
+        \end{itemize_2pt}
+    %\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Timeline}
-\begin{enumerate_3pt}
+\begin{enumerate_2pt}
     \item September 2015: \textcolor{bdf}{Qualitative} Interviews
@@
     \item Apr-May 2018: \textcolor{bdf}{Endline} survey
-\end{enumerate_3pt}
+\end{enumerate_2pt}
 \end{frame}
@@
 	\end{table}}}
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 \item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
-\end{itemize_3pt}
+\end{itemize_2pt}
 \end{frame}
@@
 \end{table}}}
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 \item Multiple hypothesis testing corrected p-values in parentheses
 \item "All Three" improvement of 28 \% in record-keeping, 17 \% in planning, 11 \% in stocking, 24 \% in marketing and 22 \% in joint decision making.
-\end{itemize_3pt}
+\end{itemize_2pt}
 \end{frame}
@@
 \end{table}}}
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 \item Profits increase by 35\% (about 0.28 sd.) - ITT.
-\end{itemize_3pt}
+\end{itemize_2pt}
 \end{frame}
@@
 \end{table}}}
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 \item Sales increase by 16\% (about 0.15 sd.) - ITT %- and 31\% (0.28 sd.) - TOT.
-\end{itemize_3pt}
+\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Other Outcomes}
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 \item \textcolor{bdf}{No significant} impacts on:
-    \begin{itemize_3pt}
+    \begin{itemize_2pt}
     \vspace{0.1in}
@@
      \item Business credit
-    \end{itemize_3pt}
-\end{itemize_3pt}
+    \end{itemize_2pt}
+\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Efficiency Gains?}
-Unpacking impacts on business practices $\rightarrow$ \textcolor{bdf}{efficiency practices}:
-\vspace{0.1in}
-\begin{itemize_3pt}
+Impact on business practices $\rightarrow$ \textcolor{bdf}{efficiency practices}:
+\vspace{0.1in}
+\begin{itemize_2pt}
 	\item Adjust stocks based on product profitability
@@
 	\item Make anticipated budget for upcoming costs
-	\vspace{0.1in}
 
@@
 	\item[] $\rightarrow$ \textcolor{bdf}{Non-record-keeping practices}
-	\vspace{0.1in}
-
-	\pause
-
 	\item[] $\rightarrow$ Causal-mediation analysis: \textcolor{bdf}{Stocking up and marketing practices} drive performance effects
-
-	\pause
-
 	\item[] $\rightarrow$ Variance in profits among treated firms does not converge
-
 	\item[] $\rightarrow$ \textcolor{bdf}{Efficiency gains}
-\end{itemize_3pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Knowledge or Aspirations?}
-\begin{itemize_3pt}
-\item Our interventions could have increased business performance and practice adoption through an increase in business aspirations rather than (or on top of) business knowledge.
-\vspace{0.1in}
-\item We directly measure business aspirations at baseline, midline, and endline for all shop owners in the sample.
-\vspace{0.1in}
-\item We elicit short (one year) and long-term (ideal) aspirations on various business dimensions:
-\vspace{0.1in}
-    \begin{itemize_3pt}
-    \item sales
-    \item shop size
-    \item number of customers
-    \item number of employees
-    \end{itemize_3pt}
-\vspace{0.1in}
-\item No treatment effects on aspirations
-\vspace{0.1in}
-\end{itemize_3pt}
-$\rightarrow$ \textcolor{bdf}{Knowledge}
+\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Business Knowledge or Aspirations?}
+Impact on practice adoption and business performance may work through ..
+\begin{itemize_2pt}
+	\item .. acquisition of \textcolor{bdf}{business knowledge} and/or
+	\item .. strengthening of \textcolor{bdf}{business aspirations}
+\end{itemize_2pt}
+
+\vspace{0.5em}
+
+We directly measure business aspirations .. 
+\begin{itemize_2pt}
+	\item .. at baseline, midline, and endline
+	\item .. for short (one year) and long ("ideal business") time horizons
+	\item .. for various dimensions of potential business expansion
+    \begin{itemize_2pt}
+   		\item Sales on a normal day
+    	\item Physical size
+   		\item Customers on a normal day
+    	\item Employees
+    \end{itemize_2pt}
+\item[] $\rightarrow$ \textcolor{bdf}{No impact on aspirations}
+\item[] $\rightarrow$ Performance likely driven by increase in \textcolor{bdf}{business knowledge}
+\end{itemize_2pt}
+
 \end{frame}
@@
 \vspace{0.1in}
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 \item Sales and profits of \textcolor{bdf}{control businesses do not decrease} from baseline to endline (roughly equal)
@@
 \item[] $\rightarrow$ \textcolor{bdf}{No evidence for business stealing}
-\end{itemize_3pt}
+\end{itemize_2pt}
 \end{frame}
@@
 \textcolor{bdf}{Small costs (per firm)}:
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 \item Cost Handbook alone: USD 100
@@
 \item Cost Handbook \& Movie \& Assistance: USD 150
-\end{itemize_3pt}
+\end{itemize_2pt}
 \vspace{0.5em}
@@
 \textcolor{bdf}{Substantial Benefits}
-\begin{itemize_3pt}
+\begin{itemize_2pt}
 \item Up to USD 330 per month in profits
 \item Adoption of top practices by retailers
-\end{itemize_3pt}
+\end{itemize_2pt}
 
@@
 \frametitle{Takeaways}
-\begin{itemize_3pt}
+\begin{itemize_2pt}
     \item \textcolor{bdf}{Curating local knowledge has value for business growth} 
@@
 	\item Behavioral interventions are \textcolor{bdf}{inexpensive and scalable}
-	\vspace{-0.5em}
-	\item[] $\rightarrow$  Attractive for policy!
-
-\end{itemize_3pt}
-\end{frame}
-
-%\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
-
-%\section*{\textbf{APPENDIX}}
-
-%\subsection{References}
+	\item[] $\rightarrow$  Attractive for policy
+
+\end{itemize_2pt}
+\end{frame}
+
+\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
+
+\section*{\textbf{APPENDIX}}
+
+\subsection*{References}
 \begin{frame}[allowframebreaks]

### 2021-02-07 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added tweaks to the referencs and to the appendix

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\usepackage{amsmath}
-\usepackage{mathpazo}
-\usepackage{hyperref}
-\usepackage{multimedia}
-\usepackage{multicol}
-\usepackage{epsfig}
-\usepackage{curves}
-\usepackage{epsfig}
-\usepackage{epic}
-\usepackage{curves}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 \usepackage{amsmath}
 \usepackage{amssymb}
-\usepackage{setspace}
-\usepackage{multicol}
-\usepackage{algorithm}
-\usepackage{algorithmic}
+\usepackage{curves}
+\usepackage{epic}
+\usepackage{epsfig}
 \usepackage{fix-cm}
@@
 \usepackage{hyperref}
+\usepackage{mathpazo}
+\usepackage{multimedia}
+\usepackage{multicol}
 \usepackage{natbib}
+\usepackage{setspace}
+\usepackage{tikz}
 
@@
 %\setbeamercolor{enumerate subitem}{fg=blue}
-%\setbeamercolor{button}{bg=offwhite,fg=blue}
-
-% Create subsection transitions without subsection numbering
-\def\subsectionname{\translate{Subsection}}
-\def\insertsubsectionnumber{\arabic{subsection}}
-\setbeamertemplate{subsection page}
-{
-  %\begin{centering}
-    %{\usebeamerfont{subsection name}\usebeamercolor[fg]{subsection name}\subsectionname~\insertsubsectionnumber}
-    %\vskip1em\par
-    \begin{beamercolorbox}[sep=14pt,center]{part title}
-      \setbeamerfont{subsection title}{size=\fontsize{14}{20}\selectfont}
-      \usebeamerfont{subsection title}\insertsubsection\par
-    \end{beamercolorbox}
-  %\end{centering}
-}
-\def\subsectionpage{\usebeamertemplate*{subsection page}}
-\AtBeginSubsection
-{\frame{\subsectionpage}}
-
-% Font
-\usefonttheme{serif}
-\setbeamercovered{invisible}
-\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
-\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
-%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}
-\setbeamerfont{title in sidebar}{}
-\setbeamerfont{author in sidebar}{}
-\setbeamercolor{section in sidebar}{bg=bdf,fg=offwhite}
-\setbeamercolor{subsection in sidebar}{bg=bdf,fg=offwhite}
-\linespread{1.25}
-
 %\setbeamercolor{title}{bg=red!25!blue,fg=white}
@@
 %\setbeamercovered{transparent}
+\setbeamercolor{section in sidebar}{bg=bdf,fg=offwhite}
+\setbeamercolor{subsection in sidebar}{bg=bdf,fg=offwhite}
+\setbeamercolor{button}{bg=bdf,fg=offwhite}
+
+% Create subsection transitions without subsection numbering
+\def\subsectionname{\translate{Subsection}}
+\def\insertsubsectionnumber{\arabic{subsection}}
+\setbeamertemplate{subsection page}
+{
+  %\begin{centering}
+    %{\usebeamerfont{subsection name}\usebeamercolor[fg]{subsection name}\subsectionname~\insertsubsectionnumber}
+    %\vskip1em\par
+    \begin{beamercolorbox}[sep=14pt,center]{part title}
+    	%\setbeamercolor{box1}{fg=yellow, bg=yellow}
+    	\setbeamerfont{subsection title}{size=\fontsize{14}{20}\selectfont}
+    	\usebeamerfont{subsection title}\insertsubsection\par
+    \end{beamercolorbox}
+  %\end{centering}
+}
+\def\subsectionpage{\usebeamertemplate*{subsection page}}
+\AtBeginSubsection
+{\frame{\subsectionpage}}
+
+% Font
+\usefonttheme{serif}
+\setbeamercovered{invisible}
+\setbeamerfont{section in sidebar}{size=\fontsize{5.3}{5}\selectfont}
+\setbeamerfont{subsection in sidebar}{size=\fontsize{4.4}{5.5}\selectfont}
+%\setbeamerfont{subsubsection in sidebar}{size=\fontsize{4}{7}\selectfont}
+\setbeamerfont{title in sidebar}{}
+\setbeamerfont{author in sidebar}{}
 \setbeamerfont{itemize/enumerate body}{size={\fontsize{9.5}{9.5}}}
@@
 %\setbeamerfont{itemize/enumerate subbody}{family=\sffamily}
+\setbeamerfont{button}{size={\fontsize{8}{8}}}
+\linespread{1.25}
 
@@
 \begin{document}
-
-% Create generic TOC
-
-%\AtBeginSection
-%{\begin{frame}{Overview}
-%\tableofcontents[currentsection,hideothersubsections]
-%\end{frame}}
 
@@
 		\end{itemize_2pt}
-	\item Does adoption of "best practices" \emph{cause} increase in performance?
-	\item How can practice adoption best be facilitated?
+	\end{itemize_2pt}
+
+\vspace{0.1in}
+
+	Open questions
+	\begin{itemize_2pt}
+		\item Does adoption of "best practices" \emph{cause} performance to increase?
+		\item How can adoption of practices best be encouraged?
 	\end{itemize_2pt}
@@
 \begin{frame}
-\frametitle{Evidence on Impact}
-	\begin{itemize_2pt}
-	\item First wave (Karlan and Valdivia, 2011, Field, et al., 2010; Bruhn \& Zia, 2013; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
-					 \citep{Karlan2011} \citep{Field2010} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Evidence on Impact}
+\frametitle{Evidence of Impact}
+	\begin{itemize_2pt}
+	\item First wave (Karlan and Valdivia, 2011, Bruhn and Zia, 2013; Giné and Mansuri, 2014; Field, et al., 2010; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
+					 \citep{Karlan2011} \citep{Field2010} \citet{Gine2014} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
+	\vspace{0.1in}
+	\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Evidence of Impact}
 	\begin{itemize_2pt}
@@
 
-\begin{frame}
-\frametitle{Evidence on Impact}
-	\begin{itemize_2pt}
-	\item Recent evaluations (McKenzie, 2020) \citep{McKenzie2020}
-	\vspace{0.1in}
-	\end{itemize_2pt}
+\begin{frame}[label=McK2020_profits]
+\frametitle{Evidence of Impact}
+
+	Including more recent evaluations \citep{McKenzie2020}
+
+\vspace{-0.5em}
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=21.5em]{pics/McK2020_profits.png}
+		\label{McKenzie(2020): Profits}
+	\end{figure}
+
+	\vspace{-1em}
+
+	\begin{itemize_2pt}
+		\item Small positive impact on practice adoption, profits, and \hyperlink{McK2020_sales}{\beamergotobutton{sales}}
+	\end{itemize_2pt}
+
+	%Right side pics
+	%\begin{tikzpicture}[remember picture, overlay]
+		%\node[shift={(-6.5em,1em)}]() at (current page.south east){%
+		%\hyperlink{appendix_sales}{\beamergotobutton{Sales}}};        
+	%\end{tikzpicture}
+
 \end{frame}
@@
 
+	\citet{Anderson2018} assign 852 South African MSEs to distinct types of training:
+	\begin{enumerate_2pt}
+		\item Marketing/sales skills
+		\item[]
+		\item[]
+		\item Finance/accounting skills
+		\item[]
+		\item[]
+	\end{enumerate_2pt}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Training Specific Domains}
+
 	\citet{Anderson2018} assign 852 South African businesses to two distinct trainings:
 	\begin{enumerate_2pt}
+
+		\item Marketing/sales skills
+		\begin{itemize_2pt}
+			\item 61\% increase in profits
+			\item "Growth focus" on higher sales, stock investments, and hiring
+			\item[] $\rightarrow$ Benefits new businesses ($=$ less market exposure)
+		\end{itemize_2pt}
+
 		\item Finance/accounting skills
-		\item Marketing/sales skills
+
+		\pause
+
+		\begin{itemize_2pt}
+			\item 41\% increase in profits
+			\item "Efficiency focus" on lower costs
+			\item[] $\rightarrow$ Benefits established businesses
+		\end{itemize_2pt}
+
+		\item[] $\rightarrow$ Different "pathways to profits" (title of the paper)
+
 	\end{enumerate_2pt}
 
-\end{frame}
-
-\begin{frame}
-\frametitle{Training Specific Domains}
-
-	\citet{Anderson2018} assign 852 South African businesses to two distinct trainings:
-	\begin{enumerate_2pt}
-		\item Finance/accounting skills
-		\begin{itemize_2pt}
-			\item Increased profits
-			\item "Efficiency focus" on lower costs
-			\item[] $\rightarrow$ Benefits established businesses (less market exposure)
-		\end{itemize_2pt}
-		\item Marketing/sales skills
-		\begin{itemize_2pt}
-			\item Increased profits
-			\item "Growth focus" on higher sales, stock investments, and hiring
-			\item[] $\rightarrow$ Benefits new businesses (less market exposure)
-		\end{itemize_2pt}
-	\end{enumerate_2pt}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Training Specific Domain}
-	\begin{itemize_2pt}
-	\item \citep{Anderson2018}
-	\vspace{0.1in}
-	\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Imprecision of Outcome Measures}
-	\begin{itemize_2pt}
-	\item Confidence Intervals, pic?
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Reliability of Self-reports}
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=23.5em]{pics/McK2020_profits.png}
+		\label{McKenzie(2020): Profits}
+	\end{figure}
+
+\vspace{-1em}
+
+	\begin{itemize_2pt}
+		\item \textcolor{bdf}{Extremely wide confidence intervals} on impact estimates
+	\vspace{0.1in}
+	\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Self-reports and aggregation}
 	\begin{itemize_2pt}
@@
 \begin{frame}
-\frametitle{Reliability of Self-reports}
+\frametitle{Self-reports and aggregation}
 	\begin{itemize_2pt}
@@
 \begin{frame}
-\frametitle{Reliability of Self-report}
+\frametitle{Self-reports and aggregation}
 	\begin{itemize_2pt}
@@
 
-%
 \begin{frame}
 \frametitle{Disseminating Knowledge}
+
+	Basic information intervention
 	\begin{itemize_2pt}
@@
 			\item \textcolor{bdf}{Pure information}: Which practices, how to adopt, and why?\\
-            %\item \textcolor{bdf}{Positive Frame}: Retailers who implement [x] report y\% \textcolor{bdf}{higher} sales and z\% \textcolor{bdf}{higher} profits.
-            %\item \textcolor{bdf}{Negative Frame}: Retailers who do \textcolor{bdf}{not} implement [x] report y\% \textcolor{bdf}{lower} sales and z\% \textcolor{bdf}{lower} profits.
-			\end{itemize_2pt}
-\bigskip
-Supplemented with two types of experiential learning:
-\bigskip
+		\end{itemize_2pt}
+	\end{itemize_2pt}
+
+	\vspace{1.0em}
+
+	Two complementary behavioral interventions:
+	\begin{itemize_2pt}
 		\item \textcolor{bdf}{Movie}
@@
 
-\bigskip
 		\item \textcolor{bdf}{On-site Assistance}
@@
 			\end{itemize_2pt}
-			\vspace{0.05in}
-%\bigskip
-%			$\rightarrow$ Horse race between role models and business counseling.
+
 	\end{itemize_2pt}
@@
 \frametitle{Research Questions}
-	\begin{itemize_2pt}
-	%\item \textcolor{bdf}{Local characterization}
-	%\vspace{0.05in}
-	%	\begin{itemize_2pt}
-	%	\item Which practices are associated with high profits?
-	%	\item How do successful businesses implement them?
-	%	\end{itemize_2pt}
-	%\vspace{0.05in}
-	\item \textcolor{bdf}{Adoption}
+
+	\textcolor{bdf}{Characterization of local best practices}
+	\begin{itemize_2pt}
+		\item Which practices are associated with high profits?
+		\item How do successful businesses implement them?
+	\end{itemize_2pt}
+	\vspace{1.0em}
+
+	\textcolor{bdf}{Adoption of best practices}
 	\begin{itemize_2pt}
 		\item Do retailers adopt these practices once peer best practices are aggregated and made common knowledge?
-		\item If so, ...
-			\begin{itemize_2pt}
-			\item Does the type of experiential involvement matter?
-			\end{itemize_2pt}
-		\end{itemize_2pt}
-    \vspace{0.3in}
-	\item \textcolor{bdf}{Impact}
+		\item If so, does the type of experiential involvement matter?
+
+	\end{itemize_2pt}
+    \vspace{1.0em}
+
+	\textcolor{bdf}{Impact on business performance}
 	\begin{itemize_2pt}
@@
 	\end{itemize_2pt}
-	\end{itemize_2pt}
+
 \end{frame}
@@
 \begin{itemize_2pt}
-\item Listing of 2042 small retail businesses from 29 administrative communities (Kelurahan) in urban Jakarta
+\item Listing of 2042 small retail businesses from 29 sub-districts ("kelurahan") in urban Jakarta
 \item Selection criteria for firm listing:
@@
 	\item Composite score of business practices above or below median
-	\item Kelurahan
+	\item Sub-district
 	\end{itemize_2pt}
@@
 \frametitle{Experimental Design}
-	\begin{itemize_2pt}
-%    \item \textcolor{bdf}{Same set of business practices} across treatments \\
-	\item Three types of information provision:
-	\vspace{0.05in}
-		\begin{itemize_2pt}
-		\item \textcolor{bdf}{Handbook} with best practices and tips
+
+	Three types of information delivery:
+		\begin{enumerate_2pt}
+			\item \textcolor{bdf}{Handbook} with best practices and implementation tips
 			\item \textcolor{bdf}{Movie} with successful peers
-		\item Best-practice on-site implementation \textcolor{bdf}{assistance}
-		\end{itemize_2pt}
-	\vspace{0.05in}
-\end{itemize_2pt}
-	\begin{itemize_2pt}
-\item{Five experimental groups}
-        %\begin{itemize_2pt}
-        %\item{Handbooks (N=1040)}
-        %: Positive Framing (N=520) and Negative Framing (N=520)}\\
-	\vspace{0.05in}
+			\item \textcolor{bdf}{On-site assistance} with practice adoption
+			\item[] $\rightarrow$ Movie, assistance exclusively based on handbook
+		\end{enumerate_2pt}
+	\vspace{0.1in}
+
+	Five experimental groups
     	\begin{enumerate_2pt}
         	\item \textcolor{bdf}{Handbook} only (N=260)
-              \item \textcolor{bdf}{Handbook} and invitation to \textcolor{bdf}{movie} screening (N=260)
-              \item \textcolor{bdf}{Handbook} and offer of two \textcolor{bdf}{assistance} visits (N=260)
-              \item \textcolor{bdf}{Handbook} and both \textcolor{bdf}{movie} and \textcolor{bdf}{assistance} (N=260)
+        	\item \textcolor{bdf}{Handbook} + invitation to \textcolor{bdf}{movie} screening (N=260)
+        	\item \textcolor{bdf}{Handbook} + offer of two \textcolor{bdf}{assistance} visits (N=260)
+        	\item \textcolor{bdf}{Handbook} + \textcolor{bdf}{movie} + \textcolor{bdf}{assistance} (N=260)
        		\item Control (N=261)
       	\end{enumerate_2pt}
-        \end{itemize_2pt}
-    %\end{itemize_2pt}
 \end{frame}
@@
 \frametitle{Summary Statistics}
+
+%\makebox[\linewidth][c]{
+%\begin{tabular}{l cc ddd}
+
 {\tiny{
@@
 		\centering	
-		%\tabcolsep=0.2cm
+		\tabcolsep=0.2cm
 
@@
 	\end{table}}}
-\begin{itemize_2pt}
-\item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
-\end{itemize_2pt}
+%\end{tabular}
+%\begin{itemize_2pt}
+%\item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
+%\end{itemize_2pt}
 \end{frame}
@@
 	\item[] $\rightarrow$ \textcolor{bdf}{Non-record-keeping practices}
-	\item[] $\rightarrow$ Causal-mediation analysis: \textcolor{bdf}{Stocking up and marketing practices} drive performance effects
+	\item[] $\rightarrow$ \textcolor{bdf}{Stocking up and marketing practices} appear to drive performance effects (causal-mediation analysis)
 	\item[] $\rightarrow$ Variance in profits among treated firms does not converge
@@
 
-\vspace{0.5em}
-
-We directly measure business aspirations .. 
+\pause
+\vspace{1.0em}
+
+We directly measure \textcolor{bdf}{business aspirations} .. 
 \begin{itemize_2pt}
@@
 
-\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
-
-\section*{\textbf{APPENDIX}}
-
-\subsection*{References}
-\begin{frame}[allowframebreaks]
+-----
+
+%\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
+
+\begin{frame}[label=references, allowframebreaks]
 \frametitle{References}
-
 \bibliographystyle{econometrica}
@@
 
+\section*{\textbf{APPENDIX}}
+
+\setbeamertemplate{sidebar right}[sidebar theme]
+
+\begin{frame}{Appendix Overview}
+\tableofcontents[currentsection,hideothersubsections]
+\end{frame}
+
+\begin{frame}[label=McK2020_sales]
+\frametitle{Evidence of Impact}
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=23.2em]{pics/McK2020_sales.png}
+		\label{McKenzie(2020): Sales}
+	\end{figure}
+
+	\vspace{-1em}
+
+	\begin{itemize_2pt}
+		\item Small positive impact on sales (back to \hyperlink{McK2020_profits}{\beamergotobutton{profits}})
+	\end{itemize_2pt}
+
+\end{frame}
+
 \end{document}

### 2021-02-08 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added slide to MSE training refinements, etc.

@@
 \begin{frame}
-\frametitle{}
+\frametitle{Business Practices and Performance}
 	\begin{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		\item 5 major domains of practices
+		\item 5 major domains of business practices
 		\begin{enumerate_2pt}
-			\item Book-keeping
+			\item Book-keeping and accounting
 			\item ?
@@
 		\item Example practices:
-		\begin{itemize_2pt}
-			\item 
-			\item 
-			\item 
-			\item 
-			\item 
-		\end{itemize_2pt}
+		\begin{enumerate_2pt}
+			\item e.g., 
+			\item e.g., 
+			\item e.g., 
+			\item e.g., 
+			\item e.g., 
+		\end{enumerate_2pt}
 	\end{itemize_2pt}
@@
 \subsection{Classical MSME Training}
-
-%\begin{frame}
-%\begin{center}
-%{ \Huge \textcolor{black}{Classical MSME Training}}
-%\end{center}
-%\end{frame}
 
@@
 \begin{frame}
-\frametitle{Evidence of Impact}
+\frametitle{Impact on Performance}
 	\begin{itemize_2pt}
@@
 \begin{frame}[label=McK2020_profits]
-\frametitle{Evidence of Impact}
+\frametitle{Impact on Performance}
 
@@
 
-\subsection{Extensions of the Classical Approach}
-
-\begin{frame}
-\frametitle{Targeting Training}
+\begin{frame}
+\frametitle{Targeted Training}
+	Refinements of the classical model
+
+	\vspace{0.5em}
+
+	\begin{itemize_2pt}
+		\item Targeting \textcolor{bdf}{specific subgroups} of the population
+		\begin{itemize_2pt}
+			\item Treating individuals with particular promise (e.g., high-growth firms)
+			\item[] $\rightarrow$ \textcolor{bdf}{Maximizing impact} (or cost-effectiveness)
+			\item Serving marginalized or disadvantaged groups
+			\item[] $\rightarrow$ Alleviating \textcolor{bdf}{particularly severe constraints}
+			\item[] $\rightarrow$ 
+			\item \textcolor{bdf}{Maximizing statistical power} through homogeneity
+		\end{itemize_2pt}
+
+	\vspace{1.0em}
+
+		\item Training of skills in \textcolor{bdf}{particular domains}
+		\begin{itemize_2pt}
+			\item Alleviating \textcolor{bdf}{specific constraints}
+			\item Investigating mechanisms of treatment impact
+		\end{itemize_2pt}
+	\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Targeted Training}
 	Female entrepreneurs
@@
 \begin{frame}
-\frametitle{Targeting Training}
+\frametitle{Targeted Training}
 	Young entrepreneurs
@@
 \begin{frame}
-\frametitle{Targeting Training}
+\frametitle{Targeted Training}
 	High-growth businesses ("gazelles")
@@
 
-%---------------------
+\subsection{Extensions of the Classical Approach}
 

### 2021-02-08 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Many small tweaks

@@
 \usepackage{setspace}
-\usepackage{tikz}
 
@@
 \begin{frame}
-\frametitle{Business Practices of Small Firms}
+\frametitle{Business Practices in Small Firms}
 
@@
 	\begin{itemize_2pt}
-		\item 5 major domains of business practices
+		\item 4 major domains of business practices
 		\begin{enumerate_2pt}
 			\item Book-keeping and accounting
-			\item ?
-			\item ?
+			\item Financial planning
 			\item Inventory management and stock control
@@
 \begin{frame}
-\frametitle{Business Practices of Small Firms}
+\frametitle{Business Practices in Small Firms}
 	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
@@
 			\item e.g.,  
-			\item e.g., 
 		\end{enumerate_2pt}
@@
 	\begin{itemize_2pt}
-		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million beneficiary entrepreneurs; \citet{McKenzie2020})
+		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million entrepreneurs; \citet{McKenzie2020})
 		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
+
+		\vspace{0.5em}
+
 		\item Examples:
@@
 	%\textcolor{}{}
-	\item Training is delivered by 600 local certified trainers and by a pool of approximately 60 international master trainers. All trainers are also entrepreneurs.
+	\item \textcolor{red}{Training is delivered by 600 local certified trainers and by a pool of approximately 60 international master trainers. All trainers are also entrepreneurs.
 	\item Empretec Training Workshops offer different levels of instruction that include:
-	\item 6-day courses (48 hours); 32-hour (usually spread over 4 days) for micro-entrepreneurs with low levels of literacy; Interactive coaching based on real business challenges of participants.
-	\vspace{0.1in}
+	\item 6-day courses (48 hours); 32-hour (usually spread over 4 days) for micro-entrepreneurs with low levels of literacy; Interactive coaching based on real business challenges of participants.}
 	\end{itemize_2pt}
@@
 
-	Including more recent evaluations \citep{McKenzie2020}
+	Including more recent evaluations \citep[see,][]{McKenzie2020}
 
@@
 		\begin{itemize_2pt}
-			\item Treating individuals with particular promise (e.g., high-growth firms)
-			\item[] $\rightarrow$ \textcolor{bdf}{Maximizing impact} (or cost-effectiveness)
-			\item Serving marginalized or disadvantaged groups
-			\item[] $\rightarrow$ Alleviating \textcolor{bdf}{particularly severe constraints}
-			\item[] $\rightarrow$ 
-			\item \textcolor{bdf}{Maximizing statistical power} through homogeneity
+			\item Alleviating \textcolor{bdf}{particularly severe constraints}
+			\item[] $\rightarrow$ Marginalized or disadvantaged groups (e.g., women, youth)
+			\item  Maximizing \textcolor{bdf}{treatment impact} (or cost-effectiveness) 
+			\item[] $\rightarrow$ Promising entrepreneurs (e.g., high-growth firms)
+
+			\vspace{0.5em}
+
+			\item Plus: \textcolor{bdf}{Maximizing statistical power} through homogeneity
 		\end{itemize_2pt}
@@
 	\begin{itemize_2pt}
+	\item ?
+	\vspace{0.1in}
+	\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{On-site Consulting}
+
+	Consulting is intensive, tailored business advice
+	\begin{itemize_2pt}
+		\item Common interventions take 88 to 500 hours and more \citep{}
+	\item[] $\rightarrow$ Typically 2-4 hours, between twice weekly and monthly
+	\item Typical price point between \textcolor{red}{$USD$ 3,000 and 12,000 per firm} \citep{}
+	\item One-on-one or group-based
+	\vspace{0.1in}
+	\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{On-site Consulting}
+	\begin{itemize_2pt}
 	\item Bloom, et al. (2013); Karlan et al. (2015); Bruhn, Karlan, and Schoar (2019)
@@
 	\item \citep{Karlan2015} \citep{Bruhn2019}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{On-site Consulting}
-	\begin{itemize_2pt}
-	\item ?
 	\vspace{0.1in}
@@
 \frametitle{Heterogeneity of Impact}
-	\begin{itemize_2pt}
-	\item Heterogeneity of treatment effects poorly understood across different approaches
+
+Heterogeneity of treatment effects poorly understood across different approaches
+\begin{itemize_2pt}
 	\item Potential constraints are manifold, and likely context-dependent
-	\item Some already mentioned in passing:
-	\begin{itemize_2pt}
-		\item Credit constraints \citep[see, e.g.,][]{} McKenzie cash paper
-		\item Gender norms and constraints
-		\item Age-related network and knowledge/skill constraints
-	\end{itemize_2pt} 
-	\vspace{0.1in}
-	\end{itemize_2pt}
+
+\vspace{0.5em}
+
+	\item Some more obvious constraints (already mentioned in passing):
+	\begin{itemize_2pt}
+		\item \textcolor{bdf}{Credit constraints} \citep[see, e.g.,][]{} McKenzie cash paper
+		\item \textcolor{bdf}{Gender norms and constraints}
+		\item \textcolor{bdf}{Age-related} network and knowledge/skill \textcolor{bdf}{constraints}
+	\end{itemize_2pt} 
+\end{itemize_2pt}
+
+	\vspace{1.0em}
+
+$\rightarrow$ More recent literature highlights \textcolor{bdf}{behavioral constraints}
+
 \end{frame}
@@
 \begin{frame}
+\frametitle{Dynamic complementarities in skill acquisition}
+
+Complementarities in skills
+\begin{itemize_2pt}
+	\item
+\end{itemize_2pt}
+
+\vspace{1.0em}
+
+Learning styles
+\begin{itemize_2pt}
+	\item
+\end{itemize_2pt}
+
+\end{frame}
+
+\begin{frame}
 \frametitle{Family Commitments}
 \begin{itemize_2pt}
+	\item Interesting; \textcolor{red}{no beh const}
+	\vspace{0.1in}
+\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Segregated Markets}
+\begin{itemize_2pt}
+	\item Missing economies of scale
+	\item \textcolor{red}{Interesting; not behavioral constraint}
+	\vspace{0.1in}
+\end{itemize_2pt}
+\end{frame}
+
+%\begin{frame}
+%\frametitle{Identity Concerns}
+%\begin{itemize_2pt}
+%	\item 
+%	\vspace{0.1in}
+%\end{itemize_2pt}
+%\end{frame}
+
+\begin{frame}
+\frametitle{Aspirations}
+\begin{itemize_2pt}
 	\item 
@@
 \begin{frame}
-\frametitle{Identity Concerns}
-	\begin{itemize_2pt}
-	\item 
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Aspirations}
-	\begin{itemize_2pt}
-	\item 
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Local Relevance of Best Practices}
+\frametitle{Local Relevance of Business Practices}
 \begin{itemize_2pt}
@@
 
------
-
 %\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
 
+\appendix
 \begin{frame}[label=references, allowframebreaks]
@@
 
-\begin{frame}{Appendix Overview}
-\tableofcontents[currentsection,hideothersubsections]
-\end{frame}
+%\begin{frame}{Appendix Overview}
+%\tableofcontents[currentsection,hideothersubsections]
+%\end{frame}
 

### 2021-02-08 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Updated educ section with png, small tweaks

@@
 			\item[] $\rightarrow$ Marginalized or disadvantaged groups (e.g., women, youth)
-			\item  Maximizing \textcolor{bdf}{treatment impact} (or cost-effectiveness) 
+			\item  Maximizing \textcolor{bdf}{treatment impact} or cost-effectiveness 
 			\item[] $\rightarrow$ Promising entrepreneurs (e.g., high-growth firms)
@@
 \frametitle{Education and literacy}
+
+Most MSE entrepreneurs have limited education
+
+\vspace{-1.9em}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=27em]{pics/McK2017_educ.png}
+	\label{McKenzie(2017): Education and cognitive functioning}
+\end{figure}
+
+\vspace{-2.5em}
+
+\begin{itemize_2pt}
+	\item Typical small-firm owner dropped out of highschool
+	\item Test scores on digitspan and Raven's matrices about \% of Western university samples \textcolor{red}{\citep[comp.][]{}}
+\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Education and literacy}
+
+Potential for heuristics and rules of thumb
 \begin{itemize_2pt}

### 2021-02-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Updated consulting slides, and high-growth MSE training

@@
 	\begin{itemize_2pt}
-	\item
-	\item
+	\item Marcel Fafchamps and Simon Quinn
+	\item Small literature on business accelerators and incubators \citep[see, e.g.,][]{Cusolito2020, Gonzalez-Uribe2017, Gonzalez-Uribe2020}
 	\vspace{0.1in}
@@
 \frametitle{On-site Consulting}
-	\begin{itemize_2pt}
-	\item ?
-	\vspace{0.1in}
+
+Typical Consulting Intervention
+\begin{itemize_2pt}
+	\item Three-step procedure
+	\begin{enumerate_2pt}
+		\item Diagnostic of practices
+		\item Identification of areas of improvement
+		\item Problem solving within interactive relationship
+	\end{enumerate_2pt}
+
+	\item \textcolor{bdf}{Sustained and intensive}
+	\begin{itemize_2pt}
+		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018}
+		\item[] $\rightarrow$ Typically several months
+		\item[] $\rightarrow$ Meetings monthly to twice weekly, 2-4 hours
+		\item Total cost between \textcolor{red}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
+	\end{itemize_2pt}
+
+	\item One-on-one or group-based
+
+	\item \textcolor{bdf}{Often gov't-subsidized} (private contributions typically around 10\%)
+	\begin{itemize_2pt}
+		\item Empirical finding: Firms often unwilling to pay market price \citep{Maffioli2020}
+		\item[] $\rightarrow$ \textcolor{bdf}{Matching-grant programs}
+	\end{itemize_2pt}
+
 \end{itemize_2pt}
@@
 
-	Consulting is intensive, tailored business advice
-	\begin{itemize_2pt}
-		\item Common interventions take 88 to 500 hours and more \citep{}
-	\item[] $\rightarrow$ Typically 2-4 hours, between twice weekly and monthly
-	\item Typical price point between \textcolor{red}{$USD$ 3,000 and 12,000 per firm} \citep{}
-	\item One-on-one or group-based
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{On-site Consulting}
-	\begin{itemize_2pt}
-	\item Bloom, et al. (2013); Karlan et al. (2015); Bruhn, Karlan, and Schoar (2019)
-	\item Large firms: \citep{Bloom2013}; SMEs: \citep{Bruhn2018}
-	\item \citep{Karlan2015} \citep{Bruhn2019}
-	\vspace{0.1in}
-	\end{itemize_2pt}
+Examples in the literature
+\begin{itemize_2pt}
+	\item \citet{Bloom2013}; \citet{Karlan2015}; \citet{Bruhn2019}
+	\item \textcolor{bdf}{Consulting in SMEs}: \citet{Bruhn2018}
+	\begin{itemize_2pt}
+		\item ...
+		\item ...
+	\end{itemize_2pt}
+\end{itemize_2pt}
+
 \end{frame}

### 2021-02-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added slides on consulting, etc.

@@
 
-	Vast heterogeneity in business practices \textcolor{bdf}{also among small firms} \citep{McKenzie2009, McKenzie2017}..
-	\begin{itemize_2pt}
-		\item .. between countries
-		\item .. between industries
-		\item .. between firms
-	\end{itemize_2pt}
+	\citet{McKenzie2017} develop measurement instrument of \textcolor{bdf}{26 business practices} 
+	\begin{itemize_2pt}
+		\item Administered in \textcolor{bdf}{7 countries} in Asia, Africa, and South America
 
@@
 
-	In cross-section, business practices \textcolor{bdf}{associated with higher sales and profits} \citep{McKenzie2017}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Business Practices in Small Firms}
-
-	\citet{McKenzie2017} identify \textcolor{bdf}{set of XX best practices} most closely associated with business performance
-	\begin{itemize_2pt}
 		\item 4 major domains of business practices
@@
 		\end{enumerate_2pt}
-	\item[] $\rightarrow$ Association with performance robust across industries and countries
-	\item[] $\rightarrow$
+	\item[] $\rightarrow$ \textcolor{bdf}{Vast heterogeneity} in business practices \citep[comp.][]{Bloom2010}
+	\item[] $\rightarrow$ \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts
+	\item[] $\rightarrow$ \textcolor{bdf}{Strong persistent component} one year out ($r=0.59$)
 	\end{itemize_2pt}
@@
 %---------------------
+
+\begin{frame}
+\frametitle{Business Practices in Small Firms}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=23em]{pics/McKenzie2017_het.png}
+	\label{McKenzie(2017): Hetereogeneity}
+\end{figure}
+
+\begin{itemize_2pt}
+	\item Hetereogeneity in business practices of MSEs across countries \citep{McKenzie2017}
+\end{itemize_2pt}
+\end{frame}
 
@@
 	\begin{itemize_2pt}
-	\item Marcel Fafchamps and Simon Quinn
+	\item Marcel Fafchamps and Simon Quinn, \citep{McKenzie2017a}
 	\item Small literature on business accelerators and incubators \citep[see, e.g.,][]{Cusolito2020, Gonzalez-Uribe2017, Gonzalez-Uribe2020}
@@
 
-		\item[] $\rightarrow$ Different "pathways to profits" (title of the paper)
+		\item[] $\rightarrow$ Different "pathways to profits"
 
@@
 
+	\pause
+
 	\item \textcolor{bdf}{Sustained and intensive}
 	\begin{itemize_2pt}
-		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018}
+		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018, Karlan2015, Bruhn2019}
 		\item[] $\rightarrow$ Typically several months
@@
 
-	\item One-on-one or group-based
+	\pause
+
+	\item Typically one-on-one (also group-based)
 
@@
 
-Examples in the literature
-\begin{itemize_2pt}
-	\item \citet{Bloom2013}; \citet{Karlan2015}; \citet{Bruhn2019}
-	\item \textcolor{bdf}{Consulting in SMEs}: \citet{Bruhn2018}
-	\begin{itemize_2pt}
-		\item ...
-		\item ...
+SME consulting \citep{Bruhn2018}
+\begin{itemize_2pt}
+	\item Evaluation of a matching grants program in Mexico
+	\begin{itemize_2pt}
+		\item
 	\end{itemize_2pt}

### 2021-02-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Many small tweaks
Added eq and colors

@@
 	\item Bloom and van Reenen (2010): Heterogeneity \citep{Bloom2010}
-	\vspace{0.1in}
 	\end{itemize_2pt}
@@
 	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
-	\vspace{0.1in}
-	\end{itemize_2pt}
+	\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Business Practices in the Production Decision}
+
+Standard Production Decision
+	\begin{itemize_2pt}
+		\item Owner maximizes output $Y = f(A, L, M, K)$ at given wealth $W$:
+
+		\item[] $\boxed{\begin{aligned} \max _{K, M, L} &\{\textcolor{red}{p} &\ f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})-\textcolor{red}{w} \textcolor{bdf}{L}-\textcolor{red}{s} \textcolor{bdf}{M}-\textcolor{red}{r} \textcolor{bdf}{K}\} \end{aligned}}$
+		\item[] $\begin{aligned} \text{s.t.} &\ \textcolor{red}{w} \textcolor{bdf}{L}+\textcolor{red}{s} \textcolor{bdf}{M}+\textcolor{red}{r} \textcolor{bdf}{K} \leq \lambda W \end{aligned}$
+
+		\begin{itemize_2pt}
+			\item[] .. where $\textcolor{bdf}{L}$ is labor, $\textcolor{bdf}{M}$ is materials, and $\textcolor{bdf}{K}$ is capital.
+			\item[] ..
+where $\textcolor{red}{p}$ is the output price, $\textcolor{red}{w}$ the cost of labor, $\textcolor{red}{s}$ the cost of raw materials, $\textcolor{red}{r}$ cost of capital, and $\textcolor{red}{A}$ 							represents a productivity factor.
+		\end{itemize_2pt}
+	%\item Bloom et al. (2016) Bloom N, Sadun R, Van Reenen J (2016) Management as a technol- ogy? NBERWorking Paper 22327, National Bureau of Economic Research, Cambridge, MA.
+	%\item McKenzie2017 3.1.
+	\end{itemize_2pt}
+
 \end{frame}
@@
 	\includegraphics[width=23em]{pics/McKenzie2017_het.png}
-	\label{McKenzie(2017): Hetereogeneity}
+	\label{McKenzie(2017): Heterogeneity}
 \end{figure}

### 2021-02-10 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Finished eqs

--- 2021-02-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
@@
 \begin{frame}
-\frametitle{?}
+\frametitle{Heterogeneity in Business Practices}
 	\begin{itemize_2pt}
@@
 	\begin{itemize_2pt}
-	\item Bloom and van Reenen (2010): Heterogeneity \citep{Bloom2010}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Business Practices and Performance}
-	\begin{itemize_2pt}
-	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
-	\vspace{0.1in}
+	\item Bloom and van Reenen (2010): Heterogeneity across mid-sized and large firms \citep{Bloom2010}
 	\end{itemize_2pt}
@@
 	\item[] $\rightarrow$ \textcolor{bdf}{Vast heterogeneity} in business practices \citep[comp.][]{Bloom2010}
-	\item[] $\rightarrow$ \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts
 	\item[] $\rightarrow$ \textcolor{bdf}{Strong persistent component} one year out ($r=0.59$)
-	\end{itemize_2pt}
-\end{frame}
-
-%---------------------
-
-\begin{frame}
-\frametitle{Business Practices in Small Firms}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=23em]{pics/McKenzie2017_het.png}
-	\label{McKenzie(2017): Hetereogeneity}
-\end{figure}
-
-\begin{itemize_2pt}
-	\item Hetereogeneity in business practices of MSEs across countries \citep{McKenzie2017}
 	\end{itemize_2pt}
@@
 	\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Business Practices in Small Firms}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=23em]{pics/McKenzie2017_het.png}
+	\label{McKenzie(2017): Heterogeneity}
+\end{figure}
+
+\begin{itemize_2pt}
+	\item Hetereogeneity in business practices of MSEs across countries \citep{McKenzie2017}
+\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Business Practices in the Production Decision}
+
+Standard Production Decision
+	\begin{itemize_2pt}
+		\item Owner maximizes output $Y = f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})$ at given wealth $\textcolor{red}{W}$:
+
+		\item[] $\boxed{ \begin{aligned} \max _{\textcolor{bdf}{K, M, L}} &\{\textcolor{red}{p} \text{ } f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})-\textcolor{red}{w} \textcolor{bdf}{L}-\textcolor{red}{s} \textcolor{bdf}{M}-\textcolor{red}{r} \textcolor{bdf}{K}\} \end{aligned} }$
+		\item[] $\boxed{ \begin{aligned} \text{s.t.} &\ \textcolor{red}{w} \textcolor{bdf}{L}+\textcolor{red}{s} \textcolor{bdf}{M}+\textcolor{red}{r} \textcolor{bdf}{K} \leq \textcolor{red}{\lambda} \textcolor{red}{W} \end{aligned} }$
+
+		\vspace{0.5em}
+
+		\begin{itemize_2pt}
+			\item[] .. where $\textcolor{bdf}{L}$ is labor, $\textcolor{bdf}{M}$ is materials, and $\textcolor{bdf}{K}$ is capital.
+			\item[] .. where $\textcolor{red}{p}$ is the output price, $\textcolor{red}{w}$ the cost of labor, $\textcolor{red}{s}$ the cost of raw materials, and $\textcolor{red}{r}$ cost of capital
+			\item[] .. where $\textcolor{red}{A}$ represents a productivity factor and \textcolor{red}{$\lambda$} parameterizes borrowing constraints
+		\end{itemize_2pt}
+
+		\vspace{0.5em}
+
+		\item 2 general conceptualizations of business practices
+		\begin{enumerate_2pt}
+			\item As factor of production $\textcolor{bdf}{B}$ chosen by owner at market price $\textcolor{red}{p_{B}}$
+			\item As technology boosting productivity factor $\textcolor{red}{A}$
+			\item[] \citep[see,][]{Bloom2016, McKenzie2017}
+		\end{enumerate_2pt}
+
+	%\item Bloom et al. (2016) Bloom N, Sadun R, Van Reenen J (2016) Management as a technol- ogy? NBERWorking Paper 22327, National Bureau of Economic Research, Cambridge, MA.
+	%\item McKenzie2017 3.1.
+	\end{itemize_2pt}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Business Practices in the Production Decision}
+
+Further specific channels of impact
+\begin{enumerate_2pt}
+	\item Better negotiation practices may affect raw material prices $\textcolor{red}{s}$
+	\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend
+	\item Marketing practices may affect output price $\textcolor{red}{p}$ by changing demand
+
+	\item[] $\rightarrow$ Plausible association between business practices and revenues, profits, and business growth
+	\item[] $\rightarrow$ Prices ($\textcolor{red}{p}$, $\textcolor{red}{s}$, and $\textcolor{red}{p_{B}}$) and inputs ($\textcolor{bdf}{K}$, $\textcolor{bdf}{L}$, and $\textcolor{bdf}{M}$) likely endogenous to business practices $\textcolor{bdf}{B}$
+\end{enumerate_2pt}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Business Practices and Performance}
+	\begin{itemize_2pt}
+	\item Bloom and van Reenen (2019): Correlation with productivity across mid-sized and large firms \citep{Bloom2019}
+	\item McKenzie2017: \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts in small firms
+	\end{itemize_2pt}
 
@@
 	\end{itemize_2pt}
+
 \end{frame}

### 2021-02-10 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Small tweaks

@@
 \begin{frame}
-\frametitle{Heterogeneity in Business Practices}
+\frametitle{Business Practices in Large Companies}
 	\begin{itemize_2pt}
@@
 \begin{frame}
-\frametitle{Heterogeneity in Business Practices}
-	\begin{itemize_2pt}
-	\item Bloom and van Reenen (2010): Heterogeneity across mid-sized and large firms \citep{Bloom2010}
+\frametitle{Business Practices in Large Companies}
+	\begin{itemize_2pt}
+	\item Bloom and van Reenen (2010): Heterogeneity across mid-sized and large firms \citep{Bloom2010, Bloom2016, Bloom2019}
 	\end{itemize_2pt}
@@
 
-Further specific channels of impact
+Further potential channels of impact
 \begin{enumerate_2pt}
 	\item Better negotiation practices may affect raw material prices $\textcolor{red}{s}$
-	\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend
+	\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend \citep[see, e.g.,][]{Bruhn2013} %Bruhn JDEff 2013 Stimulating managerial capital young entrepreneurs Bosnia
 	\item Marketing practices may affect output price $\textcolor{red}{p}$ by changing demand
@@
 	\begin{itemize_2pt}
+	\item Using panel data and a model that treats managerial capital as technology, \citet{Bloom2016} find differences in management practices account for about 30\% of cross-country TFP differences
 	\item Bloom and van Reenen (2019): Correlation with productivity across mid-sized and large firms \citep{Bloom2019}
@@
 		\item ?
+		\item More severe constraints, e.g., due to household-level reallocation \citep{Bernhardt2019, deMel2009}
 	\vspace{0.1in}
@@
 
+\begin{frame}
+\frametitle{Sales vs. Profits}
+Direct measurements
+	\begin{itemize_2pt}
+	\item \citep{Fafchamps2012} Personalized Digital Assistants (PDAs) for MSEs in Ghana
+	\item[] $\rightarrow$ Vast majority of large changes in sales and profits genuine income volatility
+	\end{itemize_2pt}
+\end{frame}
+
 % ---------------------
@@
 (2018)
+\citep{Karlan2011}
 \vspace{0.1in}

### 2021-03-03 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added citations from literature
Latest draft (many tweaks (esp starting slides)

@@
 \definecolor{red}{RGB}{213,94,0}
+\definecolor{camel}{rgb}{0.76, 0.6, 0.42}
 %#09BADB #DB1A71
@@
 \setbeamerfont{itemize/enumerate subbody}{size={\fontsize{8}{8}}}
+\setbeamerfont{itemize/enumerate subsubbody}{size={\fontsize{7}{7}}}
 %\setbeamerfont{itemize/enumerate subbody}{family=\sffamily}
@@
 \linespread{1.25}
+
+\hypersetup{
+	colorlinks,
+    linkcolor= black, % internal links
+    citecolor= camel, % citations
+    urlcolor= black % external links/urls
+}
 
@@
 
-\subsection{Business Practices Around the World}
-
-\begin{frame}
-\frametitle{Business Practices in Large Companies}
-	\begin{itemize_2pt}
-	\item Bloom and van Reenen (2010, 2019): Business practices, motivation \citep{Bloom2010, Bloom2019}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Business Practices in Large Companies}
-	\begin{itemize_2pt}
-	\item Bloom and van Reenen (2010): Heterogeneity across mid-sized and large firms \citep{Bloom2010, Bloom2016, Bloom2019}
+\subsection{Business Practices and Productivity}
+
+\begin{frame}
+\frametitle{Dispersion of Business Practices}
+
+Stylized facts about firms
+\begin{table}[ht]
+\small
+\begin{center}
+\begin{tabular}{| c | c | c | c | c | c |}
+\hline
+Large \textcolor{cerulean}{country-level} 	& Large \textcolor{cerulean}{country-level} 	\\
+heterogeneity 			& heterogeneity 		\\
+in \textcolor{bdf}{productivity} 		& in \textcolor{bdf}{mgmt quality}	 	\\
+\hline
+Large \textcolor{cerulean}{firm-level} 		& Large \textcolor{cerulean}{firm-level} 		\\
+heterogeneity			& heterogeneity 		\\
+in \textcolor{bdf}{productivity}      	& in \textcolor{bdf}{mgmt quality} \\
+\hline
+\end{tabular}
+\end{center}
+\end{table}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Dispersion of Business Practices}
+
+Mid-sized and large companies
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=17.4em]{pics/Bloom2010_mgmtdispersion.png}
+	\label{Bloom(2010): Mgmt practices}
+\end{figure}
+
+\vspace{-1.0em}
+
+\begin{itemize_2pt}
+	\item Heterogeneity in mgmt practices across mid-sized and large firms \citep{Bloom2007, Bloom2010, Syverson2011}
+\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Dispersion of Business Practices}
+
+Public-sector companies
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=17.4em]{pics/Bloom2015_mgmtdispersion.png}
+	\label{Bloom(2015): Mgmt practices}
+\end{figure}
+
+\vspace{-1.0em}
+
+\begin{itemize_2pt}
+	\item Heterogeneity in mgmt practices across schools \citep{Bloom2015} and hospitals \citep{Bloom2020}
+\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Dispersion of Business Practices}
+
+Small firms
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=20em]{pics/McKenzie2017_mgmtdispersion.png}
+	\label{McKenzie(2017): Mgmt practices}
+\end{figure}
+
+\vspace{-1.0em}
+
+\begin{itemize_2pt}
+	\item Heterogeneity in business practices across micro and small enterprises \citep{McKenzie2017}
 \end{itemize_2pt}
@@
 \begin{frame}
-\frametitle{Business Practices in Small Firms}
-
-	\citet{McKenzie2017} develop measurement instrument of \textcolor{bdf}{26 business practices} 
-	\begin{itemize_2pt}
-		\item Administered in \textcolor{bdf}{7 countries} in Asia, Africa, and South America
-
+\frametitle{Characterization of Business Practices}
+
+Set of general best practices for small firms
+
+\begin{itemize_2pt}
+	\item \citet{McKenzie2017} identify set of \textcolor{bdf}{26 business practices} most closely associated with business performance
+
+	\begin{itemize_2pt}	
 	\vspace{0.5em}
 
-		\item 4 major domains of business practices
+		\item Validated in \textcolor{bdf}{7 countries} in Asia, Africa, and South America
+
+		\item \textcolor{bdf}{4 major domains} of business practices
 		\begin{enumerate_2pt}
@@
 		\end{enumerate_2pt}
-	\item[] $\rightarrow$ \textcolor{bdf}{Vast heterogeneity} in business practices \citep[comp.][]{Bloom2010}
-	\item[] $\rightarrow$ \textcolor{bdf}{Strong persistent component} one year out ($r=0.59$)
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Business Practices in Small Firms}
-	\citet{McKenzie2017} identify set of XX practices most closely associated with business performance
-	\begin{itemize_2pt}
+
+		\vspace{0.5em}
+
+		\item[] $\rightarrow$ \textcolor{bdf}{Strong persistent component} at one-year endline ($r=0.59$)
+	\end{itemize_2pt}
+
+\end{itemize_2pt}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Characterization of Business Practices}
+
+\begin{itemize_2pt}
+	\item \citet{McKenzie2017} identify set of \textcolor{bdf}{26 business practices} most closely associated with business performance
+
+	\begin{itemize_2pt}	
+	\vspace{0.5em}
+
 		\item Example practices:
+
 		\begin{enumerate_2pt}
@@
 		\end{enumerate_2pt}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Business Practices in Small Firms}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics[width=23em]{pics/McKenzie2017_het.png}
-	\label{McKenzie(2017): Heterogeneity}
-\end{figure}
-
-\begin{itemize_2pt}
-	\item Hetereogeneity in business practices of MSEs across countries \citep{McKenzie2017}
-\end{itemize_2pt}
+
+		\vspace{0.5em}
+
+	\end{itemize_2pt}
+
+\item[] $\rightarrow$ How exactly should we think about business practices translating into performance gains?
+
+\end{itemize_2pt}
+
 \end{frame}
@@
 			\item[] .. where $\textcolor{bdf}{L}$ is labor, $\textcolor{bdf}{M}$ is materials, and $\textcolor{bdf}{K}$ is capital.
-			\item[] .. where $\textcolor{red}{p}$ is the output price, $\textcolor{red}{w}$ the cost of labor, $\textcolor{red}{s}$ the cost of raw materials, and $\textcolor{red}{r}$ cost of capital
+			\item[] .. where $\textcolor{red}{w}$ the cost of labor, $\textcolor{red}{s}$ the cost of raw materials, $\textcolor{red}{r}$ cost of capital, and $\textcolor{red}{p}$ is the output price
 			\item[] .. where $\textcolor{red}{A}$ represents a productivity factor and \textcolor{red}{$\lambda$} parameterizes borrowing constraints
 		\end{itemize_2pt}
+
+		\pause
 
@@
 			\item As technology boosting productivity factor $\textcolor{red}{A}$
-			\item[] \citep[see,][]{Bloom2016, McKenzie2017}
+			\item[] \citep[see,][]{Bloom2016, McKenzie2017, Quinn2019}
 		\end{enumerate_2pt}
 
-	%\item Bloom et al. (2016) Bloom N, Sadun R, Van Reenen J (2016) Management as a technol- ogy? NBERWorking Paper 22327, National Bureau of Economic Research, Cambridge, MA.
-	%\item McKenzie2017 3.1.
 	\end{itemize_2pt}
@@
 
-Further potential channels of impact
+Standard Production Decision
+\begin{itemize_2pt}
+	\item \tiny Owner maximizes output $Y = f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})$ at given wealth $\textcolor{red}{W}$:
+
+	\item[] $\boxed{ \begin{aligned} \max _{\textcolor{bdf}{K, M, L}} &\{\textcolor{red}{p} \text{ } f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})-\textcolor{red}{w} \textcolor{bdf}{L}-\textcolor{red}{s} \textcolor{bdf}{M}-\textcolor{red}{r} \textcolor{bdf}{K}\} \end{aligned} }$
+	\item[] $\boxed{ \begin{aligned} \text{s.t.} &\ \textcolor{red}{w} \textcolor{bdf}{L}+\textcolor{red}{s} \textcolor{bdf}{M}+\textcolor{red}{r} \textcolor{bdf}{K} \leq \textcolor{red}{\lambda} \textcolor{red}{W} \end{aligned} }$
+
+	\vspace{0.5em}
+
+	\item \normalsize Further specific channels of impact
 	\begin{enumerate_2pt}
 		\item Better negotiation practices may affect raw material prices $\textcolor{red}{s}$
-	\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend \citep[see, e.g.,][]{Bruhn2013} %Bruhn JDEff 2013 Stimulating managerial capital young entrepreneurs Bosnia
+		\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend \citep[see, e.g.,][]{Bruhn2013}
 		\item Marketing practices may affect output price $\textcolor{red}{p}$ by changing demand
@@
 	\end{enumerate_2pt}
+\end{itemize_2pt}
 
@@
 	\item Using panel data and a model that treats managerial capital as technology, \citet{Bloom2016} find differences in management practices account for about 30\% of cross-country TFP differences
-	\item Bloom and van Reenen (2019): Correlation with productivity across mid-sized and large firms \citep{Bloom2019}
-	\item McKenzie2017: \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts in small firms
+	\item Correlation with productivity in mid-sized and large firms \citep{Bloom2019}
+	\item \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts in small firms \citep{McKenzie2017}
 	\end{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million entrepreneurs; \citet{McKenzie2020})
+		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million entrepreneurs; \citet{McKenzie2021})
 		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
@@
 \frametitle{Typical Training Program}
+	Demand for business training
+
+	\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=17em]{pics/Maffioli2020_demand.png}
+	\label{Maffioli(2020): Demand}
+\end{figure}
+
+	\begin{itemize_2pt}
+	\item Demand curve for business training in Jamaica: $\sim$60-70\% willing to pay half, $\sim$10\% full price \citep{Maffioli2020}
+	\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Typical Training Program}
 	Delivery 
@@
 
-	Including more recent evaluations \citep[see,][]{McKenzie2020}
+	Including more recent evaluations \citep[see,][]{McKenzie2021}
 
@@
 		\item \textcolor{bdf}{Most common type of targeted training} (potentially complementary to classical microfinance model)
-		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016,McKenziePuerto2020}
+		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016, McKenziePuerto2021}
 		\item ?
@@
 	\begin{enumerate_2pt}
-		\item Diagnostic of practices
-		\item Identification of areas of improvement
-		\item Problem solving within interactive relationship
+		\item Diagnosing practices
+		\item Identifying areas of improvement
+		\item Joint and interactive problem solving
 	\end{enumerate_2pt}
@@
 
-	\item \textcolor{bdf}{Often gov't-subsidized} (private contributions typically around 10\%)
-	\begin{itemize_2pt}
-		\item Empirical finding: Firms often unwilling to pay market price \citep{Maffioli2020}
+	\item \textcolor{bdf}{Often gov't-subsidized} (private contributions typically $\sim$10\%) \\
+	\begin{itemize_2pt}
+		%\item Empirical finding: Firms often unwilling to pay market price \citep{Maffioli2020}
 		\item[] $\rightarrow$ \textcolor{bdf}{Matching-grant programs}
@@
 	\item McKenzie cash JDE paper
+	\item \citep{Gine2021}
+	\item \cite{Berge2015}
+	\item \cite{deMel2014}
 	\vspace{0.1in}
@@
 
-\subsection{Measurement of Firm Performance}
+\subsection{Measuring Firm Performance}
 
@@
 		\includegraphics[width=23.5em]{pics/McK2020_profits.png}
-		\label{McKenzie(2020): Profits}
+		\label{McKenzie(2020): Profits2}
 	\end{figure}
@@
 		\item \textcolor{bdf}{Extremely wide confidence intervals} on impact estimates
-	\vspace{0.1in}
-	\end{itemize_2pt}
+	\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Self-reports and aggregation}
+
+\citep{Garlick2019}
+\citep{deMel2009}
+\citep{Bernhardt2019}
+
 \end{frame}
@@
 \frametitle{References}
-\bibliographystyle{econometrica}
-\bibliography{SME_library}
+\bibliographystyle{chicago}
+\bibliography{businessTraining}
 \end{frame}

### 2021-03-08 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Updated slides (final version for Bocconi seminar)

@@
 \begin{itemize_2pt}
-	\item Heterogeneity in mgmt practices across mid-sized and large firms \citep{Bloom2007, Bloom2010, Syverson2011}
+	\item Heterogeneity in mgmt practices across mid-sized and large firms \textcolor{camel}{(Bloom et al., 2007, Bloom et al., 2010, Syverson, 2011)}
 \end{itemize_2pt}
@@
 
-\end{itemize_2pt}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Characterization of Business Practices}
-
-\begin{itemize_2pt}
-	\item \citet{McKenzie2017} identify set of \textcolor{bdf}{26 business practices} most closely associated with business performance
-
-	\begin{itemize_2pt}	
-	\vspace{0.5em}
-
-		\item Example practices:
-
-		\begin{enumerate_2pt}
-			\item e.g., 
-			\item e.g., 
-			\item e.g., 
-			\item e.g.,  
-		\end{enumerate_2pt}
-
-		\vspace{0.5em}
-
-	\end{itemize_2pt}
-
 	\item[] $\rightarrow$ How exactly should we think about business practices translating into performance gains?
@@
 \end{frame}
+
+%\begin{frame}
+%\frametitle{Characterization of Business Practices}
+
+%\begin{itemize_2pt}
+%	\item \citet{McKenzie2017} identify set of \textcolor{bdf}{26 business practices} most closely associated with business performance
+
+%	\begin{itemize_2pt}	
+%	\vspace{0.5em}
+
+%		\item Example practices:
+
+%		\begin{enumerate_2pt}
+%			\item e.g., 
+%			\item e.g., 
+%			\item e.g., 
+%			\item e.g.,  
+%		\end{enumerate_2pt}
+
+%		\vspace{0.5em}
+
+%	\end{itemize_2pt}
+
+%\end{itemize_2pt}
+
+%\end{frame}
 
@@
 			\item As factor of production $\textcolor{bdf}{B}$ chosen by owner at market price $\textcolor{red}{p_{B}}$
-			\item As technology boosting productivity factor $\textcolor{red}{A}$
-			\item[] \citep[see,][]{Bloom2016, McKenzie2017, Quinn2019}
+			\item As technology affecting productivity factor $\textcolor{red}{A}$
+			\item[] See, e.g., \textcolor{camel}{Bloom et al., (2016), McKenzie and Woodruff (2017)} %Quinn2019}
 		\end{enumerate_2pt}
@@
 
-Standard Production Decision
-\begin{itemize_2pt}
-	\item \tiny Owner maximizes output $Y = f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})$ at given wealth $\textcolor{red}{W}$:
-
-	\item[] $\boxed{ \begin{aligned} \max _{\textcolor{bdf}{K, M, L}} &\{\textcolor{red}{p} \text{ } f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})-\textcolor{red}{w} \textcolor{bdf}{L}-\textcolor{red}{s} \textcolor{bdf}{M}-\textcolor{red}{r} \textcolor{bdf}{K}\} \end{aligned} }$
-	\item[] $\boxed{ \begin{aligned} \text{s.t.} &\ \textcolor{red}{w} \textcolor{bdf}{L}+\textcolor{red}{s} \textcolor{bdf}{M}+\textcolor{red}{r} \textcolor{bdf}{K} \leq \textcolor{red}{\lambda} \textcolor{red}{W} \end{aligned} }$
-
-	\vspace{0.5em}
-
-	\item \normalsize Further specific channels of impact
+\begin{itemize_2pt}
+
+	\item \normalsize Further specific channels of potential impact
 	\begin{enumerate_2pt}
-		\item Better negotiation practices may affect raw material prices $\textcolor{red}{s}$
-		\item Record-keeping and financial planning practices may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend \citep[see, e.g.,][]{Bruhn2013}
-		\item Marketing practices may affect output price $\textcolor{red}{p}$ by changing demand
+		\item Better \textcolor{bdf}{negotiation practices} may affect raw material prices $\textcolor{red}{s}$
+		\item \textcolor{bdf}{Record-keeping} and \textcolor{bdf}{financial planning practices} may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend (see, e.g., \textcolor{camel}{Bruhn and Zia, 2013})
+		\item \textcolor{bdf}{Marketing practices} may affect output price $\textcolor{red}{p}$ by changing demand
+
+\vspace{1.0em}
 
 		\item[] $\rightarrow$ Plausible association between business practices and revenues, profits, and business growth
+
+\vspace{0.5em}
+
 		\item[] $\rightarrow$ Prices ($\textcolor{red}{p}$, $\textcolor{red}{s}$, and $\textcolor{red}{p_{B}}$) and inputs ($\textcolor{bdf}{K}$, $\textcolor{bdf}{L}$, and $\textcolor{bdf}{M}$) likely endogenous to business practices $\textcolor{bdf}{B}$
@@
 \frametitle{Business Practices and Performance}
-	\begin{itemize_2pt}
-	\item Using panel data and a model that treats managerial capital as technology, \citet{Bloom2016} find differences in management practices account for about 30\% of cross-country TFP differences
-	\item Correlation with productivity in mid-sized and large firms \citep{Bloom2019}
-	\item \textcolor{bdf}{Robust association with performance and firm survival} across industries and contexts in small firms \citep{McKenzie2017}
+
+	Using panel data and a model that treats managerial capital as technology, \citet{Bloom2016} find differences in management practices account for about 30\% of cross-country TFP differences
+	\begin{itemize_2pt}
+		\item Robust correlation with productivity in \textcolor{bdf}{mid-sized and large firms}, and in the \textcolor{bdf}{public sector} \citep{Bloom2015,Bloom2020} %\citep{Bloom2019}
+		\item Robust correlation with performance and firm survival across industries and contexts in \textcolor{bdf}{small firms} \citep{McKenzie2017}
 		\end{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		\item Does adoption of "best practices" \emph{cause} performance to increase?
+		\item Does adoption of best practices \emph{cause} performance to increase?
 		\item How can adoption of practices best be encouraged?
@@
 \frametitle{Typical Training Program}
-	Content
-	\begin{itemize_2pt}
-	%\textcolor{}{}
-	\item \textcolor{red}{Training is delivered by 600 local certified trainers and by a pool of approximately 60 international master trainers. All trainers are also entrepreneurs.
-	\item Empretec Training Workshops offer different levels of instruction that include:
-	\item 6-day courses (48 hours); 32-hour (usually spread over 4 days) for micro-entrepreneurs with low levels of literacy; Interactive coaching based on real business challenges of participants.}
-	\end{itemize_2pt}
+Stylized facts on MSME trainings
+\begin{itemize_2pt}
+	\item Group of 15 to 40 entrepreneurs per trainer
+	\item In-class (often with elements of active and interactive learning)
+	\item Period of up to two weeks	
+	\item Foci of typical syllabi
+	\begin{itemize_2pt}
+		\item \textcolor{bdf}{Encourage start-up}: Business ideas and business plans, permits, costing, pricing, and budgeting
+		\item \textcolor{bdf}{Grow existing businesses}: Record-keeping, accounting, and financial planning, marketing, human resources and hiring, stock and inventory management
+	\end{itemize_2pt}
+
+	\item Average training program not inexpensive (USD 177 per person for ILO training, \citet{Lieshout2017})
+	\item[] $\rightarrow$ Typical training program \textcolor{bdf}{highly subsidized}
+	\item[] \quad (Median contribution 10\% of full price)
+
+\end{itemize_2pt}
+
 \end{frame}
@@
 \frametitle{Typical Training Program}
+
 Demand for business training
@@
 \end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Typical Training Program}
-	Delivery 
-	\begin{itemize_2pt}
-	\item %\textcolor{}{}
-	\vspace{0.1in}
-	\end{itemize_2pt}
+
 \end{frame}
@@
 \frametitle{Impact on Performance}
-	\begin{itemize_2pt}
-	\item First wave (Karlan and Valdivia, 2011, Bruhn and Zia, 2013; Giné and Mansuri, 2014; Field, et al., 2010; Bulte et al., 2017; Anderson, Chandy, and Zia, 2018)
-					 \citep{Karlan2011} \citep{Field2010} \citet{Gine2014} \citep{Bruhn2013} \citep{Bulte2017} \citep{Anderson2018}
-	\vspace{0.1in}
+First wave of evaluations
+	\begin{itemize_2pt}
+	\item  Headline result: \textcolor{bdf}{No impact on business performance}
+	\begin{itemize_2pt}
+		\item Modest short-term adoption of practices (long-term fade-out)
+		\item Null-effect on business sales and profits
+		\item Early examples: \textcolor{camel}{Karlan and Valdivia, 2011, Bruhn and Zia, 2013; Giné and Mansuri, 2014; Field, et al., 2010} 
+		%\item Later examples: \textcolor{camel}{Bulte et al., 2017; Anderson, Chandy, and Zia, 2018}
+
+	\end{itemize_2pt}
 \end{itemize_2pt}
@@
 \frametitle{Impact on Performance}
-	\begin{itemize_2pt}
-	\item Econometric and implementation issues \citep{McKenzie2014}
-	\vspace{0.1in}
+
+Econometric and implementation issues \citep{McKenzie2014}
+	\begin{itemize_2pt}
+		\item \textcolor{bdf}{Lack of statistical power} with MDEs often substantially above policy-relevant levels
+		\begin{itemize_2pt}	
+			\item Small samples (typically $N=200-400$ per treatment cell)
+			\item Typical attendance between 40 and 70\%
+			\item Typically substantial rates of survey attrition (up to $24-28\%$)
+			\item Large heterogeneity in age, education, training delivery and costs, etc.
+		\end{itemize_2pt}
+
+		\pause
+
+		\item Endline follow-ups \textcolor{bdf}{very short-term} (typically 1-2 years out)
+
+		\item Sources of \textcolor{bdf}{selection bias} by treatment status
+		\begin{itemize_2pt}	
+			\item Firm survival can be endogenous on treatment
+			\item Record-keeping likely to increase reporting accuracy
+			\item Clear potential for differential experimenter demand effects
+		\end{itemize_2pt}
+
+		\item Most trainings offered at \textcolor{bdf}{no private costs}
+		\begin{itemize_2pt}
+			\item Potential for reverse sunken cost fallacy in valuation \citep[see,][]{Maffioli2020}
+		\end{itemize_2pt}
+
+		%\item Focus on \textcolor{bdf}{existing businesses} and \textcolor{bdf}{middle-aged entrepreneurs} (typical age 35 to 45 years)
+
 	\end{itemize_2pt}
@@
 
-	Including more recent evaluations \citep[see,][]{McKenzie2021}
+	Recent meta-study \citep{McKenzie2021}
 
@@
 		\centering
-		\includegraphics[width=21.5em]{pics/McK2020_profits.png}
+		\includegraphics[width=20em]{pics/McK2020_profits.png}
 		\label{McKenzie(2020): Profits}
@@
 	\begin{itemize_2pt}
-		\item Small positive impact on practice adoption, profits, and \hyperlink{McK2020_sales}{\beamergotobutton{sales}}
+		\item \textcolor{bdf}{Small positive impact} on practice adoption and performance 
+		\item[] $\rightarrow$ Estimated 10.1\% plus in profits, and 4.7\% plus in \hyperlink{McK2020_sales}{\beamergotobutton{sales}}
 	\end{itemize_2pt}
@@
 
-		\item Training of skills in \textcolor{bdf}{particular domains}
+		\item Training of \textcolor{bdf}{specific clusters of business practices}
 		\begin{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		\item \textcolor{bdf}{Most common type of targeted training} (potentially complementary to classical microfinance model)
-		\item Example: Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2016, McKenziePuerto2021}
-		\item ?
-		\item More severe constraints, e.g., due to household-level reallocation \citep{Bernhardt2019, deMel2009}
-	\vspace{0.1in}
+		\item Examples: 
+		\begin{itemize_2pt}
+			\item Gender and Enterprise Together (GET Ahead, ILO; \textcolor{camel}{Bulte et al., 2017}, \textcolor{camel}{McKenzie and Puerto, 2021})
+			\item Start and Improve Your Business (SIYB, IFC; \textcolor{camel}{de Mel et al., 2014})
+		\end{itemize_2pt}
+		\item \textcolor{bdf}{Most common type of targeted training} (complementary to classical microfinance model)
+
+		\vspace{0.5em}
+
+		\item Structural reasons
+		\begin{itemize_2pt}
+			\item Women overrepresented in subsistence entrepreneurship
+			\item Female entrepreneurs often subject to more severe constraints (e.g., due to household-level reallocation; see, e.g., \textcolor{camel}{Bernhardt et al.
+2019}, \textcolor{camel}{de Mel et al., 2009})
+		\end{itemize_2pt}
 	\end{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		\item Typically embedded as entrepreneurship programs in school and university
-		\item Example: University final year course in Tunisia \citep{Alaref2020}
-		\begin{itemize_2pt}
-			\item
-			\item
-		\end{itemize_2pt}
-	\end{itemize_2pt}
-\end{frame}
+		\item Typically embedded as \textcolor{bdf}{entrepreneurship courses in school or university} (business concepts and soft skills)
+		\item Example: Final year university course in Tunisia \textcolor{camel}{(Alaref et al., 2020)}
+		\begin{itemize_2pt}
+			\item Positive impact on business entry tapers off after 4 years
+		\end{itemize_2pt}
+	\end{itemize_2pt}
+
+\pause
+
+\vspace{1.0em}
+
+High-growth businesses ("gazelles")
+\begin{itemize_2pt}
+	\item Extensive-margin prediction of future MSE growth is hard \textcolor{camel}{(Fafchamps and Woodruff, 2017)} 
+	\begin{itemize_2pt}
+		\item Survey, ability measure, expert panel all explain unique variation
+		\item But: Business training for predicted gazelles shows no impact
+	\end{itemize_2pt}
+
+	\item \citet{McKenzie2017a} finds more encouraging results with a nationwide business plan competition in Nigeria
+
+	\item Small literature on business accelerators and incubators
+	\begin{itemize_2pt}
+		\item See, e.g., \textcolor{camel}{Cusolito et al., 2020}, \textcolor{camel}{Gonzalez-Uribe et al., 2017}, \textcolor{camel}{Gonzalez-Uribe et al. 2020}
+	\end{itemize_2pt}
+\end{itemize_2pt}
+
+\end{frame}
+
+%---------------------
 
@@
 \frametitle{Targeted Training}
-	High-growth businesses ("gazelles")
-	\begin{itemize_2pt}
-	\item Marcel Fafchamps and Simon Quinn, \citep{McKenzie2017a}
-	\item Small literature on business accelerators and incubators \citep[see, e.g.,][]{Cusolito2020, Gonzalez-Uribe2017, Gonzalez-Uribe2020}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-%---------------------
-
-\begin{frame}
-\frametitle{Training Specific Domains}
-
-	\citet{Anderson2018} assign 852 South African MSEs to distinct types of training:
+
+Training of specific clusters of practices
+\begin{itemize_2pt}	
+	\item \citet{Anderson2018} assign 852 South African micro-entrepreneurs to distinct types of training:
+
+	\vspace{0.5em}
+
 	\begin{enumerate_2pt}
 		\item Marketing/sales skills
+		\item[]
 		\item[]
@@
 		\item[]
+		\item[]
 	\end{enumerate_2pt}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Training Specific Domains}
-
-	\citet{Anderson2018} assign 852 South African businesses to two distinct trainings:
+\end{itemize_2pt}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Targeted Training}
+
+Training of specific clusters of practices
+\begin{itemize_2pt}	
+	\item \citet{Anderson2018} assign 852 South African micro-entrepreneurs to two distinct trainings:
+
+	\vspace{0.5em}
+
 	\begin{enumerate_2pt}
@@
 		\begin{itemize_2pt}
+			\item "Growth focus" on higher sales, stock investments, and hiring
 			\item 61\% increase in profits
-			\item "Growth focus" on higher sales, stock investments, and hiring
 			\item[] $\rightarrow$ Benefits new businesses ($=$ less market exposure)
@@
 		\begin{itemize_2pt}
+			\item "Efficiency focus" on lower costs
 			\item 41\% increase in profits
-			\item "Efficiency focus" on lower costs
 			\item[] $\rightarrow$ Benefits established businesses
@@
 
+	\end{enumerate_2pt}
+
 		\item[] $\rightarrow$ Different "pathways to profits"
 
-	\end{enumerate_2pt}
+\end{itemize_2pt}
 
@@
 
-Typical Consulting Intervention
+Stylized facts on business consulting
 \begin{itemize_2pt}
@@
 
+	\item Typically one-on-one (also group-based)
+
 	\item \textcolor{bdf}{Sustained and intensive}
 	\begin{itemize_2pt}
-		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018, Karlan2015, Bruhn2019}
+		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018} %Karlan2015, Bruhn2019
 		\item[] $\rightarrow$ Typically several months
@@
 
-	\pause
-
-	\item Typically one-on-one (also group-based)
-
 	\item \textcolor{bdf}{Often gov't-subsidized} (private contributions typically $\sim$10\%) \\
@@
 
-SME consulting \citep{Bruhn2018}
-\begin{itemize_2pt}
-	\item Evaluation of a matching grants program in Mexico
-	\begin{itemize_2pt}
-		\item
-	\end{itemize_2pt}
-\end{itemize_2pt}
+Example: Subsidized matching grant program for MSMEs in Mexico \citep{Bruhn2018}
+\begin{itemize_2pt}
+
+	\item Weekly 4-hour visits over one year
+	\item USD 12,000 per person (subsidized at $70-90\%$)
+	\item \textcolor{bdf}{Small positive impacts on profits and ROA after 1 year}
+
+	\vspace{0.5em}
+
+	\item Using admin data, \textcolor{bdf}{57\% higher employment after 5 years}
+	\begin{itemize_2pt}
+		\item Availability issues of admin data may have introduced selection
+		\item Not clear if effects concentrated among few businesses
+	\end{itemize_2pt}
+\end{itemize_2pt}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=15em]{pics/Bruhn2018_consult.png}
+	\label{Bruhn (2018): Consulting}
+\end{figure}
 
@@
 \begin{itemize_2pt}
-	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
-	\item ?
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Multimedia delivery}
-	TV shows
-	\begin{itemize_2pt}
-	\item Examples: Ruka Juu in Tanzania \citep{Bjorvatn2020} and El Mashroua in Egypt \citep{Barsoum2018}
-	\item ?
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Multimedia delivery}
+	\item Examples: \textcolor{bdf}{Reality show competitions} in Tanzania \textcolor{camel}{(Bjorvatn et al., 2020)} and Egypt \textcolor{camel}{(Barsoum et al., 2018)}
+	\item Differential random incentivization schemes
+	\item[] $\rightarrow$ No impact on business knowledge and business entry 
+	\item[] $\rightarrow$ But: \textcolor{bdf}{High viewership} (conventional MDEs substantially above policy-relevant levels)
+
+\end{itemize_2pt}
+
+\pause
+
+\vspace{1.0em}
+
 Text messages
 \begin{itemize_2pt}
-	\item \citep{Cole2019} \citep{Acimovic2020}
-	\vspace{0.1in}
+	\item Examples: 
+	\begin{itemize_2pt}
+		\item Heuristics-based business advice \textcolor{camel}{(Cole and Schoar, 2019)}
+		\item Daily personalised inventory level recommendations \textcolor{camel}{(Acimovic et al., 2020)}
+	\end{itemize_2pt}
+	\item[] $\rightarrow$ Small literature with generally \textcolor{camel}{mixed results or null effects}
+	\item[] $\rightarrow$ But: \textcolor{bdf}{MDEs substantially above policy-relevant levels}
+	\item[] $\rightarrow$ But: \textcolor{bdf}{Complementarities} between in-person training and SMS reminders still unclear
 \end{itemize_2pt}
@@
 
-\begin{frame}
-\frametitle{Complementary Constraints}
-	\begin{itemize_2pt}
-	\item McKenzie cash JDE paper
-	\item \citep{Gine2021}
-	\item \cite{Berge2015}
-	\item \cite{deMel2014}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Complementary Constraints}
-	\begin{itemize_2pt}
-	\item McKenzie cash JDE paper
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
+%\begin{frame}
+%\frametitle{Complementary Constraints}
+%	\begin{itemize_2pt}
+%	\item Core idea: \textcolor{bdf}{Address multiple interrelated constraints}
+%	\item Examples: de Mel et al. (2014), Berge et al. (2015), Gine and Iacovone (2021)
+%	\end{itemize_2pt}
+%\end{frame}
 
@@
 \begin{frame}
-\frametitle{Imprecision of Outcome Measures}
+\frametitle{Variation in Outcome Measures}
 
@@
 \begin{frame}
-\frametitle{Self-reports and aggregation}
-
-\citep{Garlick2019}
-\citep{deMel2009}
-\citep{Bernhardt2019}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Self-reports and aggregation}
-	\begin{itemize_2pt}
-	\item Self-reports of aggregate \citep{deMel2009}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Self-reports and aggregation}
-	\begin{itemize_2pt}
-	\item Disaggregating quantities in self-reports \citep{deMel2009}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Self-reports and aggregation}
-	\begin{itemize_2pt}
-	\item Direct measures \citep{deMel2009}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
+\frametitle{Variation in Outcome Measures}
+
+Alternative measures of business profits \textcolor{camel}{(de Mel et al., 2009)}
+	\begin{itemize_2pt}
+		\item 15-16 unannounced visits during one month
+		\item Random assignment of profit measure, and accounting diaries, and recall span
+	\end{itemize_2pt}
+
+	\pause
+
+	\vspace{0.5em}
+
+	\begin{enumerate_2pt}
+		\item \textcolor{bdf}{Self-reported profits most accurate measure}
+		\item[] $\rightarrow$ Correlation with sales-minus-expenditures only $r=0.3$
+		\item \textcolor{bdf}{Accounting diaries have no effect on profits} (but on sales)
+		\item With recall over 4 months vs. 1 month, entrepreneurs \textcolor{bdf}{understate revenues by $10 - 15 \%$ due to memory} 
+		\item Entrepreneurs estimate average rival business to \textcolor{bdf}{underreport sales by 30\%}
+	\end{enumerate_2pt}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Variation in Outcome Measures}
+
+Survey media and frequencies {(Garlick et al, 2019)}
+\begin{itemize_2pt}
+	\item 12-week panel with detailed measurements of employees, profits, sales, assets, transfers, etc.
+
+	\item Random assignment to different survey modes and frequencies
+	\begin{enumerate_2pt}
+		\item Monthly in-person
+		\item Weekly in-person
+		\item Weekly phone
+	\end{enumerate_2pt}
+
+	\pause
+
+	\item Survey medium
+	\begin{itemize_2pt}
+		\item \textcolor{bdf}{All survey modes generally yield similar statistical moments}
+		\item Phone surveys yield higher within-firm, cross-temporal variation
+		\item[] (Some evidence for greater social desirability bias.)
+	\end{itemize_2pt}
+
+	\item Survey frequency
+	\begin{itemize_2pt}
+		\item \textcolor{bdf}{Higher frequency generally does not alter statistical moments}
+		\item No evidence for higher attrition
+	\end{itemize_2pt}
+\end{itemize_2pt}
+\end{frame}
+
+%\begin{frame}
+%\frametitle{Variation in Outcome Measures}
+%	\begin{itemize_2pt}
+%		\item \citep{deMel2009}
+%		\item \citep{Bernhardt2019}
+%	\end{itemize_2pt}
+%\end{frame}
+
+%\begin{frame}
+%\frametitle{Self-reports and aggregation}
+%	\begin{itemize_2pt}
+%	\item Direct measures \citep{deMel2009}
+%	\vspace{0.1in}
+%	\end{itemize_2pt}
+%\end{frame}
 
@@
 \begin{frame}
-\frametitle{Sales vs. Profits}
-	\begin{itemize_2pt}
-	\item  \citep{deMel2009}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Sales vs. Profits}
-	\begin{itemize_2pt}
-	\item \citep{deMel2009}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Sales vs. Profits}
-Direct measurements
-	\begin{itemize_2pt}
-	\item \citep{Fafchamps2012} Personalized Digital Assistants (PDAs) for MSEs in Ghana
-	\item[] $\rightarrow$ Vast majority of large changes in sales and profits genuine income volatility
-	\end{itemize_2pt}
-\end{frame}
-
-% ---------------------
-
-\begin{frame}
-\frametitle{?}
-\begin{itemize_2pt}
-	\item 
-	\vspace{0.1in}
-\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{?}
-\begin{itemize_2pt}
-	\item 
-	\vspace{0.1in}
+\frametitle{Variation in Outcome Measures}
+Technological aids \textcolor{camel}{(Fafchamps et al., 2012)}
+	\begin{itemize_2pt}
+	\item Random assignment to Personalized Digital Assistants (PDAs)
+	\
+	\item Potential channels of impact
+	\begin{enumerate_2pt}
+		\item More timely data entry
+		\item Greater accuracy (especially by correct use of skip patterns)
+		\item More and more complex consistency checks
+
+	\end{enumerate_2pt}
+
+	\vspace{0.5em}
+
+	\item \textcolor{bdf}{Vast majority of large changes in sales and profits genuine income volatility}
+	\item Positive, but limited, effect of consistency checks in reducing variation in firm performance (and within-firm autocorrelation)
+
 	\end{itemize_2pt}
@@
 
-	\item Some more obvious constraints (already mentioned in passing):
-	\begin{itemize_2pt}
-		\item \textcolor{bdf}{Credit constraints} \citep[see, e.g.,][]{} McKenzie cash paper
+	\item Some more obvious constraints:
+	\begin{itemize_2pt}
+		\item \textcolor{bdf}{Credit constraints} (e.g., Berge et al., 2015, Gin\'e and Iacovone, 2021)
+		\item \textcolor{bdf}{Age-related} network and knowledge/skill \textcolor{bdf}{constraints}
 		\item \textcolor{bdf}{Gender norms and constraints}
-		\item \textcolor{bdf}{Age-related} network and knowledge/skill \textcolor{bdf}{constraints}
-	\end{itemize_2pt} 
 	\end{itemize_2pt}
@@
 
-$\rightarrow$ More recent literature highlights \textcolor{bdf}{behavioral constraints}
+	$\rightarrow$ More recent literature highlights additional \textcolor{bdf}{behavioral constraints}
+
+\end{itemize_2pt}
 
@@
 \begin{itemize_2pt}
-	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
+	\item Example: Heuristics-based business training program by \citet{Drexler2014}
+	\item[] $\rightarrow$ Discussed under \hyperlink{Drexler_thumb}{\beamergotobutton{alternative approaches}}
+	\item See also, \textcolor{camel}{Cole and Schoar (2019)} and \textcolor{camel}{Arra\'iz et al. (2019)}
+\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Family and neighborhood}
+
+Family commitments
+\begin{itemize_2pt}
+	\item \textcolor{bdf}{Unequal responsibilities for child care} (see, e.g., \textcolor{camel}{Delecourt and Fitzpatrick, 2021})
+	\begin{itemize_2pt}
+		\item Audit study with mystery shoppers among drug stores in Uganda
+		\item Average gender profit gap of 60\%
+		\item Close to all women have $\geq$ 1 child, breastfeed for median 19.8 months
+		\item[] $\rightarrow$ Among female entrepreneurs, those with child at work ..
+		\begin{itemize_2pt}
+			\item .. are \textcolor{bdf}{out of stock} more often, and stock up less.
+			\item .. have \textcolor{bdf}{48\% lower profits}.
+		\end{itemize_2pt}
+	\end{itemize_2pt}
+\end{itemize_2pt}
+
+\pause
+\vspace{1.0em}
+
+Market segregation
+\begin{itemize_2pt}
+	\item Markets can be geographically (and socially) segregated, especially in residential areas
+	\begin{itemize_2pt}
+		\item Potential \textcolor{bdf}{demand constraints} (in the spirit of \textcolor{camel}{Hardy and Kagy, 2020}, for women in Ghana)
+		\item (Scant work, but seems important.)
+	\end{itemize_2pt}
+\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Dynamic complementarities in skill acquisition}
+
+Complementarities in skills
+\begin{itemize_2pt}
+	\item Clusters of skills may be more valuable in combination
+	\begin{itemize_2pt}
+		\item Record keeping and financial planning complement each other
+	\end{itemize_2pt}
+	\item Skills may build on each other
+	\begin{itemize_2pt}
+		\item Profit calculation relies on record keeping
+		\item Advanced inventory management relies on record keeping (and profit calculation)
+	\end{itemize_2pt}
+\end{itemize_2pt}
+
+\vspace{1.0em}
+
+Learning styles
+\begin{itemize_2pt}
+	\item Psychological research finds interpersonal differences in \textcolor{bdf}{exploration-exploitation behavior} 
+	\begin{itemize_2pt}
+		\item Evidence for trait-like persistence of preference (see, e.g.,\textcolor{camel}{Waldner et al., 1998, Engler et al., 2010})
+		\item If technology has initial fixed costs, poverty \textit{per se} may affect trade-off
+	\end{itemize_2pt}
+
+\end{itemize_2pt}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Aspirations}
+
+Aspirations theory \citep[following][]{Dalton2016}
+\begin{itemize_2pt}
+	\item Aspirations are \textcolor{bdf}{desired level of outcome}
+
+	\item In theoretical work, aspirations are modeled as \textcolor{bdf}{reference-dependent preferences}
+	\begin{itemize_2pt}
+		\item Agent derives utility from relative level wrt their aspirations
+		\item[] $\rightarrow$ Aspirations motivate effort
+		\item Behavioral constraint: \textcolor{bdf}{Agent neglects outcomes $\rightarrow$ aspirations}
+	\end{itemize_2pt}
+
+	\vspace{0.5em}
+
+	\begin{figure}[htbp]
+		\centering
+		\includegraphics[width=12em]{pics/asp.png}
+		\label{Aspirations}
+	\end{figure}
+
+	\pause
+
+	\item Consequence: Sufficiently \textcolor{bdf}{poor agent} with sufficiently \textcolor{bdf}{low aspirations} chooses \textcolor{bdf}{suboptimally low effort}
+	\item[] $\rightarrow$ Potential for behavioral poverty trap
 	\vspace{0.1in}
-\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Dynamic complementarities in skill acquisition}
-
-Complementarities in skills
-\begin{itemize_2pt}
-	\item
+
+%\begin{figure}[htbp]
+%	\centering
+%	\includegraphics[width=15em]{pics/Ray2019_aspsMulti.png}
+%	\label{Ray(2019): Aspirations}
+%\end{figure}
+
+\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Aspirations}
+
+Evidence on aspirations in entrepreneurship
+\begin{itemize_2pt}
+	\item Descriptive evidence that micro entrepreneurs show \textcolor{bdf}{sizable growth aspirations} \citep{Dalton2018}
+	\begin{itemize_2pt}
+		\item Both short-term and long-term, for growth in size, labor, and sales
+		\item Entrepreneurs update dynamically given new information
+	\end{itemize_2pt}
+
+	\pause
+
+	\item \textcolor{camel}{Garlick et al. (in progress)} cross-randomize role-model intervention and large UCT to study complementarity
+	\begin{itemize_2pt}
+		\item \textcolor{bdf}{Exposure to role models increases aspirations, labor supply, expenditures, and sales}
+		\item Cash also increases aspirations, labor supply, expenditures, and sales
+	\end{itemize_2pt}
+
+	\pause
+
+	\item Aspiration interventions can backfire
+	\begin{itemize_2pt}
+		\item Goal setting intervention resulted in \textit{lower} investment \citep{McKenzieYang2021}
+		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 
+		\item[] \quad \citep[see also,][]{Galiani2018}
+	\end{itemize_2pt}
+
+\end{itemize_2pt}
+\end{frame}
+
+\subsection{Alternative Approaches}
+
+\begin{frame}[label=Drexler_thumb]
+\frametitle{Rules of Thumb}
+
+Core idea: Provide \textcolor{bdf}{simplified rules} to make training more cognitively accessible
+
+\begin{itemize_2pt}
+
+	\item Example: 
+	\begin{itemize_2pt}
+		\item Instead of detailed accounting practices, ..
+		\item[] .. focus on \textcolor{bdf}{physical separation of household and business finances} 
+		\item[] .. and only transfer money with an explicit \textcolor{bdf}{"IOU" note}
 	\end{itemize_2pt}
@@
 
-Learning styles
-\begin{itemize_2pt}
-	\item
-\end{itemize_2pt}
-
-\end{frame}
-
-\begin{frame}
-\frametitle{Family Commitments}
-\begin{itemize_2pt}
-	\item Interesting; \textcolor{red}{no beh const}
-	\vspace{0.1in}
-\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Segregated Markets}
-\begin{itemize_2pt}
-	\item Missing economies of scale
-	\item \textcolor{red}{Interesting; not behavioral constraint}
-	\vspace{0.1in}
-\end{itemize_2pt}
-\end{frame}
-
-%\begin{frame}
-%\frametitle{Identity Concerns}
-%\begin{itemize_2pt}
-%	\item 
-%	\vspace{0.1in}
-%\end{itemize_2pt}
-%\end{frame}
-
-\begin{frame}
-\frametitle{Aspirations}
-\begin{itemize_2pt}
-	\item 
-	\vspace{0.1in}
-\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Local Relevance of Business Practices}
-\begin{itemize_2pt}
-	\item 
-	\vspace{0.1in}
-\end{itemize_2pt}
-\end{frame}
-
-\subsection{Alternative Approaches}
+	\item Classical study: \textcolor{camel}{Drexler, Fischer, \& Schoar (2014)}
+	\begin{itemize_2pt}
+		\item Comparison of heuristics-based and standard accounting training with 1,193 micro-entrepreneurs in the Dominican  Republic
+		\item Null effect for full sample
+		\item[] $\rightarrow$ Statistical power limited due to substantial missing sales data
+		\item[] $\rightarrow$ \textcolor{bdf}{Larger gains with heuristics-based training for less educated entrepreneurs}
+
+	\end{itemize_2pt}
+\end{itemize_2pt}
+\end{frame}
 
@@
 	\begin{itemize_2pt}
-	\item Drexler, Fischer \& Schoar (2014) \citep{Drexler2014}
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Rules of Thumb}
-	\begin{itemize_2pt}
-	\item \citep{Arraiz2019} \citep{Cole2019}
-	\vspace{0.1in}
+		\item \textcolor{camel}{Arr\'aiz et al. (2019)} compare 4-hours heuristics-based finance training with standard finance and accounting program among 2,408 micro-entrepreneurs in Ecuador 
+		\begin{itemize_2pt}
+			\item Heuristics-based training increases daily business sales and profits by about 8\% each
+			\item Effects driven by \textcolor{bdf}{women} and entrepreneurs with \textcolor{bdf}{lower cognitive scores}
+		\end{itemize_2pt}
+
+		\vspace{1.0em}
+
+		\item Points of critique
+		\begin{itemize_2pt}
+			\item \textcolor{bdf}{Limited target group} of cognitively challenged
+			\item \textcolor{bdf}{Limited scope} (mostly confined to accounting practices)
+			\item So far \textcolor{bdf}{no long-term follow-up} (studies use 1-year endlines)
+			\item \textcolor{camel}{Cole and Schoar (2019)} find more mixed evidence for text-based rule-of-thumb assistance among micro-entrepreneurs in India and The Philippines
+		\end{itemize_2pt}
+
 	\end{itemize_2pt}
@@
 \frametitle{Entrepreneurial mindset}
-	\begin{itemize_2pt}
-	\item \citep{Campos2017}
-	\vspace{0.1in}
+
+Core idea: \textcolor{bdf}{Develop proactive mindset and increase growth aspirations}
+\begin{itemize_2pt}
+	\item Examples: 
+	\begin{itemize_2pt}
+		\item Encourage continued search for new opportunities
+		\item Encourage reflection on business differentiation
+		\item Learning by doing and from mistakes
+		\item Set daily goals
+	\end{itemize_2pt}
+
+	\vspace{1.0em}
+
+	\item \textcolor{camel}{Campos et al. (2017)} compare mindset training to standard business training among 1,500 micro-entrepreneurs in Togo
+	\begin{itemize_2pt}
+		\item 36 hours classroom instruction
+		\item 4 monthly 3-hours one-on-one follow-ups by trainer
+		\item USD 750 per person
+		\item[] $\rightarrow$ \textcolor{bdf}{Initiative training improves business profits by 30\% over 2.5 years}
+		\item[] \quad (Standard business training improves profits by 11\%)
+		\item[] $\rightarrow$ \textcolor{bdf}{Costs amortized within a year through firm profits}
+	\end{itemize_2pt}
+
 	\end{itemize_2pt}
@@
 \frametitle{Entrepreneurial mindset}
-	\begin{itemize_2pt}
-	\item \citep{Alibhai2019} \citep{Ubfal2019}
-	\vspace{0.1in}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=23em]{pics/McKenzie2020_mindset.png}
+	\label{McKenzie (2020): Mindset}
+\end{figure}
+
+\vspace{-1.0em}
+
+\begin{itemize_2pt}
+	\item \textcolor{bdf}{Average increases in business profits of 14\% and in sales of 10\%}
+	\item Programs show \textcolor{bdf}{substantial heterogeneity} wrt content and focus
+	\item[] $\rightarrow$ Heterogeneous, but generally positive, results
+\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Entrepreneurial mindset}
+
+Points of critique
+\begin{itemize_2pt}
+	\item \textcolor{bdf}{Probably limited target group}
+	\item Not clear whether standard curriculum and personal initiative training are \textcolor{bdf}{complements or substitutes}
+	\item \textcolor{camel}{Alibhai et al. (2019)} and \textcolor{camel}{Ubfal et al. (2019)} find \textcolor{bdf}{mixed results with lower treatment intensity}
+	\item No work yet on whether \textcolor{bdf}{classroom training and/or one-on-one follow-ups} necessary and/or sufficient conditions for success
 \end{itemize_2pt}
@@
 \begin{frame}
-\frametitle{Local Knowledge}
-	\begin{itemize_2pt}
-	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Local Knowledge}
-	\begin{itemize_2pt}
-	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Local Knowledge}
-	\begin{itemize_2pt}
-	\item Cai and Szeidl (2019), Brooks et al. (2018), Lafortune et al. (2020), Seither (2020), Abebe et al. (2020)?
-	\vspace{0.1in}
-	\end{itemize_2pt}
+\frametitle{Local Knowledge and Mentoring}
+
+Local entrepreneurs as mentors
+
+\begin{itemize_2pt}
+
+	\item Core ideas: 
+	\begin{itemize_2pt}
+		\item \textcolor{bdf}{Information may be highly localized}
+		\item \textcolor{bdf}{Peers may know better} about particular local constraints and practices
+		\item \textcolor{bdf}{Social learning} may work better between peers
+		\item Local mentors may be more \textcolor{bdf}{cost effective}
+	\end{itemize_2pt}
+
+	\item[] $\rightarrow$ Who mentors?
+	\item[] $\rightarrow$ Will mentors agree to share information?
+	\item[] $\rightarrow$ How to incentivize continued mentoring?
+
+\end{itemize_2pt}
+\end{frame}
+
+\begin{frame}
+\frametitle{Local Knowledge and Mentoring}
+
+\begin{itemize_2pt}
+	\item Successful business owners mentor smaller firms (\textcolor{camel}{Brooks et al., 2018})
+	\begin{itemize_2pt}
+		\item Random assignment of mentors or standard business training to 372 female micro-entrepreneurs in Kenya
+		\item Mentorship dyads
+		\begin{itemize_2pt}
+			\item Mentors local entrepreneurs from more profitable firms
+			\item \textcolor{bdf}{Encouragement of weekly meetings at mentor's firm for one month}
+			\item Many dyads continue meeting for more than one year
+		\end{itemize_2pt}
+
+		\item Mentored businesses show \textcolor{bdf}{increases in profits by 20\%}
+		\item $\rightarrow$ \textcolor{bdf}{Effect fades after one year} (when dyad dissolves)
+		\item No effect of standard business training.
+
+		\vspace{0.5em}
+
+		\item \textcolor{camel}{McKenzie and Puerto (2020)} find no impact of a 5-months mentoring scheme among female micro-entrepreneurs in Kenya
+	\end{itemize_2pt}
+\end{itemize_2pt}
+
+\end{frame}
+
+\begin{frame}
+\frametitle{Local Knowledge and Mentoring}
+
+Peer-to-peer learning
+
+\begin{itemize_2pt}
+	\item Core idea: \textcolor{bdf}{Firms may improve through mutual social learning}
+
+	\vspace{0.5em}
+
+	\item Firms matched among peers \textcolor{camel}{(Cai and Szeidl, 2018)}
+	\begin{itemize_2pt}
+		\item Random assignment of \textcolor{bdf}{peer group meetings} among 2,820 SMEs in China
+		\item Monthly meetings with 9 peers for 10 months
+		\item Peer groups of different sizes and sector compositions
+
+		\vspace{0.5em}
+
+		\item[] $\rightarrow$ \textcolor{bdf}{Sales increased by $8-10\%$} 
+		\item[] $\rightarrow$ Comparable increases in material inputs, employment, and assets
+
+	\end{itemize_2pt}
+
+\end{itemize_2pt}
+
 \end{frame}
@@
 
-\begin{frame}
-\frametitle{Role Models}
-	\begin{itemize_2pt}
-	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Role Models}
-	\begin{itemize_2pt}
-	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
-\begin{frame}
-\frametitle{Role Models}
-	\begin{itemize_2pt}
-	\item  La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013); Riley (2018)
-	\vspace{0.1in}
-	\end{itemize_2pt}
-\end{frame}
-
 \addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
@@
 	\begin{itemize_2pt}
-    \item
+    \item \textcolor{bdf}{Business practices differ substantially across firms} ..
+    \item[] \quad .. and vary with productivity
+    \item \textcolor{bdf}{Standard business training has limited ability} to change practices and firm performance in the short-term ..
+    \item[] \quad .. while long-term evidence is scarce
+    \item Some of that is due to \textcolor{bdf}{measurement error} (especially wrt firm profits) and \textcolor{bdf}{lack of statistical power} ..
+    \item[] \quad .. but \textcolor{bdf}{extensions of classical approach} also show promise:
+
+\vspace{0.5em}
+
+    \begin{itemize_2pt}
+    	\item Personal initiative training
+    	\item Business mentoring
+    	\item Peer-to-peer learning
+    \end{itemize_2pt}
    	\vspace{0.10in}
@@
 \begin{itemize_2pt}
-\item \textcolor{bdf}{Classroom Training}: Field, et al.
-(2010); Karlan \& Valdivia (2011); Bruhn \& Zia (2013); McKenzie \& Woodruff (2014, 2017); Bulte et al.
-(2017); Anderson, Chandy \& Zia (2018); Lafortune et al.
-(2018)
-\citep{Karlan2011}
+\item \textcolor{bdf}{Classroom Training}: \textcolor{camel}{Field, et al.
+(2010), Karlan \& Valdivia (2011), Bruhn \& Zia (2013), McKenzie \& Woodruff (2014, 2017), Bulte et al.
+(2017), Anderson, Chandy, \& Zia (2018), Lafortune et al.
+(2018)}
 \vspace{0.1in}
-\item \textcolor{bdf}{Consulting}: Bloom, et al. (2013); Karlan et al (2015); Bruhn, Karlan \& Schoar (2019)
+\item \textcolor{bdf}{Consulting}: \textcolor{camel}{Bloom, et al. (2013), Karlan et al (2015), Bruhn, Karlan, \& Schoar (2019)}
 \vspace{0.1in}
@@
     \begin{itemize_2pt}
-    \item Brooks et al. (2018) $\rightarrow$ Local mentors (market information)
-    \item Cai \& Szeidl (2018) $\rightarrow$ Business meetings
-    \item Abebe et al. (2019) $\rightarrow$ Management experience matching
+    \item \textcolor{camel}{Brooks et al. (2018)} $\rightarrow$ Local mentors (market information)
+    \item \textcolor{camel}{Cai \& Szeidl (2018)} $\rightarrow$ Business meetings
+    \item \textcolor{camel}{Abebe et al. (2019)} $\rightarrow$ Management experience matching
     \end{itemize_2pt}
@@
 	\item Vast heterogeneity in business practices and performance across similar businesses \citep{deMel2009}
-	\item Variation in practices accounts for more than 20\% of variation in productivity within the same firm in the US \citep{Bloom2019}
+	\item Variation in practices accounts for up to 30\% of variation in TFP across plants within the same firm in the US \citep{Bloom2019}
 	\item[] $\rightarrow$ Research has largely overlooked this heterogeneity in program design and implementation
@@
 \frametitle{Selecting Local Best Practices}
-\begin{itemize_2pt}
-\item Detailed \textcolor{bdf}{qualitative interviews} with local business peers:
+
+Detailed \textcolor{bdf}{qualitative interviews} with local business peers
     \begin{itemize_2pt}
@@
     \end{itemize_2pt}
+
 \vspace{0.1in}
-\item Baseline \textcolor{bdf}{quantitative survey}
+
+\textcolor{bdf}{Quantitative baseline survey}
     \begin{itemize_2pt}
@@
     \end{itemize_2pt}
-\end{itemize_2pt}
+
 \end{frame}
@@
 	\begin{itemize_2pt}
-		\item \textcolor{bdf}{Handbook}
-		\begin{itemize_2pt}
-			\item \textcolor{bdf}{Pure information}: Which practices, how to adopt, and why?\\
+		\item Handbook
+		\begin{itemize_2pt}
+			\item \textcolor{bdf}{Pure information} on profitable practices, implementation advice
 		\end{itemize_2pt}
@@
 
-	Two complementary behavioral interventions:
-	\begin{itemize_2pt}
-		\item \textcolor{bdf}{Movie}
-		\begin{itemize_2pt}
-			\item \textcolor{bdf}{Psychological and emotional involvement}$\rightarrow$ social learning is possible through \textcolor{bdf}{observing the successful experience of similar others}.
-			\item Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013).\\
-		\end{itemize_2pt}
-
-		\item \textcolor{bdf}{On-site Assistance}
-			\begin{itemize_2pt}
-				\item \textcolor{bdf}{Hands-on involvement} $\rightarrow$ social learning is possible through own \textcolor{bdf}{experience, 					with a small nudge} (Kolb, 1984).
+Two complementary behavioral interventions
+	\begin{itemize_2pt}
+		\item Movie of successful peers
+		\begin{itemize_2pt}
+			\item \textcolor{bdf}{Psychological and emotional involvement}
+			\item[] $\rightarrow$ Social learning through \textcolor{bdf}{observing experiences of similar others}
+			\item \textcolor{camel}{Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013)}
+		\end{itemize_2pt}
+
+		\item On-site assistance
+			\begin{itemize_2pt}
+				\item \textcolor{bdf}{Hands-on involvement}
+				\item[] $\rightarrow$ Social learning through own \textcolor{bdf}{idiosyncratic experience} \textcolor{camel}{(Kolb, 1984)}
 				\item Facilitated by local lay person
 			\end{itemize_2pt}
+		\item[] $\rightarrow$ Movie and assistance based exclusively on handbook!
 
@@
 	\begin{itemize_2pt}
-		\item Do retailers adopt these practices once peer best practices are aggregated and made common knowledge?
+		\item Do retailers adopt best practices once aggregated and made common knowledge?
 		\item If so, does the type of experiential involvement matter?
@@
 	\begin{itemize_2pt}
-		\item Does firm profitability increase?
+		\item Does adoption increase firm profits?
 		\item If so, what are the channels?
@@
 			\item \textcolor{bdf}{On-site assistance} with practice adoption
-			\item[] $\rightarrow$ Movie, assistance exclusively based on handbook
+			%\item[] $\rightarrow$ Movie, assistance exclusively based on handbook
 		\end{enumerate_2pt}
@@
 		\centering	
-		\tabcolsep=0.2cm
+		\tabcolsep=0.1cm
+		\fontsize{5.2}{5.2}\selectfont
 
 			\begin{tabular}{l*{10}{c}}
-			\hline\hline
+			\hline
+			& (1)  &&(2) && (3)  &&(4) && (5) \\
 			\hline
@@
 \\
-\\
 \textcolor{bdf}{Business Practices} \\
@@
 %\hspace{3mm} Discussion Subscore                        & 0.57	&& 0.59	  && 0.61	&& 0.6	&& 0.64  \\
-&		&&		&&		&& \\
-		\hline
 		\hline
@@
 %\end{tabular}
-%\begin{itemize_2pt}
-%\item Test of Joint Orthoganality from Multinomial Logit (P-value): 0.857
-%\end{itemize_2pt}
+
+\vspace{-0.5em}
+
+\begin{itemize_2pt}
+\item[] \tiny Test of joint orthogonality from multinomial logit (p-value): \quad 0.857
+\end{itemize_2pt}
 \end{frame}
@@
   \centering
- %   \tabcolsep=0.10cm
+ 	\fontsize{7}{7}\selectfont
+
+    \tabcolsep=0.10cm
     %\begin{adjustbox}{width=11cm}
@@
   \centering
-    %\tabcolsep=0.10cm
+  \fontsize{7}{7}\selectfont
+    \tabcolsep=0.10cm
    % \begin{adjustbox}{width=11cm}
@@
 %\begin{adjustbox}{width=10cm}
-%	\tabcolsep=0.05cm
+\fontsize{5.5}{5.5}\selectfont
+	\tabcolsep=0.10cm
 	\begin{tabular}{l*{10}{c}}
-		\hline \hline
+		\hline
 		\\
 			&\textcolor{bdf}{Record}			&&\textcolor{bdf}{Planning}			&&\textcolor{bdf}{Stocking-up}	&&\textcolor{bdf}{Marketing} && \textcolor{bdf}{Joint} \\
-&\textcolor{bdf}{Keeping}                       &&                        &&	                   &&	 && Decision-making \\
+&\textcolor{bdf}{Keeping}                       &&                        &&	                   &&	 && \textcolor{bdf}{Decision-making} \\
 					&(1)					&&(2)						&&(3) 						&&(4) && (5)\\
@@
 \end{table}}}
-\begin{itemize_2pt}
-\item Multiple hypothesis testing corrected p-values in parentheses
-\item "All Three" improvement of 28 \% in record-keeping, 17 \% in planning, 11 \% in stocking, 24 \% in marketing and 22 \% in joint decision making.
-\end{itemize_2pt}
+\begin{itemize}
+\item[] \tiny Multiple hypothesis testing corrected p-values in parentheses
+\end{itemize}
+
+\begin{itemize}
+\item \small ``All Three" improvement of 28 \% in record-keeping, 17 \% in planning, 11 \% in stocking, 24 \% in marketing and 22 \% in joint decision making.
+\end{itemize}
+
 \end{frame}
@@
 %\begin{adjustbox}{width=9cm}
-%	\tabcolsep=0.05cm
+\fontsize{5.7}{5.7}\selectfont
+	\tabcolsep=0.10cm
 	\begin{tabular}{l*{5}{c}}
 \hline
-\hline
-			   &&Profits	        &&Profits \\
-				&&last month  		&&last month \\
+&& (1) && (2) \\
+\hline
+			   &&\textcolor{bdf}{Profits}	        &&\textcolor{bdf}{Profits} \\
+				&&\textcolor{bdf}{last month}  		&&\textcolor{bdf}{last month} \\
 			&&(win 5\%)			&&(IHS) \\
@@
 \end{table}}}
-\begin{itemize_2pt}
-\item Profits increase by 35\% (about 0.28 sd.) - ITT.
+
+\vspace{-0.5em}
+
+\begin{itemize_2pt}
+\item Intention to treat (ITT): Profits increase by 35\% (about 0.28 sd.)
 \end{itemize_2pt}
@@
 %\begin{adjustbox}{width=9cm}
-%	\tabcolsep=0.05cm
+\fontsize{5.7}{5.7}\selectfont
+	\tabcolsep=0.10cm
 	\begin{tabular}{l*{5}{c}}
 \hline
-\hline
-                &&ITT	        &&TOT \\
-			   &&Sales	        &&Sales \\
-				&&last month  		&&last month \\
-			&&(win 5\%)			&&(win 5\% \\
+&& (1) && (2) \\
+\hline
+                &&\textcolor{bdf}{ITT}	        &&\textcolor{bdf}{TOT} \\
+			   &&\textcolor{bdf}{Sales}	        &&\textcolor{bdf}{Sales} \\
+				&&\textcolor{bdf}{last month}  		&&\textcolor{bdf}{last month} \\
+			&&(win 5\%)			&&(win 5\%) \\
 				&&(1)				&&(2)	\\
@@
 Assigned Handbook 					&&-396.976   	&&               -417.198		\\
-       								 	&&        (314.252)   	&&          -417.198	\\
+       								 	&&        (314.252)   	&&          (-397.174)	\\
 
@@
 \end{table}}}
-\begin{itemize_2pt}
-\item Sales increase by 16\% (about 0.15 sd.) - ITT %- and 31\% (0.28 sd.) - TOT.
+
+\vspace{-0.5em}
+
+\begin{itemize_2pt}
+\item Intention to treat (ITT): Sales increase by 16\% (about 0.15 sd.)
 \end{itemize_2pt}
@@
 \frametitle{Other Outcomes}
-\begin{itemize_2pt}
-\item \textcolor{bdf}{No significant} impacts on:
+
+\textcolor{bdf}{No significant} impacts on:
     \begin{itemize_2pt}
@@
     \vspace{0.1in} 		
-    \item Size of the shop
+    \item Business size
       \vspace{0.1in}
@@
 	\item[] $\rightarrow$ \textcolor{bdf}{Non-record-keeping practices}
-	\item[] $\rightarrow$ \textcolor{bdf}{Stocking up and marketing practices} appear to drive performance effects (causal-mediation analysis)
+	\item[] $\rightarrow$ Causal mediation analysis: \textcolor{bdf}{Stocking up and marketing practices} drive performance impact
 	\item[] $\rightarrow$ Variance in profits among treated firms does not converge
@@
 	\item .. acquisition of \textcolor{bdf}{business knowledge} and/or
-	\item .. strengthening of \textcolor{bdf}{business aspirations}
+	\item .. strengthening of \textcolor{bdf}{growth aspirations}
 \end{itemize_2pt}
@@
 
+\begin{frame}
+\frametitle{Questions}
+
+\textcolor{bdf}{Any questions?}
+\begin{itemize_2pt}
+    \item[] .. happy to stay on for a little while!
+\end{itemize_2pt}
+\end{frame}
+
 %\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}

### 2021-03-08 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added citations

@@
 \begin{itemize_2pt}
-	\item Heterogeneity in mgmt practices across mid-sized and large firms \textcolor{camel}{(Bloom et al., 2007, Bloom et al., 2010, Syverson, 2011)}
+	\item Heterogeneity in mgmt practices across mid-sized and large firms \textcolor{camel}{\citep{Bloom2007, Bloom2010, Syverson2011}}
 \end{itemize_2pt}
@@
 			\item As technology affecting productivity factor $\textcolor{red}{A}$
-			\item[] See, e.g., \textcolor{camel}{Bloom et al., (2016), McKenzie and Woodruff (2017)} %Quinn2019}
+			\item[] \citep[See, e.g.,][]{Bloom2016, McKenzie2017}
 		\end{enumerate_2pt}
@@
 		\item Better \textcolor{bdf}{negotiation practices} may affect raw material prices $\textcolor{red}{s}$
-		\item \textcolor{bdf}{Record-keeping} and \textcolor{bdf}{financial planning practices} may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend (see, e.g., \textcolor{camel}{Bruhn and Zia, 2013})
+		\item \textcolor{bdf}{Record-keeping} and \textcolor{bdf}{financial planning practices} may affect borrowing constraints $\textcolor{red}{\lambda}$ through banks' willingness to lend \citep[see, e.g.][]{Bruhn2013}
 		\item \textcolor{bdf}{Marketing practices} may affect output price $\textcolor{red}{p}$ by changing demand
@@
 
-	\item Average training program not inexpensive (USD 177 per person for ILO training, \citet{Lieshout2017})
+	\item Average training program not inexpensive (USD 177 per person for ILO training, \citet{vanLieshout2017})
 	\item[] $\rightarrow$ Typical training program \textcolor{bdf}{highly subsidized}
@@
 		\item Null-effect on business sales and profits
-		\item Early examples: \textcolor{camel}{Karlan and Valdivia, 2011, Bruhn and Zia, 2013; Giné and Mansuri, 2014; Field, et al., 2010} 
-		%\item Later examples: \textcolor{camel}{Bulte et al., 2017; Anderson, Chandy, and Zia, 2018}
+		\item Early examples: \citet{Field2010, Karlan2011, Bruhn2013}, also \citet[][WP in 2014]{Gine2021}
 
@@
 		\begin{itemize_2pt}
-			\item Gender and Enterprise Together (GET Ahead, ILO; \textcolor{camel}{Bulte et al., 2017}, \textcolor{camel}{McKenzie and Puerto, 2021})
-			\item Start and Improve Your Business (SIYB, IFC; \textcolor{camel}{de Mel et al., 2014})
+			\item Gender and Enterprise Together \citep[GET Ahead, ILO;][]{Bulte2017, McKenziePuerto2021}
+			\item Start and Improve Your Business \citep[SIYB, IFC;][]{deMel2014}
 		\end{itemize_2pt}
@@
 			\item Women overrepresented in subsistence entrepreneurship
-			\item Female entrepreneurs often subject to more severe constraints (e.g., due to household-level reallocation; see, e.g., \textcolor{camel}{Bernhardt et al.
-2019}, \textcolor{camel}{de Mel et al., 2009})
+			\item Female entrepreneurs often subject to more severe constraints; e.g., due to household-level reallocation \citep[see, e.g.,][]{Bernhardt2019, deMel2009a}
 		\end{itemize_2pt}
@@
 		\item Typically embedded as \textcolor{bdf}{entrepreneurship courses in school or university} (business concepts and soft skills)
-		\item Example: Final year university course in Tunisia \textcolor{camel}{(Alaref et al., 2020)}
+		\item Example: Final year university course in Tunisia \citep{Alaref2020}
 		\begin{itemize_2pt}
@@
 \begin{itemize_2pt}
-	\item Extensive-margin prediction of future MSE growth is hard \textcolor{camel}{(Fafchamps and Woodruff, 2017)} 
+	\item Extensive-margin prediction of future MSE growth is hard \citep{Fafchamps2017}
 	\begin{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		\item See, e.g., \textcolor{camel}{Cusolito et al., 2020}, \textcolor{camel}{Gonzalez-Uribe et al., 2017}, \textcolor{camel}{Gonzalez-Uribe et al. 2020}
+		\item \citet{Cusolito2021, GonzalezUribe2018, GonzalezUribe2021}
 	\end{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		\item Goal setting intervention resulted in \textit{lower} investment \citep{McKenzieYang2021}
+		\item Goal setting intervention resulted in \textit{lower} investment \citep{McKenzie2021a}
 		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 

### 2021-03-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added citations

@@
     citecolor= camel, % citations
-    urlcolor= black % external links/urls
+    urlcolor= camel % external links/urls
 }
@@
 	\begin{itemize_2pt}
-		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018} %Karlan2015, Bruhn2019
+		\item Total of 88 to 200 hours and more \citep{Anderson2020, Bruhn2018} %[citation]Karlan2015, Bruhn2019
 		\item[] $\rightarrow$ Typically several months
@@
 \begin{itemize_2pt}
-	\item Examples: \textcolor{bdf}{Reality show competitions} in Tanzania \textcolor{camel}{(Bjorvatn et al., 2020)} and Egypt \textcolor{camel}{(Barsoum et al., 2018)}
+	\item Examples: \textcolor{bdf}{Reality show competitions} in Tanzania \citep{Bjorvatn2020} and Egypt \citep{Barsoum2018}
 	\item Differential random incentivization schemes
@@
 	\begin{itemize_2pt}
-		\item Heuristics-based business advice \textcolor{camel}{(Cole and Schoar, 2019)}
-		\item Daily personalised inventory level recommendations \textcolor{camel}{(Acimovic et al., 2020)}
+		\item Heuristics-based business advice \citep{Cole2018}
+		\item Daily personalized inventory level recommendations \citep{Acimovic2020}
 	\end{itemize_2pt}
@@
 
-Alternative measures of business profits \textcolor{camel}{(de Mel et al., 2009)}
+Alternative measures of business profits \citep{deMel2009}
 	\begin{itemize_2pt}
@@
 
-Survey media and frequencies {(Garlick et al, 2019)}
+Survey media and frequencies \citep{Garlick2019}
 \begin{itemize_2pt}
 	\item 12-week panel with detailed measurements of employees, profits, sales, assets, transfers, etc.
-
 	\item Random assignment to different survey modes and frequencies
@@
 \frametitle{Variation in Outcome Measures}
-Technological aids \textcolor{camel}{(Fafchamps et al., 2012)}
+Technological aids \citep{Fafchamps2012}
 	\begin{itemize_2pt}
 	\item Random assignment to Personalized Digital Assistants (PDAs)
-	\
 	\item Potential channels of impact
@@
 	\begin{itemize_2pt}
-		\item \textcolor{bdf}{Credit constraints} (e.g., Berge et al., 2015, Gin\'e and Iacovone, 2021)
-		\item \textcolor{bdf}{Age-related} network and knowledge/skill \textcolor{bdf}{constraints}
+		\item \textcolor{bdf}{Credit constraints} \citep[e.g.,][]{Berge2015, Gine2021}%[citation] mcenzie
+		\item \textcolor{bdf}{Education} and \textcolor{bdf}{literacy constraints}
 		\item \textcolor{bdf}{Gender norms and constraints}
+		%\item \textcolor{bdf}{Age-related} network and knowledge/skill \textcolor{bdf}{constraints}
 	\end{itemize_2pt}
@@
 	\item[] $\rightarrow$ Discussed under \hyperlink{Drexler_thumb}{\beamergotobutton{alternative approaches}}
-	\item See also, \textcolor{camel}{Cole and Schoar (2019)} and \textcolor{camel}{Arra\'iz et al. (2019)}
+	\item See also, \citet{Cole2018} and \citet{Arraiz2019}
 \end{itemize_2pt}
@@
 \begin{itemize_2pt}
-	\item \textcolor{bdf}{Unequal responsibilities for child care} (see, e.g., \textcolor{camel}{Delecourt and Fitzpatrick, 2021})
+	\item \textcolor{bdf}{Unequal responsibilities for child care} \citep[see, e.g.,][]{Delecourt2021}
 	\begin{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		\item Potential \textcolor{bdf}{demand constraints} (in the spirit of \textcolor{camel}{Hardy and Kagy, 2020}, for women in Ghana)
+		\item Potential \textcolor{bdf}{demand constraints} \citep[in the spirit of][, for women in Ghana]{Hardy2020}
 		\item (Scant work, but seems important.)
@@
 	\begin{itemize_2pt}
-		\item Evidence for trait-like persistence of preference (see, e.g.,\textcolor{camel}{Waldner et al., 1998, Engler et al., 2010})
+		\item Evidence for trait-like persistence of preference (see, e.g.,\textcolor{camel}{Waldner et al., 1998, Engler et al., 2010})%[citation]
 		\item If technology has initial fixed costs, poverty \textit{per se} may affect trade-off
@@
 \begin{itemize_2pt}
-	\item Descriptive evidence that micro entrepreneurs show \textcolor{bdf}{sizable growth aspirations} \citep{Dalton2018}
+	\item Descriptive evidence that \textcolor{bdf}{micro-entrepreneurs show sizable growth aspirations} \citep{Dalton2018}
 	\begin{itemize_2pt}
@@
 
-	\item \textcolor{camel}{Garlick et al. (in progress)} cross-randomize role-model intervention and large UCT to study complementarity
+	\item \href{https://www.poverty-action.org/study/impact-cash-transfers-aspirations-and-goal-setting-economic-outcomes-and-well-being}{Garlick et al.
+(in progress)} cross-randomize role-model intervention and large UCT to study complementarity
 	\begin{itemize_2pt}
@@
 		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 
-		\item[] \quad \citep[see also,][]{Galiani2018}
+		\item[] \quad \citet[See also,][]{Galiani2018}
 	\end{itemize_2pt}

### 2021-03-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added citations to pres

@@
 		\item[] $\rightarrow$ Potential of aspiration frustration if external constraints bind 
-		\item[] \quad \citet[See also,][]{Galiani2018}
+		\item[] \quad \citep[see also,][]{Galiani2018}
 	\end{itemize_2pt}
@@
 
-	\item Classical study: \textcolor{camel}{Drexler, Fischer, \& Schoar (2014)}
+	\item Classical study: \citet{Drexler2014}
 	\begin{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		\item \textcolor{camel}{Arr\'aiz et al. (2019)} compare 4-hours heuristics-based finance training with standard finance and accounting program among 2,408 micro-entrepreneurs in Ecuador 
+		\item \citet{Arraiz2019} compare 4-hours heuristics-based finance training with standard finance and accounting program among 2,408 micro-entrepreneurs in Ecuador 
 		\begin{itemize_2pt}
@@
 			\item So far \textcolor{bdf}{no long-term follow-up} (studies use 1-year endlines)
-			\item \textcolor{camel}{Cole and Schoar (2019)} find more mixed evidence for text-based rule-of-thumb assistance among micro-entrepreneurs in India and The Philippines
+			\item \citet{Cole2018} find more mixed evidence for text-based rule-of-thumb assistance among micro-entrepreneurs in India and The Philippines
 		\end{itemize_2pt}
@@
 
-	\item \textcolor{camel}{Campos et al. (2017)} compare mindset training to standard business training among 1,500 micro-entrepreneurs in Togo
+	\item \citet{Campos2017} compare mindset training to standard business training among 1,500 micro-entrepreneurs in Togo
 	\begin{itemize_2pt}
@@
 	\item Not clear whether standard curriculum and personal initiative training are \textcolor{bdf}{complements or substitutes}
-	\item \textcolor{camel}{Alibhai et al. (2019)} and \textcolor{camel}{Ubfal et al. (2019)} find \textcolor{bdf}{mixed results with lower treatment intensity}
+	\item \citet{Alibhai2019} and \citet{Ubfal2020} find \textcolor{bdf}{mixed results with lower treatment intensity}
 	\item No work yet on whether \textcolor{bdf}{classroom training and/or one-on-one follow-ups} necessary and/or sufficient conditions for success
@@
 \begin{itemize_2pt}
-	\item Successful business owners mentor smaller firms (\textcolor{camel}{Brooks et al., 2018})
+	\item Successful business owners mentor smaller firms \citep{Brooks2018}
 	\begin{itemize_2pt}
@@
 
-		\item \textcolor{camel}{McKenzie and Puerto (2020)} find no impact of a 5-months mentoring scheme among female micro-entrepreneurs in Kenya
+		\item \citet{McKenziePuerto2021} find no impact of a 5-months mentoring scheme among female micro-entrepreneurs in Kenya
 	\end{itemize_2pt}
@@
 
-	\item Firms matched among peers \textcolor{camel}{(Cai and Szeidl, 2018)}
+	\item Firms matched among peers \citep{Cai2018}
 	\begin{itemize_2pt}

### 2021-03-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added last citations to pres

@@
 \begin{itemize_2pt}
-	\item Heterogeneity in mgmt practices across mid-sized and large firms \textcolor{camel}{\citep{Bloom2007, Bloom2010, Syverson2011}}
+	\item Heterogeneity in mgmt practices across mid-sized and large firms \citep{Bloom2007, Bloom2010, Syverson2011}
 \end{itemize_2pt}
@@
 \begin{itemize_2pt}
-\item \textcolor{bdf}{Classroom Training}: \textcolor{camel}{Field, et al.
-(2010), Karlan \& Valdivia (2011), Bruhn \& Zia (2013), McKenzie \& Woodruff (2014, 2017), Bulte et al.
-(2017), Anderson, Chandy, \& Zia (2018), Lafortune et al.
-(2018)}
+\item \textcolor{bdf}{Classroom Training}: \citet{McKenzie2014, Karlan2011, Bruhn2013, Anderson2018, Bulte2017, Field2010}
 \vspace{0.1in}
-\item \textcolor{bdf}{Consulting}: \textcolor{camel}{Bloom, et al. (2013), Karlan et al (2015), Bruhn, Karlan, \& Schoar (2019)}
+\item \textcolor{bdf}{Consulting}:\citet{Bruhn2018, Anderson2020, Karlan2015}
 \vspace{0.1in}
@@
     \begin{itemize_2pt}
-    \item \textcolor{camel}{Brooks et al. (2018)} $\rightarrow$ Local mentors (market information)
-    \item \textcolor{camel}{Cai \& Szeidl (2018)} $\rightarrow$ Business meetings
-    \item \textcolor{camel}{Abebe et al. (2019)} $\rightarrow$ Management experience matching
+    \item \citet{Brooks2018} $\rightarrow$ Local mentors (market information)
+    \item \citet{Cai2018} $\rightarrow$ Business meetings
+    \item \citet{Abebe2019} $\rightarrow$ Management experience matching
     \end{itemize_2pt}
@@
 \begin{itemize_2pt}
-	\item Vast heterogeneity in business practices and performance across similar businesses \citep{deMel2009}
+	\item Vast heterogeneity in business practices and performance across similar businesses \citep{McKenzie2017, deMel2009}
 	\item Variation in practices accounts for up to 30\% of variation in TFP across plants within the same firm in the US \citep{Bloom2019}
@@
 			\item[] $\rightarrow$ Social learning through \textcolor{bdf}{observing experiences of similar others}
-			\item \textcolor{camel}{Bernard, et al. (2014); La Ferrara et al. (2012); Chong and La Ferrara (2009); Berg and Zia (2013)}
+			\item[] \quad \citep[see,e.g.,][]{Bernard2014, Ferrara2012, Chong2009, Berg2017}
 		\end{itemize_2pt}
@@
 				\item \textcolor{bdf}{Hands-on involvement}
-				\item[] $\rightarrow$ Social learning through own \textcolor{bdf}{idiosyncratic experience} \textcolor{camel}{(Kolb, 1984)}
+				\item[] $\rightarrow$ Social learning through own \textcolor{bdf}{idiosyncratic experience}
 				\item Facilitated by local lay person
@@
 
-\begin{frame}
-\frametitle{Handbook Content}
-
-\begin{figure}[htbp]
-	\centering
-		\includegraphics[width=2.6in]{pics/Handbook_stepbystep.jpg}
-
-	\label{height}
-\end{figure}
-\end{frame}
+%\begin{frame}
+%\frametitle{Handbook Content}
+
+%\begin{figure}[htbp]
+%	\centering
+%		\includegraphics[width=2.6in]{pics/Handbook_stepbystep.jpg}
+
+%	\label{height}
+%\end{figure}
+%\end{frame}
 
@@
 
-\textcolor{bdf}{No significant} impacts on:
+\textcolor{bdf}{No significant impacts} on:
     \begin{itemize_2pt}
@@
 \appendix
-\begin{frame}[label=references, allowframebreaks]
+\begin{frame}[allowframebreaks] %label=references, 
 \frametitle{References}
@@
 
-\section*{\textbf{APPENDIX}}
+\section*{\textbf{Appendix}}
 

### 2021-03-10 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Small tweaks

@@
 	\begin{itemize_2pt}
-		\item At least \textcolor{bdf}{USD 1 billion per year} (to 4-5 million entrepreneurs; \citet{McKenzie2021})
+		\item At least \textcolor{bdf}{USD 1 billion per year} \citep[for $\sim$ 4-5 million entrepreneurs;][]{McKenzie2021}
 		\item Classical training programs \emph{precede} evidence that business practices vary and are predictive for productivity
@@
 	\item Group of 15 to 40 entrepreneurs per trainer
-	\item In-class (often with elements of active and interactive learning)
+	\item \textcolor{bdf}{In-class} (may incl elements of active and interactive learning)
 	\item Period of up to two weeks	
@@
 
-	\item Average training program not inexpensive (USD 177 per person for ILO training, \citet{vanLieshout2017})
+	\item Average training program not inexpensive \citep[USD 177 per person for ILO training;][]{vanLieshout2017}
 	\item[] $\rightarrow$ Typical training program \textcolor{bdf}{highly subsidized}
@@
 \begin{itemize_2pt}
-	\item Demand curve for business training in Jamaica: $\sim$60-70\% willing to pay half, $\sim$10\% full price \citep{Maffioli2020}
+	\item Demand curve for business training in Jamaica: \textcolor{bdf}{$\sim$10\% willing to pay full price}, $\sim$60-70\% half  \citep{Maffioli2020}
 \end{itemize_2pt}
@@
 		\item Null-effect on business sales and profits
-		\item Early examples: \citet{Field2010, Karlan2011, Bruhn2013}, also \citet[][WP in 2014]{Gine2021}
+		\item Early examples: \citet{Field2010, Karlan2011, Bruhn2013}; also \citet[][WP in 2014]{Gine2021}
 
@@
 			\item Typical attendance between 40 and 70\%
-			\item Typically substantial rates of survey attrition (up to $24-28\%$)
+			\item Often substantial rates of survey attrition (up to $24-28\%$)
 			\item Large heterogeneity in age, education, training delivery and costs, etc.
@@
 
-		\item Endline follow-ups \textcolor{bdf}{very short-term} (typically 1-2 years out)
+		\item \textcolor{bdf}{Endline follow-ups typically short-term} (typically 1-2 years out)
 
@@
 		\begin{itemize_2pt}
-			\item Potential for reverse sunken cost fallacy in valuation \citep[see,][]{Maffioli2020}
+			\item Potentially lower valuation, utilization \citep[see,][]{Maffioli2020}
 		\end{itemize_2pt}
@@
 		\begin{itemize_2pt}
-			\item Women overrepresented in subsistence entrepreneurship
-			\item Female entrepreneurs often subject to more severe constraints; e.g., due to household-level reallocation \citep[see, e.g.,][]{Bernhardt2019, deMel2009a}
+			\item Women overrepresented in mere subsistence entrepreneurship
+			\item Female entrepreneurs often subject to more severe constraints
+			\item[] \citep[e.g., due to household-level reallocation; see][]{Bernhardt2019, deMel2009a}
 		\end{itemize_2pt}
@@
 		\begin{itemize_2pt}
-			\item Positive impact on business entry tapers off after 4 years
+			\item Initial positive impact on business entry
+			\item[] $\rightarrow$ \textcolor{bdf}{Effects taper off after 4 years} (no evidence for lasting effects)
 		\end{itemize_2pt}
@@
 
-\vspace{1.0em}
+\vspace{0.5em}
 
@@
 		\item Survey, ability measure, expert panel all explain unique variation
-		\item But: Business training for predicted gazelles shows no impact
-	\end{itemize_2pt}
-
-	\item \citet{McKenzie2017a} finds more encouraging results with a nationwide business plan competition in Nigeria
+		\item But: \textcolor{bdf}{Business training for predicted gazelles shows no impact}
+	\end{itemize_2pt}
+
+	\item \citet{McKenzie2017a} finds \textcolor{bdf}{more encouraging results with a large-scale, high-stakes business plan competition} in Nigeria
 
@@
 	\begin{itemize_2pt}
-		\item \citet{Cusolito2021, GonzalezUribe2018, GonzalezUribe2021}
+		\item See, e.g., \citet{Cusolito2021, GonzalezUribe2018, GonzalezUribe2021}
 	\end{itemize_2pt}
@@
 \begin{itemize_2pt}	
-	\item \citet{Anderson2018} assign 852 South African micro-entrepreneurs to two distinct trainings:
+	\item \citet{Anderson2018} vary \textcolor{bdf}{training focus} among 852 South African micro-entrepreneurs
 
@@
 		\begin{itemize_2pt}
-			\item "Growth focus" on higher sales, stock investments, and hiring
+			\item \textcolor{bdf}{"Growth focus" on higher sales, stock investments, and hiring}
 			\item 61\% increase in profits
@@
 		\begin{itemize_2pt}
-			\item "Efficiency focus" on lower costs
+			\item \textcolor{bdf}{"Efficiency focus" on lower costs}
 			\item 41\% increase in profits
@@
 
-	\item Typically one-on-one (also group-based)
+	\item Typically one-on-one \citep[also group-based; see,][]{McKenzie2021b}
 
@@
 		\item[] $\rightarrow$ Meetings monthly to twice weekly, 2-4 hours
-		\item Total cost between \textcolor{red}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
+		\item Total cost between \textcolor{bdf}{USD 4,000 and 12,000 per firm} \citep{Anderson2020, Bruhn2018}
 	\end{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		%\item Empirical finding: Firms often unwilling to pay market price \citep{Maffioli2020}
 		\item[] $\rightarrow$ \textcolor{bdf}{Matching-grant programs}
@@
 
-Example: Subsidized matching grant program for MSMEs in Mexico \citep{Bruhn2018}
+Example: Matching grant program for MSMEs in Mexico \citep{Bruhn2018}
 \begin{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		\item Availability issues of admin data may have introduced selection
+		\item Limited availability of admin data may introduce \textcolor{bdf}{selection bias}
 		\item Not clear if effects concentrated among few businesses
@@
 	\item Differential random incentivization schemes
-	\item[] $\rightarrow$ No impact on business knowledge and business entry 
+	\item[] $\rightarrow$ \textcolor{bdf}{No impact} on business knowledge and business entry 
 	\item[] $\rightarrow$ But: \textcolor{bdf}{High viewership} (conventional MDEs substantially above policy-relevant levels)
@@
 		\item Heuristics-based business advice \citep{Cole2018}
-		\item Daily personalized inventory level recommendations \citep{Acimovic2020}
-	\end{itemize_2pt}
-	\item[] $\rightarrow$ Small literature with generally \textcolor{camel}{mixed results or null effects}
-	\item[] $\rightarrow$ But: \textcolor{bdf}{MDEs substantially above policy-relevant levels}
-	\item[] $\rightarrow$ But: \textcolor{bdf}{Complementarities} between in-person training and SMS reminders still unclear
+		\item Personalized inventory recommendations \citep{Acimovic2020}
+	\end{itemize_2pt}
+	\item[] $\rightarrow$ Small literature with generally \textcolor{bdf}{mixed results or null effects}
+	\item[] $\rightarrow$ But: \textcolor{bdf}{Extremely cheap} (MDEs above policy-relevant levels)
+	\item[] $\rightarrow$ But: \textcolor{bdf}{Potential complementarities} with in-person training
 \end{itemize_2pt}
@@
 		\item 15-16 unannounced visits during one month
-		\item Random assignment of profit measure, and accounting diaries, and recall span
+		\item Random assignment of profit measure, accounting diaries, and recall span
 	\end{itemize_2pt}
@@
 		\item \textcolor{bdf}{Accounting diaries have no effect on profits} (but on sales)
-		\item With recall over 4 months vs. 1 month, entrepreneurs \textcolor{bdf}{understate revenues by $10 - 15 \%$ due to memory} 
+		\item With recall over 4 months vs. 1 month, entrepreneurs \textcolor{bdf}{understate revenues by $10 - 15 \%$ due to memory loss} 
 		\item Entrepreneurs estimate average rival business to \textcolor{bdf}{underreport sales by 30\%}
@@
 \begin{itemize_2pt}
-	\item 12-week panel with detailed measurements of employees, profits, sales, assets, transfers, etc.
+	\item 12-week panel with detailed measurements of employees, assets, profits, sales, transfers, etc.
 	\item Random assignment to different survey modes and frequencies
@@
 	\begin{itemize_2pt}
-		\item \textcolor{bdf}{All survey modes generally yield similar statistical moments}
-		\item Phone surveys yield higher within-firm, cross-temporal variation
-		\item[] (Some evidence for greater social desirability bias.)
+		\item \textcolor{bdf}{All survey modes generally result in similar statistical moments}
+		\item Phone surveys yield higher within-firm variation
+		\item[] (And may be more vulnerable to social desirability bias.)
 	\end{itemize_2pt}
@@
 
-	\item \textcolor{bdf}{Vast majority of large changes in sales and profits genuine income volatility}
-	\item Positive, but limited, effect of consistency checks in reducing variation in firm performance (and within-firm autocorrelation)
+	\item Key result: \textcolor{bdf}{Vast majority of large changes in sales and profits genuine income volatility}
+	\begin{itemize_2pt}
+		\item Positive, but limited, effect of consistency checks in reducing variation in firm performance
+	\end{itemize_2pt}
 
@@
 \begin{itemize_2pt}
-	\item Typical small-firm owner dropped out of highschool
+	\item Typical micro-entrepreneur is a high-school dropout
 	\item Test scores on digitspan and Raven's matrices about \% of Western university samples \textcolor{red}{\citep[comp.][]{}}
@@
 \begin{itemize_2pt}
-	\item \textcolor{bdf}{Unequal responsibilities for child care} \citep[see, e.g.,][]{Delecourt2021}
+	\item \textcolor{bdf}{Unequal responsibilities for child care} \citep{Delecourt2021}
 	\begin{itemize_2pt}
@@
 	\begin{itemize_2pt}
-		\item Potential \textcolor{bdf}{demand constraints} \citep[in the spirit of][, for women in Ghana]{Hardy2020}
+		\item Potential \textcolor{bdf}{demand constraints} \citep[in the spirit of][studying women in Ghana]{Hardy2020}
 		\item (Scant work, but seems important.)
@@
 	\begin{itemize_2pt}
-		\item Agent derives utility from relative level wrt their aspirations
+		\item Agent derives utility from relative level wrt aspirations
 		\item[] $\rightarrow$ Aspirations motivate effort
@@
 
-	\item Consequence: Sufficiently \textcolor{bdf}{poor agent} with sufficiently \textcolor{bdf}{low aspirations} chooses \textcolor{bdf}{suboptimally low effort}
-	\item[] $\rightarrow$ Potential for behavioral poverty trap
+	\item Consequence: Sufficiently \textcolor{bdf}{poor agents} with sufficiently \textcolor{bdf}{low aspirations} choose suboptimally low effort
+	\item[] $\rightarrow$ Potential for \textcolor{bdf}{behavioral poverty trap}
 	\vspace{0.1in}
@@
 		\item \textcolor{bdf}{Exposure to role models increases aspirations, labor supply, expenditures, and sales}
-		\item Cash also increases aspirations, labor supply, expenditures, and sales
+		\item[] (Cash also increases aspirations, labor supply, expenditures, and sales.)
 	\end{itemize_2pt}
@@
 
-	\item Aspiration interventions can backfire
+	\item \textcolor{bdf}{Aspiration interventions can backfire}
 	\begin{itemize_2pt}

### 2021-03-15 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Added lit for explo-exploit

@@
 
-	\item Typically one-on-one \citep[also group-based; see,][]{McKenzie2021b}
+	\item Typically one-on-one \citep[also group-based; see,][]{Iacovone2021}
 
@@
 \begin{itemize_2pt}
-	\item Psychological research finds interpersonal differences in \textcolor{bdf}{exploration-exploitation behavior} 
-	\begin{itemize_2pt}
-		\item Evidence for trait-like persistence of preference (see, e.g.,\textcolor{camel}{Waldner et al., 1998, Engler et al., 2010})%[citation]
+	\item Exploration-exploitation trade-off 
+	\begin{itemize_2pt}
+
+		\item Not clear how much to exploit available best practice, and how much to invest in search for innovation
+		\item Psychological research finds interpersonal differences in \textcolor{bdf}{preference for information search} \cite[see, e.g.,][]{Hills2015, Schulz2020, Gonzalez2011}
+		%\item Evidence for trait-like persistence of this preference (see, e.g.,\textcolor{camel}{Waldner et al., 1998, Engler et al., 2010})%[citation]
 		\item If technology has initial fixed costs, poverty \textit{per se} may affect trade-off
